### 2016-06-08 asce-paper.tex
initialising ascelike manuscript

\documentclass[Journal,SectionNumbers,SingleSpace]{ascelike}

\usepackage{subfigure}
\usepackage{epsfig}
%\usepackage{timesmt}

\usepackage[utf8]{inputenc}
\usepackage[OT1]{fontenc}
\usepackage{graphicx}
\usepackage[english]{babel}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}

\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{url}
\usepackage{tikz}
\usetikzlibrary{shapes.misc,fit}

%\usepackage[bookmarks]{hyperref}
\usepackage[colorlinks=true,citecolor=red,linkcolor=black]{hyperref}

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}
\newcommand{\posrealszero}{\reals_{\ge 0}}
\newcommand{\naturals}{\mathbb{N}}

\newcommand{\dd}{\,\mathrm{d}}

\newcommand{\mbf}[1]{\mathbf{#1}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\renewcommand{\vec}[1]{{\bm#1}}

\newcommand{\uz}{^{(0)}} % upper zero
\newcommand{\un}{^{(n)}} % upper n
\newcommand{\ui}{^{(i)}} % upper i

\newcommand{\ul}[1]{\underline{#1}}
\newcommand{\ol}[1]{\overline{#1}}

\newcommand{\Rsys}{R_\text{sys}}
\newcommand{\lRsys}{\ul{R}_\text{sys}}
\newcommand{\uRsys}{\ol{R}_\text{sys}}

\newcommand{\Fsys}{F_\text{sys}}
\newcommand{\lFsys}{\ul{F}_\text{sys}}
\newcommand{\uFsys}{\ol{F}_\text{sys}}

\def\Tsys{T_\text{sys}}

\newcommand{\E}{\operatorname{E}}
\newcommand{\V}{\operatorname{Var}}
\newcommand{\wei}{\operatorname{Wei}} % Weibull Distribution
\newcommand{\ig}{\operatorname{IG}}   % Inverse Gamma Distribution

\def\yz{y\uz}
\def\yn{y\un}
%\def\yi{y\ui}
\newcommand{\yfun}[1]{y^{({#1})}}
\newcommand{\yfunl}[1]{\ul{y}^{({#1})}}
\newcommand{\yfunu}[1]{\ol{y}^{({#1})}}

\def\ykz{y\uz_k}
\def\ykn{y\un_k}

\def\yzl{\ul{y}\uz}
\def\yzu{\ol{y}\uz}
\def\ynl{\ul{y}\un}
\def\ynu{\ol{y}\un}
\def\yil{\ul{y}\ui}
\def\yiu{\ol{y}\ui}

\def\ykzl{\ul{y}\uz_k}
\def\ykzu{\ol{y}\uz_k}
\def\yknl{\ul{y}\un_k}
\def\yknu{\ol{y}\un_k}

\def\nz{n\uz}
\def\nn{n\un}
%\def\ni{n\ui}
\newcommand{\nfun}[1]{n^{({#1})}}
\newcommand{\nfunl}[1]{\ul{n}^{({#1})}}
\newcommand{\nfunu}[1]{\ol{n}^{({#1})}}

\def\nkz{n\uz_k}
\def\nkn{n\un_k}
\newcommand{\nkzfun}[1]{n\uz_{#1}}

\def\nzl{\ul{n}\uz}
\def\nzu{\ol{n}\uz}
\def\nnl{\ul{n}\un}
\def\nnu{\ol{n}\un}
\def\nil{\ul{n}\ui}
\def\niu{\ol{n}\ui}

\def\nkzl{\ul{n}\uz_k}
\def\nkzu{\ol{n}\uz_k}
\def\nknl{\ul{n}\un_k}
\def\nknu{\ol{n}\un_k}

\def\taut{\tau(\vec{t})}
\def\ttau{\tilde{\tau}}
\def\ttaut{\ttau(\vec{t})}

\def\MZ{\mathcal{M}\uz}
\def\MN{\mathcal{M}\un}

\def\MkZ{\mathcal{M}\uz_k}
\def\MkN{\mathcal{M}\un_k}

\def\PkZ{\Pi\uz_k}
\def\PkN{\Pi\un_k}
\newcommand{\PZi}[1]{\Pi\uz_{#1}}

\def\tnow{t_\text{now}}
\def\tpnow{t^+_\text{now}}

\newcommand{\comments}[1]{{\small\color{gray} #1}}

\newtheorem{example}{Example}

\allowdisplaybreaks

\title{Notes for ISIPTA poster}
\author{Gero Walter, Frank P.A. Coolen, Simme Douwe Flapper}

\begin{document}
\title{ROBUST REMAINING USEFUL LIFE FOR COMPLEX SYSTEMS\\ or\\ ROBUST BAYESIAN RELIABILITY FOR COMPLEX SYSTEMS\\ or \ldots}

\author{
Gero Walter%
\thanks{
School of Industrial Engineering,
Eindhoven University of Technology, Eindhoven, The Netherlands.
E-mail: g.walter@tue.nl.},
\ Ph.D.
\\
and
Frank P.A. Coolen%
\thanks{
Department of Mathematical Sciences,
Durham University, Durham, United Kingdom.
E-mail: frank.coolen@durham.ac.uk.},
\ Ph.D.
}

\maketitle

% slightly adapted ESREL abstract
\begin{abstract}
In reliability engineering, data about failure events is often scarce.
To arrive at meaningful estimates for the reliability of a system,
it is therefore often necessary to also include expert information in the analysis,
which is straightforward in the Bayesian approach by using an informative prior distribution.
%
A problem that then can arise is called prior-data conflict:
from the viewpoint of the prior, the observed data seem very surprising,
i.e., the information from data is in conflict with the prior assumptions.
It has been recognised that models based on conjugate priors can be insensitive to prior-data conflict,
in the sense that the spread of the posterior distribution does not increase in case of such a conflict,
thus conveying a false sense of certainty by communicating that we can quantify the reliability of a system quite precisely when in fact we cannot.
%
We present an approach to mitigate this issue, by considering sets of prior distributions
to model vague knowledge on component lifetimes,
and study how surprisingly early or late component failures
affect the prediction of the reliability of a system with arbitrary layout,
making use of survival signature to characterise the system under study.
Our approach can be seen as a robust Bayesian procedure or imprecise probability method
that appropriately reflects surprising data in the posterior system survival function or other posterior inferences.
\end{abstract}

\KeyWords{System Reliability, Imprecise Probability, Survival Signature, Robust Bayesian, Remaining Useful Life}

***slightly adapted ESREL abstract, must be 150--175 words long (this has 226), may not contain references or mathematics.

\section{Introduction}

***reuse ESREL paper intro

\section{The Meat}

System with components of $k=1,\ldots,K$ different types.
There are $n_k$ components of type $k$ in the system.

For each $k$, component lifetimes ($i=1,\ldots,n_k$) are $T_i^k \mid \lambda_k \sim \wei(\kappa,\lambda_k)$,
where $\kappa$ is fixed and known:
\begin{linenomath*}
\begin{align}
f_k(t_i^k \mid \lambda_k) &= \frac{\kappa}{\lambda_k} (t_i^k)^{\kappa-1} e^{-\frac{(t_i^k)^{\kappa-1}}{\lambda_k}} \\
F_k(t_i^k \mid \lambda_k) &= 1 - e^{-\frac{(t_i^k)^\kappa}{\lambda_k}} = P_k(T_i^k \leq t_i^k \mid \lambda_k)
\end{align}
\end{linenomath*}

Conjugate prior is $\lambda_k \sim \ig(\alpha_k,\beta_k)$:
\begin{linenomath*}
\begin{align}
f_{\lambda_k}(\lambda_k\mid \alpha_k,\beta_k) &= \frac{(\beta_k)^{\alpha_k}}{\Gamma(\alpha_k)} \lambda_k^{-\alpha_k -1} e^{-\frac{\beta_k}{\lambda_k}}
\end{align}
\end{linenomath*}
In terms of canonical parameters $\nkz$ and $\ykz$, we assume $\lambda_k \mid \nkz,\ykz \sim \ig(\nkz + 1, \nkz\ykz)$.

Set of priors $\MkZ$ defined by $(\nkz,\ykz) \in \PkZ = [\nkzl,\nkzu] \times [\ykzl,\ykzu]$.

Observing a one of a kind system with $n_k$ components of type $k$ running until $\tnow$,
where $e_k$ components have failed by $\tnow$, and $n_k - e_k$ components still function:
\begin{linenomath*}
\begin{align}
\mbf{t}^k_{e_k;n_k} &= \big( \underbrace{t^k_1, \ldots, t^k_{e_k}}_{e_k \text{failure times}},
                             \underbrace{\tpnow, \ldots, \tpnow}_{n_k-e_k \text{censored obs.}} \big)
\end{align}
\end{linenomath*}

\end{document}

### 2016-06-13 asce-paper.tex
posternotes theory in

@@
 \ Ph.D.
+\\
+and ???
 }
@@
 \maketitle
+
+Invited for special issue ``The treatment of uncertainty in risk and reliability modelling and decision making''
+(special issue code SI022A), guest editors Luca Podolfillini, Bruno Sudret, Enrico Zio,
+in ASCE-ASME Journal of Risk and Uncertainty in Engineering Systems: Part A (Civil Engineering)
 
@@
 
-\section{The Meat}
+\section{Bayesian Analysis of Weibull Lifetimes}
 
@@
 
+\section{Sets of Priors}
+
 Set of priors $\MkZ$ defined by $(\nkz,\ykz) \in \PkZ = [\nkzl,\nkzu] \times [\ykzl,\ykzu]$.
+
+***illustrate prior-data conflict similar to ESREL paper
+
+\section{Robust RUL Estimation for Complex Systems via the Survival Signature}
+
+\subsection{Right-censored Lifetimes}
 
@@
 
+***change to general right-censoring? So $n_k-e_k \to c_k$, $e_k+c_k=n_k$,
+introduce sets of observed and censored?
+
+\subsection{Bayesian Estimation of Component Scale Parameter}
+
+Posterior:
+\begin{linenomath*}
+\begin{align}
+f_{\lambda_k\mid\ldots}(\lambda_k\mid\nkz,\ykz,\mbf{t}^k_{e_k;n_k})
+ &\propto f_{\lambda_k}(\lambda_k)
+          \big[ 1- F_k(\tnow\mid\lambda_k) \big]^{n_k-e_k}
+          \prod_{i=1}^{e_k} f_k(t_i^k \mid \lambda_k) 
+\end{align}
+\end{linenomath*}
+and so $\lambda_k\mid\nkz,\ykz,\mbf{t}^k_{e_k;n_k} \sim \ig(\nkn + 1, \nkn\ykn)$, where
+\begin{linenomath*}
+\begin{align}
+\nkn + 1 &= \nkz + e_k + 1 \\
+\nkn\ykn &= \nkz\ykz + (n_k-e_k) \tnow^\kappa + \sum_{i=1}^{e_k} (t_i^k)^\kappa
+\end{align}
+\end{linenomath*}
+so the posterior expectation for $\lambda$ is
+\begin{linenomath*}
+\begin{align}
+\E[\lambda_k\mid\nkn,\ykn] &= \ykn
+                            = \frac{\nkz}{\nkz + e_k} \ykz +
+                              \frac{e_k}{\nkz + e_k} \cdot \Big[\frac{n_k-e_k}{e_k} \tnow^\kappa + \frac{1}{e_k}\sum_{i=1}^{e_k} (t_i^k)^\kappa \Big]
+\end{align}
+\end{linenomath*}
+
+\subsection{RUL using the Survival Signature}
+
+System survival calculated by %(see Risk Analysis paper eq. (7))
+\begin{linenomath*}
+\begin{align}
+P(\Tsys > t) &= \sum_{l_1=0}^{n_1} \cdots \sum_{l_K=0}^{n_K} \Phi(l_1,\ldots,l_K) P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \\
+\intertext{ and assuming components of different types are independent,}
+             &= \sum_{l_1=0}^{n_1} \cdots \sum_{l_K=0}^{n_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K P(C^k_t = l_k)
+\end{align}
+\end{linenomath*}
+where the survival signature $\Phi(l_1,\ldots,l_K)$ is non-decreasing in each $l_k$ for coherent systems,
+and $P(C^k_t = l_k)$ is the (predictive) probability that exactly $l_k$ components of type $k$ function at time $t$.
+
+A priori, we have, for $l_k = 0,1,\ldots, n_k$,
+\begin{linenomath*}
+\begin{align}
+P(C^k_t = l_k\mid\nkz,\ykz)
+ &= { n_k \choose l_k} \int [F_k(t \mid\lambda_k)]^{n_k-l_k}
+                        [1 - F_k(t \mid\lambda_k)]^{l_k} f_{\lambda_k}(\lambda_k\mid\nkz,\ykz) \dd \lambda_k
+\end{align}
+\end{linenomath*}
+under the assumption that components of the same type are independent given $\lambda_k$.
+
+\subsection{Posterior Predictive Distribution}
+
+For the situation with the system observed until $\tnow$, with data $\mbf{t}^k_{e_k;n_k}$,
+we need the posterior predictive probability $P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$.
+
+For $l_k > n_k - e_k$, we must have $P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k}) = 0$,
+as at most $n_k - e_k$ components can function for $t > \tnow$.
+
+%(Should one work with the subsystem consisting only of the non-failed $n_k - e_k$ components?)\\
+
+A posteriori, we have, for $l_k = 0,1,\ldots, n_k - e_k$,
+\begin{linenomath*}
+\begin{align}
+P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})
+ &= { n_k - e_k \choose l_k} \int [P_k(T \leq t \mid T > \tnow, \lambda_k)]^{n_k - e_k - l_k} \times \\ & \hspace*{2ex}
+                              [1 - P_k(T \leq t \mid T > \tnow, \lambda_k)]^{l_k}
+    f_{\lambda_k\mid\ldots}(\lambda_k\mid\nkz,\ykz,\mbf{t}^k_{e_k;n_k}) \dd \lambda_k
+\end{align}
+\end{linenomath*}
+
+Now,
+\begin{linenomath*}
+\begin{align}
+P_k(T \leq t \mid T > \tnow, \lambda_k)
+ &= \frac{P_k(\tnow < T \leq t \mid\lambda_k)}{P_k(T > \tnow \mid \lambda_k)}
+  = \frac{F_k(t\mid\lambda_k) - F_k(\tnow\mid\lambda_k)}{1-F_k(\tnow\mid\lambda_k)} \\
+ &= \frac{e^{-\frac{(\tnow)^\kappa}{\lambda_k}} - e^{-\frac{t^\kappa}{\lambda_k}}}{e^{-\frac{(\tnow)^\kappa}{\lambda_k}}}
+  = 1 - e^{-\frac{t^\kappa - (\tnow)^\kappa}{\lambda_k}}
+\end{align}
+\end{linenomath*}
+
+With this and the posterior substituted in, we get
+\begin{linenomath*}
+\begin{align}
+\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})} \\
+ &= { n_k - e_k \choose l_k} \int \Big[1 - e^{-\frac{t^\kappa - (\tnow)^\kappa}{\lambda_k}}\Big]^{n_k - e_k - l_k}
+                                  \Big[    e^{-\frac{t^\kappa - (\tnow)^\kappa}{\lambda_k}}\Big]^{l_k} \times \\ & \hspace*{28ex}
+    \frac{[\nkn\ykn]^{\nkn + 1}}{\Gamma(\nkn+1)} \lambda_k^{-(\nkn + 1) - 1} e^{-\frac{\nkn\ykn}{\lambda_k}} \dd \lambda_k \\
+ &= { n_k - e_k \choose l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j { n_k - e_k - l_k \choose j} \frac{[\nkn\ykn]^{\nkn + 1}}{\Gamma(\nkn+1)} 
+    \times \\ & \hspace*{25ex}
+    \int \lambda_k^{-(\nkn + 1) - 1} e^{-\frac{(l_k + j) (t^\kappa - (\tnow)^\kappa) + \nkn\ykn}{\lambda_k}} \dd \lambda_k
+\end{align}
+\end{linenomath*}
+
+The terms remaining under the integral form the core of an $\ig(\nkn + 1, \nkn\ykn + (l_k + j) (t^\kappa - (\tnow)^\kappa))$,
+allowing us to solve the integral using the corresponding normalization constant.
+\begin{linenomath*}
+\begin{align}
+\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})} \\
+ &= { n_k - e_k \choose l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j { n_k - e_k - l_k \choose j}
+    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) (t^\kappa - (\tnow)^\kappa)}\right)^{\nkn + 1} \\
+ &= \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!}   
+    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) (t^\kappa - (\tnow)^\kappa)}\right)^{\nkn + 1} \\
+ &= \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!} \times \\ & \hspace*{13ex}  
+    \left(\frac{\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^\kappa + (n_k-e_k) (\tnow)^\kappa }%
+               {\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^\kappa + (n_k-e_k-l_k-j) (\tnow)^\kappa + (l_k + j) t^\kappa }\right)^{%
+    \nkz + e_k + 1} 
+\end{align}
+\end{linenomath*}
+for $l_k \in \{0,1,\ldots,n_k-e_k\}$.
+
+We actually need to compute only those $P(C^k_t = l_k\mid \ldots)$ with $l_k$'s for which $\Phi(l_1,\ldots,l_K) > 0$.
+
+Seen as function in $t$, we see that $t$ appears $n_k-e_k-l_k+1$ times,
+once in each summand, in the denominator of the fraction powered to the $\nkn+1$,
+and summands whith even $j$ are decreasing in $t$,
+while summands whith odd $j$ are increasing in $t$.
+Nevertheless, in total $P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$
+must be decreasing in $t$, as the remaining $n_k-e_k$ components continue to age,
+and so the probability that $l_k$ of them remain operational must decrease.
+
+\subsection{Optimizing over Sets of Parameters}
+
+%I would think that
+%$\min / \max_{(\nkz,\ykz) \in \PkZ} P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$
+%must be solved by numeric optimization for each $k, l_k, t$ 
+%because of the alternating signs for the summands.
+%(In absolute terms, each summand is increasing in $\ykz$, but not monotone in $\nkz$.)
+
+%(Box-constraint optimization possible, e.g., with option \texttt{L-BFGS-B} of \texttt{optim} in \textbf{R}.)
+Similar to the considerations about $t$, as higher values for $\ykz$ mean higher expected lifetimes for the components,
+the larger $\ykz$, the higher the probability that many components survive
+($P(C^k_t = l_k\mid\ldots)$ high for large $l_k$)
+and, with that, the lower the probability that few or no components survive
+($P(C^k_t = l_k\mid\ldots)$ low for small $l_k$).
+
+In terms of the cumulative probability mass function (cmf) for $C^k_t$, which can be written as 
+\begin{linenomath*}
+\begin{align}
+%F_{C^k_t}(l_k \mid \nkz,\ykz, \mbf{t}^k_{e_k;n_k}) = P(C^k_t \leq l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k}) 
+% = \sum_{q=0}^{l_k} P(C^k_t = q\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})
+F_{C^k_t}(l_k \mid \ldots) = P(C^k_t \leq l_k\mid\ldots) = \sum_{q=0}^{l_k} P(C^k_t = q\mid\ldots)\,,
+\end{align}
+\end{linenomath*}
+we therefore conclude that
+the lower cmf $\ul{F}(C^k_t = l_k\mid \ldots)$ must be obtained with the lower bounds for all $\ykz$, $k=1,\ldots,K$,
+and the upper cmf $\ol{F}(C^k_t = l_k\mid \ldots)$ must be obtained with the respective upper bounds.
+
+***proove rigorously (would need a kind of likelihood difference order)?
+%Do I get your comments right that based on lower and upper bounds
+%$\ul{P}(C^k_t = l_k\mid \ldots)$ and $\ol{P}(C^k_t = l_k\mid \ldots)$ for all $l_k = 0, 1, \ldots, n_k - e_k$,
+%we can easily get lower and upper bounds for the cdf $F_{C^k_t}(l_k \mid \ldots)$?
+
+Furthermore, higher expected lifetimes for the components must mean
+a longer system survival, so in turn the $\ul{F}_{C^k_t}(l_k \mid \ldots)$'s
+should give us the lower bound for $P(\Tsys > t\mid\ldots)$,
+and the $\ol{F}_{C^k_t}(l_k \mid \ldots)$'s the upper bound.
+Note that e.g.\ $\ul{F}_{C^k_t}(l_k \mid \ldots)$ may, however, not correspond to a single parameter pair $(\nkz, \ykz)$.
+Also, in the system survival equation ($t > \tnow$)
+\begin{linenomath*}
+\begin{align} \label{eq:25}
+\lefteqn{%
+P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)} \hspace*{10ex}\nonumber\\ 
+ &= \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K
+    P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})
+\end{align}
+\end{linenomath*}
+we cannot simply plug in all the $\ul{P}(C^k_t = l_k\mid \ldots)$ %and $\ol{P}(C^k_t = l_k\mid \ldots)$
+to get $\ul{P}(\Tsys > t\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$, % and $\ol{P}(\Tsys > t\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$,
+as the $\ul{P}(C^k_t = l_k\mid \ldots)$ could correspond to different $(\nkz,\ykz)$ for each $l_k$.
+(It would give us a lower bound for $\ul{P}(\Tsys > t\mid\ldots)$, however, but it might be very coarse.)
+
+Writing out Equation~\eqref{eq:25}, we get
+\begin{linenomath*}
+\begin{align}
+\lefteqn{P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)} \\
+ &= \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K
+    P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k}) \\
+ &= \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K
+    \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!} \times \\ & \hspace*{45ex}
+    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) (t^\kappa - (\tnow)^\kappa)}\right)^{\nkn + 1} \\
+ &= \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K \label{eq:30}
+    \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!} \times \\ & \hspace*{17ex}
+    \left(\frac{\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^\kappa + (n_k-e_k) (\tnow)^\kappa }%
+               {\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^\kappa + (n_k-e_k-l_k-j) (\tnow)^\kappa + (l_k + j) t^\kappa }\right)^{%
+    \nkz + e_k + 1} 
+\end{align}
+\end{linenomath*}
+
+While it is clear that the lower bounds for $\ykz$ will lead to the lower system survival function,
+the role of $\nkz$ is not so clear.
+We therefore resort to numerical optimization of \eqref{eq:25} over $\{\nkz, k=1,\ldots,K\}$
+to obtain the lower bound for $P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)$.
+
 \end{document}

### 2016-06-24 asce-paper.tex
suggestion Frank for elicitation part
working on intro

@@
 
+***``For most ASCE journals, the maximum number of words and word-equivalents is 10,000 for technical papers''
+
 % slightly adapted ESREL abstract
@@
 
-***reuse ESREL paper intro
+In reliability engineering, a central task is to describe the reliability of a complex system.
+This is usually done by determining the \emph{reliability function} $R(t)$,
+in other contexts also known as the \emph{survival function} $S(t)$,
+giving the probability that the system has not failed by time $t$:
+\begin{align}
+R_\text{sys}(t) = P(T_\text{sys} \geq t)\,,
+\end{align}
+where $T_\text{sys}$ is the random variable giving the failure time of the system. %
+%\footnote{}
+Based on the distribution of $T_\text{sys}$, which can also be expressed
+in terms of the cumulative distribution function $F_\text{sys}(t) = 1 - R_\text{sys}(t)$,
+the density $p_\text{sys}(t)$ or the hazard rate $\lambda_\text{sys}(t)$,
+decisions about, e.g., scheduling of maintenance work can be made.
+
+Often, there is no failure data for the system itself
+(e.g., if the system is a prototype, or the system is used under unique circumstances),
+but there is some information about failure times for the components the system is made of.
+Information on the distribution of component failure times $T_i$,
+where $i = 1, \ldots, n$ if the system consists of $n$ components,
+can then be used to derive the distribution of $T_\text{sys}$.
+In this paper, we consider*** a simple parallel system
+where all components are of the same type,
+and our observations consist solely of the failure times of one or more components in this system.
+%In the last section, we will briefly describe
+%how the approach can be generalized to arbitrary system structures
+%using the survival signature \cite{2012:survsign},
+%which allows for different types of components and
+%the inclusion of data from component tests, as in \citeNP{2014:bayessurvsign}.
+%
+We assume a parametric probability distribution for component lifetimes $T_i$. 
+The Bayesian approach allows to base estimation of the component failure distributions
+on both data and further knowledge not given by the data,
+the latter usually provided in the form of expert knowledge.
+This knowledge is encoded in form of a so-called prior distribution,
+a distribution on the parameter(s) of the component lifetime distribution.
+This expert knowledge is especially important when there is very few data on the components (like in our scenario),
+as only with its help meaningful estimates for the system reliability can be made.
 
@@
 
+\section{elicitation}
+
+*** prior via pseudo-observations, can contain censored pseudo-data
+
+*** cf paper from Frank 20ys ago (?)
+
 \end{document}

### 2016-07-07 asce-paper.tex
adding refs, work on intro

@@
 
+\def\Rsys{R_\text{sys}}
 \def\Tsys{T_\text{sys}}
@@
 \begin{align}
-R_\text{sys}(t) = P(T_\text{sys} \geq t)\,,
+\Rsys(t) = P(\Tsys \geq t)\,,
 \end{align}
-where $T_\text{sys}$ is the random variable giving the failure time of the system. %
+where $\Tsys$ is the random variable giving the failure time of the system. %
 %\footnote{}
-Based on the distribution of $T_\text{sys}$, which can also be expressed
-in terms of the cumulative distribution function $F_\text{sys}(t) = 1 - R_\text{sys}(t)$,
+Based on the distribution of $\Tsys$, which can also be expressed
+in terms of the cumulative distribution function $F_\text{sys}(t) = 1 - \Rsys(t)$,
 the density $p_\text{sys}(t)$ or the hazard rate $\lambda_\text{sys}(t)$,
@@
 but there is some information about failure times for the components the system is made of.
-Information on the distribution of component failure times $T_i$,
-where $i = 1, \ldots, n$ if the system consists of $n$ components,
-can then be used to derive the distribution of $T_\text{sys}$.
-In this paper, we consider*** a simple parallel system
-where all components are of the same type,
-and our observations consist solely of the failure times of one or more components in this system.
+We are able to analyse systems of arbitrary system structures, %layout of components,
+i.e., any combination and nesting of series, parallel, k-out-of-n, or bridge-type arrangements,
+by use of the survival signature \cite{2012:survsign}.
+In this paper, we assume that components can be divided into $K$ different groups,
+and components within each group $k$ ($k=1, \ldots, K$) can be assumed to follow the same failure time distribution.
+We denote components of group $k$ as \emph{type $k$ components},
+and assume independence between component types,
+such that failure times of components of different types are independent.
+We assume that type $k$ component lifetimes $T_i^k$ ($i = 1, \ldots, n_k$)
+are Weibull distributed, with type-specific parameters $\beta_k$ (shape) and $\lambda_k$ (scale).
+***type-specific shape not implemented yet!***
+
+Focusing on the prototype application,
+we assume that our observations consist solely of the failure times of components in this system up to time $\tnow$,
+such that the failure times of components that have not failed by $\tnow$ are right-censored,
+and calculate $\Rsys(t \mid t > \tnow) = P(\Tsys \geq t \mid t > \tnow)$,
+which can be used to determine the remaining useful life (in short RUL, see, e.g., ***) of the system.
+%This sparse information is complemented by expert information on component lifetimes $T_i^k$.
+
+The Bayesian approach allows to base estimation of the component failure distributions
+on both data and further knowledge not given by the data,
+the latter usually provided in the form of expert knowledge.
+This knowledge is encoded in form of a so-called prior distribution,
+a distribution on the parameter of the component lifetime distributions.
+This expert knowledge is especially important when there is very few data on the components (like in our scenario),
+as only with its help meaningful estimates for the system reliability can be made.
+
+***
+
+This work extends \ldots
+
+The paper is structured as follows:
+
 %In the last section, we will briefly describe
@@
 %the inclusion of data from component tests, as in \citeNP{2014:bayessurvsign}.
-%
-We assume a parametric probability distribution for component lifetimes $T_i$. 
-The Bayesian approach allows to base estimation of the component failure distributions
-on both data and further knowledge not given by the data,
-the latter usually provided in the form of expert knowledge.
-This knowledge is encoded in form of a so-called prior distribution,
-a distribution on the parameter(s) of the component lifetime distribution.
-This expert knowledge is especially important when there is very few data on the components (like in our scenario),
-as only with its help meaningful estimates for the system reliability can be made.
+%Information on the distribution of component failure times $T_i$,
+%where $i = 1, \ldots, n$ if the system consists of $n$ components,
+%can then be used to derive the distribution of $T_\text{sys}$.
 
@@
 System with components of $k=1,\ldots,K$ different types.
-There are $n_k$ components of type $k$ in the system.
+There are $n_k$ exchangeable components of type $k$ in the system.
 
@@
 
+\pagebreak
+%
+%
+% Now we start the appendices, with the new section name, "Appendix", and a 
+%  new counter, "I", "II", etc.
+%
+\appendix\label{section:references}
+%
+% Here's the first appendix, the list of references:
+%
+\bibliography{refs}
+%
+%\cite{key}   produces citations with full author list and year 
+%\citeNP{key} produces citations with full author list and year, but without enclosing parentheses
+%\citeA{key}  produces citations with only the full author list
+%\citeN{key}  produces citations with the full author list and year, but
+%             which can be used as nouns in a sentence; no parentheses appear around
+%             the author names, but only around the year
+%\citeyear{key}   produces the year information only, within parentheses
+%\citeyearNP{key} produces the year information only
+%
+%
+% And now for some pretty impressive notation.  In this example, I have used
+%   the tabular environment to line up the columns in ASCE style.
+%   Note that this and all appendices (except the references) start with 
+%   the \section command
+%
+\section{Notation}
+\emph{The following symbols are used in this paper:}%\par\vspace{0.10in}
+\nopagebreak
+\par
+\begin{tabular}{r  @{\hspace{1em}=\hspace{1em}}  l}
+$D$                    & pile diameter (m); \\
+$R$                    & distance (m);      and\\
+$C_{\mathrm{Oh\;no!}}$ & fudge factor.
+\end{tabular}
+
 \end{document}

### 2016-07-08 asce-paper.tex
intro section from esrel2015 paper

@@
 in terms of the cumulative distribution function $F_\text{sys}(t) = 1 - \Rsys(t)$,
-the density $p_\text{sys}(t)$ or the hazard rate $\lambda_\text{sys}(t)$,
+%the density $p_\text{sys}(t)$ or the hazard rate $\lambda_\text{sys}(t)$,
 decisions about, e.g., scheduling of maintenance work can be made.
@@
 This knowledge is encoded in form of a so-called prior distribution,
-a distribution on the parameter of the component lifetime distributions.
+a distribution on the parameters of the component lifetime distributions.
 This expert knowledge is especially important when there is very few data on the components (like in our scenario),
@@
 
-***
+However, the choice for the prior distribution to encode the given expert knowledge is often debatable,
+and a specific choice of prior is difficult to justify.
+A way to deal with this is to employ sensitivity analysis,
+i.e., studying the effect of different choices of prior distribution on the quantities of interest
+(in our case, the system reliability function, which, in Bayesian terms, is a predictive distribution).
+This idea has been explored in systematic sensitivity analysis, or robust Bayesian methods
+(for an overview on this approach, see, e.g.,
+\citeNP{1994:berger} or \citeNP{2000:rios}). %\citeNP{2005:ruggeri}, \citeNP{2000:bergerinsuaruggeri}
 
-This work extends \ldots
+The work we present here can be seen as belonging to the robust Bayesian approach,
+as our work uses sets of priors. However, our focus and interpretation is slightly different,
+as we consider the result of our procedure, sets of reliability functions, as the proper result,
+while a robust Bayesian would base his analyses on a single reliability function from the set
+in case (s)he was able to conclude that quantities of interest are not `too sensitive' to the choice of prior.
+In contrast, our viewpoint is rooted in the theory of imprecise or interval probability \cite{1991:walley,itip},
+where sets of distributions are used to express the precision of probability statements themselves:
+the smaller the set, the more precise the probability statement.
+Indeed, the system reliability function $\Rsys(t)$ is a collection of probability statements,
+and a small set for $\Rsys(t)$ will indicate that we can quantify the reliability of the system quite precisely,
+while a large set will indicate that our knowledge about $\Tsys$ is rather shaky.
 
-The paper is structured as follows:
+In line with imprecise or interval probability methods, we will thus have, for each $t$,
+a lower reliability $\lRsys(t) = \ul{P}(T_\text{sys} \geq t)$,
+and an upper reliability $\uRsys(t) = \ol{P}(T_\text{sys} \geq t)$.
+We will explain in Sections~\ref{sec:modforsurpr} and *** how these bounds are obtained
+based on a set of prior distributions on the scale parameter of the component lifetime distribution.
+
+The central merit of our method is that it adequately reflects prior-data conflict
+(see, e.g., \citeNP{2006:evans}),
+i.e.\ the conflict that can arise between prior assumptions on component lifetimes
+and observed behaviour of components in the system under study.
+As we will show in Section~\ref{sec:weibull}, when taking the standard choice of a conjugate prior,
+prior-data conflict is ignored, as the spread of the posterior distribution does not increase in case of such a conflict,
+ultimately conveying a false sense of certainty
+by communicating that we can quantify the reliability of a system quite precisely when in fact we can not.
+%
+In contrast, our method will indicate prior-data conflict by wider bounds for $\Rsys(t)$.
+This behaviour is obtained by a specific choice for the set of priors (see \citeNP{Walter2009a} and \citeNP{diss} \S 3.1.4)
+which leads to larger sets of posterior distributions when prior knowledge and data are in conflict
+(see Section~\ref{sec:modforsurpr} for more details).
+
+This work extends \ldots ***
+
+***comment on shape parameter $\beta_k$ being fixed***
+
+We study the effect of surprisingly early or late component failures,
+%on the system reliability prediction,
+showing that observations in conflict to prior assumptions
+indeed lead to more cautious system reliability predictions.
+
+The paper is organized as follows.
+In Section~\ref{sec:weibull}, we describe a Bayesian analysis for Weibull component lifetimes
+and illustrate the issue of prior-data conflict.
+Section~\ref{sec:modforsurpr} then details the use of sets of priors
+for the scale parameter $\lambda_k$ of the Weibull distribution,
+showing how this mitigates the prior-data conflict issue for $\lambda_k$.
 
@@
 \section{Bayesian Analysis of Weibull Lifetimes}
+\label{sec:weibull}
 
@@
 
-\section{Sets of Priors}
+\section{Models reflecting surprising data / Sets of Priors}
+\label{sec:modforsurpr}
 

### 2016-07-12 asce-paper.tex
inv gamma with params a and b
rul paper, start of sec 2

@@
 In this paper, we assume that components can be divided into $K$ different groups,
-and components within each group $k$ ($k=1, \ldots, K$) can be assumed to follow the same failure time distribution.
+and components within each group $k$ ($k=1, \ldots, K$) can be assumed to be exchangeable,
+i.e., to follow the same failure time distribution.
 We denote components of group $k$ as \emph{type $k$ components},
@@
 and calculate $\Rsys(t \mid t > \tnow) = P(\Tsys \geq t \mid t > \tnow)$,
-which can be used to determine the remaining useful life (in short RUL, see, e.g., ***) of the system.
+which can be used to determine the remaining useful life of the system
+(in short RUL, see, e.g., \citeNP{2014:rul-review}).
 %This sparse information is complemented by expert information on component lifetimes $T_i^k$.
@@
 a distribution on the parameters of the component lifetime distributions.
-This expert knowledge is especially important when there is very few data on the components (like in our scenario),
+Expert knowledge is especially important when there is very few data on the components (like in our scenario),
 as only with its help meaningful estimates for the system reliability can be made.
@@
 
+Due to the iterative nature of the Bayesian framework,
+it is possible to use a set of posteriors based on component test data as the set of priors
+instead of a purely expert-based set of priors as discussed so far.
+In that case, prior-data conflict sensitivity allows to uncover also a conflict between
+current observations in the running system and past observations from component tests.
+
 This work extends \ldots ***
@@
 showing how this mitigates the prior-data conflict issue for $\lambda_k$.
+***
 
@@
 
-System with components of $k=1,\ldots,K$ different types.
-There are $n_k$ exchangeable components of type $k$ in the system.
-
-For each $k$, component lifetimes ($i=1,\ldots,n_k$) are $T_i^k \mid \lambda_k \sim \wei(\kappa,\lambda_k)$,
-where $\kappa$ is fixed and known:
+We consider a system with components of $k=1,\ldots,K$ different types;
+for each type $k$, there are $n_k$ exchangeable components in the system.
+For each type $k$ component, we assume for its lifetime $T_i^k$ ($i=1,\ldots,n_k$, $k = 1, \ldots, K$)
+a Weibull distribution with fixed shape parameter $\beta_k > 0$, with density and cdf%
+\footnote{Our approach would be possible also for other parametric lifetime distributions
+that form a canonical exponential family
+(see, e.g., \citeNP[p.~202 and 272f]{2000:bernardosmith}, or \citeNP[p.~8]{diss}).}
 \begin{linenomath*}
 \begin{align}
-f_k(t_i^k \mid \lambda_k) &= \frac{\kappa}{\lambda_k} (t_i^k)^{\kappa-1} e^{-\frac{(t_i^k)^{\kappa-1}}{\lambda_k}} \\
-F_k(t_i^k \mid \lambda_k) &= 1 - e^{-\frac{(t_i^k)^\kappa}{\lambda_k}} = P_k(T_i^k \leq t_i^k \mid \lambda_k)
+f_k(t_i^k \mid \lambda_k) &= \frac{\beta_k}{\lambda_k} (t_i^k)^{\beta_k-1} e^{-\frac{(t_i^k)^{\beta_k-1}}{\lambda_k}}\, \\
+F_k(t_i^k \mid \lambda_k) &= 1 - e^{-\frac{(t_i^k)^\beta_k}{\lambda_k}} = P_k(T_i^k \leq t_i^k \mid \lambda_k)\,,
 \end{align}
 \end{linenomath*}
+%For each $k$, component lifetimes ($i=1,\ldots,n_k$) are
+in short $T_i^k \mid \lambda_k \sim \wei(\beta_k,\lambda_k)$.
+%where $\beta_k$ is fixed and known:
 
-Conjugate prior is $\lambda_k \sim \ig(\alpha_k,\beta_k)$:
+Conjugate prior is $\lambda_k \sim \ig(a_k,b_k)$:
 \begin{linenomath*}
 \begin{align}
-f_{\lambda_k}(\lambda_k\mid \alpha_k,\beta_k) &= \frac{(\beta_k)^{\alpha_k}}{\Gamma(\alpha_k)} \lambda_k^{-\alpha_k -1} e^{-\frac{\beta_k}{\lambda_k}}
+f_{\lambda_k}(\lambda_k\mid a_k,b_k) &= \frac{(b_k)^{a_k}}{\Gamma(a_k)} \lambda_k^{-a_k -1} e^{-\frac{b_k}{\lambda_k}}
 \end{align}

### 2016-07-12 asce-paper.tex
more in sec 2 (drop k there?)

@@
 For each type $k$ component, we assume for its lifetime $T_i^k$ ($i=1,\ldots,n_k$, $k = 1, \ldots, K$)
-a Weibull distribution with fixed shape parameter $\beta_k > 0$, with density and cdf%
+a Weibull distribution with fixed shape parameter $\beta_k > 0$,
+in short $T_i^k \mid \lambda_k \sim \wei(\beta_k,\lambda_k)$,
+with density and cdf%
 \footnote{Our approach would be possible also for other parametric lifetime distributions
@@
 \begin{align}
-f_k(t_i^k \mid \lambda_k) &= \frac{\beta_k}{\lambda_k} (t_i^k)^{\beta_k-1} e^{-\frac{(t_i^k)^{\beta_k-1}}{\lambda_k}}\, \\
+f_k(t_i^k \mid \lambda_k) &= \frac{\beta_k}{\lambda_k} (t_i^k)^{\beta_k-1} e^{-\frac{(t_i^k)^{\beta_k-1}}{\lambda_k}}\,, \\
 F_k(t_i^k \mid \lambda_k) &= 1 - e^{-\frac{(t_i^k)^\beta_k}{\lambda_k}} = P_k(T_i^k \leq t_i^k \mid \lambda_k)\,,
@@
 \end{linenomath*}
-%For each $k$, component lifetimes ($i=1,\ldots,n_k$) are
-in short $T_i^k \mid \lambda_k \sim \wei(\beta_k,\lambda_k)$.
-%where $\beta_k$ is fixed and known:
-
-Conjugate prior is $\lambda_k \sim \ig(a_k,b_k)$:
+where $\lambda_k > 0$ and $t > 0$.%
+\footnote{The shape parameter $\beta_k$ determines whether the hazard rate is increasing ($\beta_k > 1$)
+or decreasing ($\beta_k < 1$) over time.
+For $\beta_k=1$, we obtain the Exponential distribution with constant hazard rate as a special case.
+The value for $\beta_k$ will thus often be clear from practical considerations.}
+The scale parameter $\lambda_k$ can be interpreted through the relation
+\begin{linenomath*}
+\begin{align}
+\E[T_i^k \mid \lambda_k] &= \lambda_k^{1/\beta_k}\, \Gamma(1 + 1/\beta_k)\,.
+\label{eq:lambdainterpret}
+\end{align}
+\end{linenomath*}
+For encoding expert knowledge about the reliability of the components,
+we need to assign a prior distribution over the scale parameter $\lambda_k$.
+A convenient choice is to use the inverse Gamma distribution,
+commonly parametrized in terms of the hyperparameters $a_k > 0$ and $b_k > 0$:
+%Conjugate prior is $\lambda_k \sim \ig(a_k,b_k)$:
 \begin{linenomath*}
@@
 \end{linenomath*}
-In terms of canonical parameters $\nkz$ and $\ykz$, we assume $\lambda_k \mid \nkz,\ykz \sim \ig(\nkz + 1, \nkz\ykz)$.
+in short, $\lambda_k \mid a_k, b_k \sim \ig(a_k,b_k)$.
+The inverse Gamma is convenient because it is a conjugate prior,
+i.e., the posterior obtained by Bayes' rule is again inverse Gamma and thus easily tractable;
+the prior parameters only need to be updated to obtain the posterior parameters.
+
+***drop $k$ for rest of this and next section?***
+
+In the standard Bayesian approach, 
+one has to fix a prior by choosing values for $a_k$ and $b_k$
+to encode specific prior information about component lifetimes.
+In our imprecise approach, we allow instead these parameters
+to vary in a set, this is advantageous also
+because expert knowledge is often vague,
+and it is difficult for the expert(s) to pin down precise hyperparameter values.
+For the definition of the hyperparameter set,
+we use however a parametrization in terms of $\nz > 1$ and $\yz > 0$ instead of $a_k$ and $b_k$,
+\begin{linenomath*}
+\begin{align}
+\nz &= \alpha - 1\,,
+&
+\yz &= \beta / \nz \,,
+\end{align}
+\end{linenomath*}
+where $\yz$ can be interpreted as the prior guess for the scale parameter $\lambda$,
+as $\E[\lambda\mid\nz,\yz] = \yz$.
+This parametrization also makes the nature of the combination
+of prior information and data through Bayes' rule more clear:
+After observing $n$ component lifetimes $\vec{t} = (t_1, \ldots, t_n)$,
+the updated parameters are
+\begin{linenomath*}
+\begin{align}
+\nn &= \nz + n\,, 
+&
+\yn &=  \frac{\nz \yz + \taut}{\nz + n}\,,
+\label{eq:ig-update}
+\end{align}
+\end{linenomath*}
+where $\taut = \sum_{i=1}^n t_i^k$. %
+%\footnote{
+We thus have
+\begin{linenomath*}
+\begin{align}
+\lambda \mid \nz, \yz, \vec{t} \sim \ig(\nz + n + 1, \nz \yz + \taut). %}
+\label{eq:ig-update-alpha}
+\end{align}
+\end{linenomath*}
+From the simple update rule \eqref{eq:ig-update}, we see that
+$\yn$ is a weighted average of the prior parameter $\yz$ and the Maximum Likelihood estimator $\taut/n$,
+with weights $\nz$ and $n$, respectively.
+$\nz$ can thus be interpreted as a prior strength or pseudocount,
+indicating how much our prior guess should weigh against the $n$ observations.
+Furthermore, $\V[\lambda\mid\nz,\yz] = (\yz)^2 / (1 - 1/\nz)$,
+so for fixed $\yz$, the higher $\nz$,
+the more probability mass is concentrated around $\yz$. %$p(\lambda\mid\nz,\yz)$
+
+%In terms of canonical parameters $\nkz$ and $\ykz$, we assume $\lambda_k \mid \nkz,\ykz \sim \ig(\nkz + 1, \nkz\ykz)$.
 

### 2016-07-13 asce-paper.tex
setup R files, rest of sec 2

@@
 f_k(t_i^k \mid \lambda_k) &= \frac{\beta_k}{\lambda_k} (t_i^k)^{\beta_k-1} e^{-\frac{(t_i^k)^{\beta_k-1}}{\lambda_k}}\,, \\
-F_k(t_i^k \mid \lambda_k) &= 1 - e^{-\frac{(t_i^k)^\beta_k}{\lambda_k}} = P_k(T_i^k \leq t_i^k \mid \lambda_k)\,,
+F_k(t_i^k \mid \lambda_k) &= 1 - e^{-\frac{(t_i^k)^{\beta_k}}{\lambda_k}} = P(T_i^k \leq t_i^k \mid \lambda_k)\,,
 \end{align}
@@
 
-***drop $k$ for rest of this and next section?***
-
 In the standard Bayesian approach, 
@@
 we use however a parametrization in terms of $\nz > 1$ and $\yz > 0$ instead of $a_k$ and $b_k$,
-\begin{linenomath*}
-\begin{align}
-\nz &= \alpha - 1\,,
-&
-\yz &= \beta / \nz \,,
-\end{align}
-\end{linenomath*}
+where we drop the index $k$ for the discussion about the prior model in the following,
+keeping in mind that each component type will have its own specific parameters.
+We use
+%\begin{linenomath*}
+%\begin{align}
+$\nz = a - 1$ and
+%&
+$\yz = b / \nz$,
+%\end{align}
+%\end{linenomath*}
 where $\yz$ can be interpreted as the prior guess for the scale parameter $\lambda$,
@@
 \end{linenomath*}
-where $\taut = \sum_{i=1}^n t_i^k$. %
+where $\taut = \sum_{i=1}^n (t_i)^\beta$. %
 %\footnote{
@@
 \end{linenomath*}
+%In terms of canonical parameters $\nkz$ and $\ykz$, we assume $\lambda_k \mid \nkz,\ykz \sim \ig(\nkz + 1, \nkz\ykz)$.
 From the simple update rule \eqref{eq:ig-update}, we see that
-$\yn$ is a weighted average of the prior parameter $\yz$ and the Maximum Likelihood estimator $\taut/n$,
+$\yn$ is a weighted average of the prior parameter $\yz$ and the maximum likelihood (ML) estimator $\taut/n$,
 with weights $\nz$ and $n$, respectively.
@@
 
-%In terms of canonical parameters $\nkz$ and $\ykz$, we assume $\lambda_k \mid \nkz,\ykz \sim \ig(\nkz + 1, \nkz\ykz)$.
+However, the weighted average structure for $\yn$
+is behind the problematic behaviour in case of prior-data conflict.
+Assume that from expert knowledge we expect
+to have a mean component lifetime of 9 weeks.
+Using \eqref{eq:lambdainterpret}, with $\beta=2$ we obtain $\yz = 103.13$.
+We choose $\nz = 2$, so our prior guess for the mean component lifetime
+counts like having two observations with this mean.
+If we now have a sample of two observations
+with surprisingly early failure times $t_1 = 1$ and $t_2 = 2$,
+using \eqref{eq:ig-update} we get $\nfun{2} = 4$
+and $\yfun{2} = \frac{1}{4}(2 \cdot 103.13 + 1^2 + 2^2) = 52.82$,
+so our posterior expectation for the scale parameter $\lambda$ is $52.82$,
+equivalent to a mean component lifetime of $6.44$ weeks.
+The posterior standard deviation (sd) for $\lambda$ is $60.99$.
+Compared to the prior standard deviation of $145.85$,
+the posterior expresses now more confidence that mean lifetimes are around $\yfun{2} = 52.82$
+than the prior had about $\yz = 103.13$.
+This irritating conclusion is illustrated in Figure~\ref{fig:weibull-pdc};
+the posterior cdf is shifted halfway towards the values for $\lambda$
+that the two observations suggest
+(the ML estimator for $\lambda$ would be $2.5$),
+and is steeper than the prior (so the pdf is more pointed),
+thus conveying a false sense of certainty about $\lambda$.%
+\footnote{This is a general problem in Bayesian analysis with canonical conjugate priors.
+For such priors, the same update formula \eqref{eq:ig-update} applies,
+and so conflict is averaged out, for details see \citeN{Walter2009a} and \citeN[\S 3.1.4 and \S A.1.2]{diss}.}
+We would obtain almost the same %values of $\nfun{2}$ and $\yfun{2}$, and so the same 
+posterior distribution
+if we had assumed the mean component lifetime to be 7 weeks (so $\yz = 62.39$),
+and observed lifetimes $t_1 = 6$, $t_2 = 7$ in line with our expectations.
+It seems unreasonable to make the same probability statements on component lifetimes in these two fundamentally different scenarios.
+
+\begin{figure}
+\includegraphics[width=0.48\textwidth]{fig1font}
+\caption{Prior and posterior cdf for $\lambda$ given surprising observations;
+the conflict between prior assumptions and data is averaged out,
+with a more pointed posterior giving a false sense of certainty.}
+\label{fig:weibull-pdc}
+\end{figure}
 

### 2016-07-13 figure1.R

@@ -1,0 +1,63 @@
+# --------------------------------------------------------------------------- #
+# ASCE-ASME paper - code for Fig 1
+# --------------------------------------------------------------------------- #
+
+source("weibull-sys-functions.R")
+source("plotdefs.R")
+
+# example for Fig 1: assume mean ft = 9
+k <- 2
+y0 <- failuretolambda(9,k)
+n0 <- 2
+t1 <- 1
+t2 <- 2
+
+n2 <- n0 + 2
+y2 <- (n0*y0 + t1^k + t2^k)/n2
+y2
+
+eft2 <- lambdatofailure(y2,k)
+eft2
+
+invgammavar <- function(n0, y0)
+  y0^2/(1-1/n0)
+invgammasd <- function(n0, y0)
+  sqrt(y0^2/(1-1/n0))
+
+invgammavar(n2, y2)
+invgammasd(n2, y2)
+invgammasd(n0, y0)
+
+(2*failuretolambda(7) + 6^2 + 7^2)/4
+
+# inverse gamma pdf and cdf with canonical parameters n0 and y0
+cdinvgamma <- function(x, n0, y0, ...)
+  dinvgamma(x, shape = n0+1, scale = n0*y0, ...)
+
+cpinvgamma <- function(x, n0, y0, ...)
+  pinvgamma(x, shape = n0+1, scale = n0*y0, ...)
+
+xseq <- seq(0.1, 200, length.out = 300)
+
+par(mar=c(3,3,1,1)+0.1)
+plot(xseq, cdinvgamma(xseq, n2, y2), type="l", xlab="", ylab="")
+mtext(expression(lambda), 1, 2)
+mtext(expression(p(lambda)), 2, 2)
+lines(xseq, cdinvgamma(xseq, n0, y0), lty=2)
+legend("topright", legend = c("prior", "posterior"), lty = c(2,1),
+       inset = 0.02)
+#title(main = "Prior and posterior densities")
+
+#setEPS()
+#postscript("fig1.eps",width=5,height=3)
+pdf("fig1.pdf",width=5,height=3)
+par(mar=c(3,3,1,1)+0.1)
+plot(xseq, cpinvgamma(xseq, n2, y2), type="l", xlab="", ylab="", col = "blue")
+mtext(expression(lambda), 1, 2)
+mtext(expression(F(lambda)), 2, 2)
[…]

### 2016-07-13 plotdefs.R

@@ -1,0 +1,11 @@
+# --------------------------------------------------------------------------- #
+# ASCE-ASME paper - plot definitions
+# --------------------------------------------------------------------------- #
+
+bottomlegend <- theme(legend.position = 'bottom', legend.direction = 'horizontal', legend.title = element_blank())
+rightlegend <- theme(legend.title = element_blank())
+ijarcols <- c("#b2df8a", "#1f78b4")
+ijarcol <- scale_colour_manual(values = ijarcols)
+ijarfill <- scale_fill_manual(values = ijarcols)
+
+#

### 2016-07-13 weibull-sys-functions.R

@@ -1,0 +1,346 @@
+###############################################################################
+#       Functions to calculate and plot sets of reliability curves            #
+#       for systems consisting of Weibull componentswith fixed shape          #
+###############################################################################
+
+# provides dinvgamma(x, shape, scale) where shape = alpha and scale = beta
+library(actuar)
+library(luck)
+library(ReliabilityTheory)
+library(ggplot2)
+library(reshape2)
+
+# translate lambda parameter of weibull to expected failure time
+# lambda - scale parameter of weibull
+# beta   - shape parameter of weibull
+lambdatofailure <- function(lambda, beta = 2){
+  lambda^(1/beta) * gamma(1 + 1/beta)
+}
+
+# translate failure time to lambda parameter of weibull
+# ft   - expected failure time
+# beta - shape parameter of weibull
+failuretolambda <- function(ft, beta = 2){
+  (ft/gamma(1 + 1/beta))^beta
+}
+
+# inverse gamma pdf and cdf with canonical parameters n0 and y0
+cdinvgamma <- function(x, n0, y0, ...)
+  dinvgamma(x, shape = n0+1, scale = n0*y0, ...)
+
+cpinvgamma <- function(x, n0, y0, ...)
+  pinvgamma(x, shape = n0+1, scale = n0*y0, ...)
+
+# function to calculate P(C_t = l | n^(0), y^(0), data),
+# the posterior predictive probability that l components function at time t
+# in the system observed until t_now (notion "of type k" dropped here)
+# this implements (20)
+# n0y0    pair c(n0,y0) of prior parameters
+# t       time t for which to calculate P(C_t), t > t_now
+# l       number of functioning components, \in {0, 1, ..., n-e}
+# n       number of components in the system
+# tnow    time until the system is observed
+# fts     vector of length e giving the observed failure times,
+#         or NULL if no failures observed
+# kappa   fixed weibull shape parameter
+# prior   whether the prior predictive should be calculated,
+#         when FALSE, fts is ignored 
[…]

### 2016-07-13 figure1.R
fig1 in ggplot, rest of sec 2

@@ -6,17 +6,17 @@ source("weibull-sys-functions.R")
 source("plotdefs.R")
 
 # example for Fig 1: assume mean ft = 9
-k <- 2
-y0 <- failuretolambda(9,k)
+beta <- 2
+y0 <- failuretolambda(9, beta)
 n0 <- 2
 t1 <- 1
 t2 <- 2
 
 n2 <- n0 + 2
-y2 <- (n0*y0 + t1^k + t2^k)/n2
+y2 <- (n0*y0 + t1^beta + t2^beta)/n2
 y2
 
-eft2 <- lambdatofailure(y2,k)
+eft2 <- lambdatofailure(y2, beta)
 eft2
 
 invgammavar <- function(n0, y0)
@@ -28,36 +28,21 @@ invgammavar(n2, y2)
 invgammasd(n2, y2)
 invgammasd(n0, y0)
 
+failuretolambda(7)
 (2*failuretolambda(7) + 6^2 + 7^2)/4
 
-# inverse gamma pdf and cdf with canonical parameters n0 and y0
-cdinvgamma <- function(x, n0, y0, ...)
-  dinvgamma(x, shape = n0+1, scale = n0*y0, ...)
-
-cpinvgamma <- function(x, n0, y0, ...)
-  pinvgamma(x, shape = n0+1, scale = n0*y0, ...)
-
+# the plot
 xseq <- seq(0.1, 200, length.out = 300)
-
-par(mar=c(3,3,1,1)+0.1)
-plot(xseq, cdinvgamma(xseq, n2, y2), type="l", xlab="", ylab="")
-mtext(expression(lambda), 1, 2)
-mtext(expression(p(lambda)), 2, 2)
-lines(xseq, cdinvgamma(xseq, n0, y0), lty=2)
-legend("topright", legend = c("prior", "posterior"), lty = c(2,1),
-       inset = 0.02)
-#title(main = "Prior and posterior densities")
-
+fig1df <- data.frame(x = rep(xseq, 2),
+                     y = c(cpinvgamma(xseq, n0, y0), cpinvgamma(xseq, n2, y2)),
+                     p = factor(rep(c("Prior", "Posterior"), each = length(xseq)),
+                                levels = c("Prior", "Posterior")))
+fig1 <- ggplot(fig1df, aes(x=x)) + geom_line(aes(y=y, group=p, colour=p)) + ylim(0, 1) + 
[…]

### 2016-07-13 weibull-sys-functions.R

@@ -42,10 +42,10 @@ cpinvgamma <- function(x, n0, y0, ...)
 # tnow    time until the system is observed
 # fts     vector of length e giving the observed failure times,
 #         or NULL if no failures observed
-# kappa   fixed weibull shape parameter
+# beta    fixed weibull shape parameter
 # prior   whether the prior predictive should be calculated,
 #         when FALSE, fts is ignored 
-postpredC <- function(n0y0, kappa, n, fts, tnow, t, l, prior = FALSE){
+postpredC <- function(n0y0, beta, n, fts, tnow, t, l, prior = FALSE){
   if (t < tnow)
     stop("t must be larger than tnow")
   if(!prior){
@@ -59,29 +59,26 @@ postpredC <- function(n0y0, kappa, n, fts, tnow, t, l, prior = FALSE){
     stop("l can be at most n-e")
   nn <- n0y0[1] + e
   if(!prior)
-    nnyn <- n0y0[1]*n0y0[2] + (n-e)*tnow + sum(fts^kappa)
+    nnyn <- n0y0[1]*n0y0[2] + (n-e)*tnow + sum(fts^beta)
   else
     nnyn <- n0y0[1]*n0y0[2]
   j <- seq(0, n-e-l)
-  choose(n-e, l) * sum( (-1)^j * choose(n-e-l, j) * (nnyn/(nnyn + (l+j)*(t^kappa - tnow^kappa)))^(nn + 1))
+  choose(n-e, l) * sum( (-1)^j * choose(n-e-l, j) * (nnyn/(nnyn + (l+j)*(t^beta - tnow^beta)))^(nn + 1))
 }
 
 # calculates the probability mass function for C_t
-postpredCpmf <- function(n0y0, kappa, n, fts, tnow, t, prior = FALSE){
+postpredCpmf <- function(n0y0, beta, n, fts, tnow, t, prior = FALSE){
   l <- seq(0, n-length(fts))
   res <- numeric(length(l))
-  for (i in l) res[i+1] <- postpredC(n0y0, kappa, n, fts, tnow, t, i, prior = prior)
+  for (i in l) res[i+1] <- postpredC(n0y0, beta, n, fts, tnow, t, i, prior = prior)
   res <- array(res)
   dimnames(res)[[1]] <- l
   res
 }
 
[…]

### 2016-07-14 asce-paper.tex
fig1 in ggplot, rest of sec 2
ref to Frank paper RESS 2016
densities f without index
sec 3 with fig 2

@@
-\documentclass[Journal,SectionNumbers,SingleSpace]{ascelike}
+\documentclass[Journal,SectionNumbers,SingleSpace,InsideFigs]{ascelike}
 
-\usepackage{subfigure}
-\usepackage{epsfig}
+%\usepackage{subfigure}
+%\usepackage{epsfig}
 %\usepackage{timesmt}
@@
 \begin{document}
-\title{ROBUST REMAINING USEFUL LIFE FOR COMPLEX SYSTEMS\\ or\\ ROBUST BAYESIAN RELIABILITY FOR COMPLEX SYSTEMS\\ or \ldots}
+\title{ROBUST BAYESIAN RELIABILITY FOR COMPLEX SYSTEMS\\ or \ldots}
 
@@
 \begin{align}
-f_k(t_i^k \mid \lambda_k) &= \frac{\beta_k}{\lambda_k} (t_i^k)^{\beta_k-1} e^{-\frac{(t_i^k)^{\beta_k-1}}{\lambda_k}}\,, \\
-F_k(t_i^k \mid \lambda_k) &= 1 - e^{-\frac{(t_i^k)^{\beta_k}}{\lambda_k}} = P(T_i^k \leq t_i^k \mid \lambda_k)\,,
+f(t_i^k \mid \lambda_k) &= \frac{\beta_k}{\lambda_k} (t_i^k)^{\beta_k-1} e^{-\frac{(t_i^k)^{\beta_k-1}}{\lambda_k}}\,, \\
+F(t_i^k \mid \lambda_k) &= 1 - e^{-\frac{(t_i^k)^{\beta_k}}{\lambda_k}} = P(T_i^k \leq t_i^k \mid \lambda_k)\,,
 \end{align}
@@
 \begin{align}
-f_{\lambda_k}(\lambda_k\mid a_k,b_k) &= \frac{(b_k)^{a_k}}{\Gamma(a_k)} \lambda_k^{-a_k -1} e^{-\frac{b_k}{\lambda_k}}
+f(\lambda_k\mid a_k,b_k) &= \frac{(b_k)^{a_k}}{\Gamma(a_k)} \lambda_k^{-a_k -1} e^{-\frac{b_k}{\lambda_k}}
 \end{align}
@@
 It seems unreasonable to make the same probability statements on component lifetimes in these two fundamentally different scenarios.
-
+%
+%\iffalse
 \begin{figure}
-\includegraphics[width=0.48\textwidth]{fig1font}
+\centering
+\includegraphics[width=0.8\textwidth]{fig1}
 \caption{Prior and posterior cdf for $\lambda$ given surprising observations;
@@
 \end{figure}
+%\fi
 
@@
 
-Set of priors $\MkZ$ defined by $(\nkz,\ykz) \in \PkZ = [\nkzl,\nkzu] \times [\ykzl,\ykzu]$.
+Despite this issue of ignoring prior-data conflict,
+the tractability of the update step
+(the posterior is again a parametric distribution)
+is a very attractive feature of the conjugate setting.
+As was shown by \citeN{Walter2009a} (see also \citeNP{diss}, \S 3.1),
+it is possible to retain tractability and to have a meaningful reaction to prior-data conflict
+when using sets of priors generated by varying both $\nz$ and $\yz$.
+Then, the magnitude of the set of posteriors,
+and with it the precision of posterior probability statements,
+will be sensitive to the degree of prior-data conflict,
+i.e.\ leading to more cautious probability statements when prior-data conflict occurs.
 
-***illustrate prior-data conflict similar to ESREL paper
+Instead of a single prior guess $\yz$ for the mean component lifetimes,
+we will now assume a range of prior guesses $[\yzl, \yzu]$, and also a range $[\nzl, \nzu]$ of pseudocounts,
+i.e., we now consider the set of priors
+\begin{linenomath*}
+\begin{align}
+\MZ := \{ f(\lambda\mid\nz,\yz) \mid \nz \in [\nzl, \nzu], \yz \in [\yzl, \yzu] \}
+\label{eq:setofpriors}
+\end{align}
+\end{linenomath*}
+to express our prior knowledge about component lifetimes.
+Each of the priors $f(\lambda\mid\nz,\yz)$ is then updated to the posterior
+$f(\lambda\mid\nz,\yz,\vec{t}) = f(\lambda\mid\nn,\yn)$
+by using \eqref{eq:ig-update},
+such that the set of posteriors $\MN$ can be written as
+$\MN = \{ f(\lambda\mid\nn,\yn) \mid \nz \in [\nzl, \nzu], \yz \in [\yzl, \yzu] \}$.
+This procedure of using Bayes' Rule element by element
+is seen as self-evident in the robust Bayesian literature,
+but can be formally justified as being \emph{coherent}
+(a self-consistency property)
+in the framework of imprecise probability, where it is known as
+\emph{Generalized Bayes' Rule} \cite[\S 6.4]{1991:walley}.
 
-\section{Robust RUL Estimation for Complex Systems via the Survival Signature}
+Technically, it is crucial to consider a range of pseudocounts $[\nzl, \nzu]$
+along with the range of prior guesses $[\yzl, \yzu]$,
+as only then $\taut/n \not\in [\yzl, \yzu]$
+leads to the set of posteriors being larger
+and hence reflecting prior-data conflict.
+
+Continuing the example from Section~\ref{sec:weibull} and Figure~\ref{fig:weibull-pdc},
+assume now for the mean component lifetimes the range 9 to 11 weeks,
+this corresponds to $[\yzl,\yzu] = [103.13, 154.06]$.
+We also choose $[\nzl,\nzu] =[2, 5]$,
+so we value our prior information as equivalent to having seen two to five observations.
+Compare now the set of posteriors obtained from observing
+$t_1 = 1$, $t_2 = 2$ (as before), see Figure~\ref{fig:setofpost-pdc-nopdc} (left),
+and $t_1 = 10$, $t_2 = 11$, see Figure~\ref{fig:setofpost-pdc-nopdc} (right).
+We now have a clear difference between the two scenarios of
+observations in line with expectations and observations in conflict.
+In the prior-data conflict case, the set of posteriors (blue)
+is shifted towards the left, but has about the same size as the set of priors (yellow),
+and so posterior quantification of reliability has the same precision,
+despite having seen two observations.
+Instead, in the no conflict case, the set of posteriors is smaller than the set of priors,
+such that the two observations have increased the precision of reliability statements.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{fig2}
+\caption{Set of prior and posterior cdfs for $\lambda$ for two surprising observations $t_1 = 1$, $t_2 = 2$ (left)
+and two unsurprising observations $t_1 = 10$, $t_2 = 11$ (right).}
+\label{fig:setofpost-pdc-nopdc}
+\end{figure}
+
+As each posterior in $\MN$ corresponds to a predictive distribution for $\Tsys$,
+we will have a set of reliability functions $\Rsys(t)$.
+The derivation of $\Rsys(t)$ for systems with $K$ component types and arbitrary layout
+will be given in Section~\ref{sec:robrel} below.
+This will include, in contrast to previous studies using sets of priors of type 
+\eqref{eq:setofpriors}, the treatment of censored observations.
+More specifically, we consider the case of \emph{non-informative right censoring},
+where the censoring process is independent of the failure process.
+
+\section{Robust Reliability for Complex Systems via the Survival Signature}
+\label{sec:robrel}
+
+***Set of priors $\MkZ$ defined by $(\nkz,\ykz) \in \PkZ = [\nkzl,\nkzu] \times [\ykzl,\ykzu]$.
 
@@
 
-*** cf paper from Frank 20ys ago (?)
+*** cf paper from Frank \cite{1996:coolen::cens}
 

### 2016-07-14 weibull-sys-functions.R

@@ -31,6 +31,12 @@ cdinvgamma <- function(x, n0, y0, ...)
 cpinvgamma <- function(x, n0, y0, ...)
   pinvgamma(x, shape = n0+1, scale = n0*y0, ...)
 
+cpigforoptim <- function(ny, t, ...)
+  cpinvgamma(t, ny[1], ny[2], ...)
+
+cpigfornoptim <- function(n, y, t, ...)
+  cpinvgamma(t, n, y, ...)
+
 # function to calculate P(C_t = l | n^(0), y^(0), data),
 # the posterior predictive probability that l components function at time t
 # in the system observed until t_now (notion "of type k" dropped here)

### 2016-07-15 asce-paper.tex
organizing sec 4

@@
 
-***Set of priors $\MkZ$ defined by $(\nkz,\ykz) \in \PkZ = [\nkzl,\nkzu] \times [\ykzl,\ykzu]$.
+We now consider a system of arbitrary layout,
+consisting of components of $K$ types.
+This system is observed until time $\tnow$,
+leading to censored observations,
+and we will explain in Section~\ref{sec:lambdawithcens}
+how the scale parameter $\lambda_k$ for component type $k$
+can be estimated in this situation.
+%
+Section~\ref{sec:sysrelwithsurvsign} describes then
+how the system relibility function can be efficiently obtained using the survival signature.
+%
+For this, we need the posterior predictive distribution
+of the number of components function at times $t > \tnow$,
+which we will derive in Section~\ref{sec:postpred}.
+%
+Finally, in Section~\ref{sec:optimize} we describe how
+the lower and upper bound for the system reliability function
+are obtained when prior parameters $(\nkz,\ykz)$
+vary in sets $\PkZ = [\nkzl,\nkzu] \times [\ykzl,\ykzu]$,
+defining sets $\MkZ$ of prior distributions over $\lambda_k$,
+as introduced in Section~\ref{sec:modforsurpr}.
 
-\subsection{Right-censored Lifetimes}
+\subsection{Bayesian Estimation of Component Scale Parameter with Right-censored Lifetimes}
+\label{sec:lambdawithcens}
 
@@
 introduce sets of observed and censored?
-
-\subsection{Bayesian Estimation of Component Scale Parameter}
 
@@
 
-\subsection{RUL using the Survival Signature}
+\subsection{System Reliability using the Survival Signature}
+\label{sec:sysrelwithsurvsign}
 
@@
 \subsection{Posterior Predictive Distribution}
+\label{sec:postpred}
 
@@
 \subsection{Optimizing over Sets of Parameters}
+\label{sec:optimize}
+
+***Set of priors $\MkZ$ defined by $(\nkz,\ykz) \in \PkZ = [\nkzl,\nkzu] \times [\ykzl,\ykzu]$.
 
@@
 
-\section{elicitation}
+\section{Elicitation of prior parameter sets}
 
@@
 *** cf paper from Frank \cite{1996:coolen::cens}
+
+\section{Examples}
+
+\section{Concluding Remarks}
 

### 2016-07-15 asce-paper.tex
start sec 4.1

@@
 
-Observing a one of a kind system with $n_k$ components of type $k$ running until $\tnow$,
-where $e_k$ components have failed by $\tnow$, and $n_k - e_k$ components still function:
+Consider observing a prototype system until $\tnow$,
+where the system has $K$ different types of components,
+and for each type $k$ there are $n_k$ components in the system.
+Denoting the number of type $k$ components that have failed by $\tnow$ by $e_k$,
+there are $n_k - e_k$ components still functioning at $\tnow$.
+We denote the corresponding vector of observations by
 \begin{linenomath*}
@@
 \mbf{t}^k_{e_k;n_k} &= \big( \underbrace{t^k_1, \ldots, t^k_{e_k}}_{e_k \text{failure times}},
-                             \underbrace{\tpnow, \ldots, \tpnow}_{n_k-e_k \text{censored obs.}} \big)
+                             \underbrace{\tpnow, \ldots, \tpnow}_{n_k-e_k \text{censored obs.}} \big)\,,
 \end{align}
 \end{linenomath*}
+where $t^+$ indicates a censored observation.
 

### 2016-07-18 asce-paper.tex
Sec 4.1

@@
 This system is observed until time $\tnow$,
-leading to censored observations,
+leading to censored observation of lifetimes of components within the system,
 and we will explain in Section~\ref{sec:lambdawithcens}
@@
 Section~\ref{sec:sysrelwithsurvsign} describes then
-how the system relibility function can be efficiently obtained using the survival signature.
+how the system reliability function can be efficiently obtained using the survival signature.
 %
@@
 \end{linenomath*}
-where $t^+$ indicates a censored observation.
+where $t^+$ indicates a right-censored observation.
+%
+%***change to general right-censoring? So $n_k-e_k \to c_k$, $e_k+c_k=n_k$,
+%introduce sets of observed and censored?
 
-***change to general right-censoring? So $n_k-e_k \to c_k$, $e_k+c_k=n_k$,
-introduce sets of observed and censored?
-
-Posterior:
+According to Bayes' rule, multiplying the prior density and the likelihood
+(which accounts for right-censored observations through the cdf terms)
+gives a term proportional to the density of the posterior distribution for $\lambda_k$:
 \begin{linenomath*}
 \begin{align}
-f_{\lambda_k\mid\ldots}(\lambda_k\mid\nkz,\ykz,\mbf{t}^k_{e_k;n_k})
- &\propto f_{\lambda_k}(\lambda_k)
-          \big[ 1- F_k(\tnow\mid\lambda_k) \big]^{n_k-e_k}
-          \prod_{i=1}^{e_k} f_k(t_i^k \mid \lambda_k) 
+%f_{\lambda_k\mid\ldots}(\lambda_k\mid\nkz,\ykz,\mbf{t}^k_{e_k;n_k})
+% &\propto f_{\lambda_k}(\lambda_k)
+%          \big[ 1- F_k(\tnow\mid\lambda_k) \big]^{n_k-e_k}
+%          \prod_{i=1}^{e_k} f_k(t_i^k \mid \lambda_k) 
+f(\lambda_k\mid\nkz,\ykz,\mbf{t}^k_{e_k;n_k})
+ &\propto f(\lambda_k)
+          \big[ 1- F(\tnow\mid\lambda_k) \big]^{n_k-e_k}
+          \prod_{i=1}^{e_k} f(t_i^k \mid \lambda_k) 
 \end{align}
 \end{linenomath*}
-and so $\lambda_k\mid\nkz,\ykz,\mbf{t}^k_{e_k;n_k} \sim \ig(\nkn + 1, \nkn\ykn)$, where
+Conjugacy is preserved and we get 
+$\lambda_k\mid\nkz,\ykz,\mbf{t}^k_{e_k;n_k} \sim \ig(\nkn + 1, \nkn\ykn)$, where
 \begin{linenomath*}
@@
 \nkn + 1 &= \nkz + e_k + 1 \\
-\nkn\ykn &= \nkz\ykz + (n_k-e_k) \tnow^\kappa + \sum_{i=1}^{e_k} (t_i^k)^\kappa
+\nkn\ykn &= \nkz\ykz + (n_k-e_k) (\tnow)^\beta + \sum_{i=1}^{e_k} (t_i^k)^\beta
 \end{align}
 \end{linenomath*}
-so the posterior expectation for $\lambda$ is
-\begin{linenomath*}
-\begin{align}
-\E[\lambda_k\mid\nkn,\ykn] &= \ykn
-                            = \frac{\nkz}{\nkz + e_k} \ykz +
-                              \frac{e_k}{\nkz + e_k} \cdot \Big[\frac{n_k-e_k}{e_k} \tnow^\kappa + \frac{1}{e_k}\sum_{i=1}^{e_k} (t_i^k)^\kappa \Big]
-\end{align}
-\end{linenomath*}
+are the updated parameters of the inverse gamma distribution.
+%The posterior expectation for $\lambda_k$ is
+%\begin{linenomath*}
+%\begin{align}
+%\E[\lambda_k\mid\nkn,\ykn] &= \ykn
+%                            = \frac{\nkz}{\nkz + e_k} \ykz +
+%                              \frac{e_k}{\nkz + e_k} \cdot \Big[\frac{n_k-e_k}{e_k} (\tnow)^\beta 
+%                                                                    + \frac{1}{e_k} \sum_{i=1}^{e_k} (t_i^k)^\beta \Big]
+%\end{align}
+%\end{linenomath*}
 
@@
 
+***from poster or similar
+
 \section{Concluding Remarks}

### 2016-07-18 asce-paper.tex
Sec 4.3

@@
 \begin{align}
+\label{eq:weibulldens}
 f(t_i^k \mid \lambda_k) &= \frac{\beta_k}{\lambda_k} (t_i^k)^{\beta_k-1} e^{-\frac{(t_i^k)^{\beta_k-1}}{\lambda_k}}\,, \\
+\label{eq:weibullcdf}
 F(t_i^k \mid \lambda_k) &= 1 - e^{-\frac{(t_i^k)^{\beta_k}}{\lambda_k}} = P(T_i^k \leq t_i^k \mid \lambda_k)\,,
@@
 f(\lambda_k\mid a_k,b_k) &= \frac{(b_k)^{a_k}}{\Gamma(a_k)} \lambda_k^{-a_k -1} e^{-\frac{b_k}{\lambda_k}}
+\label{eq:ig-def}
 \end{align}
@@
 \begin{align}
-\mbf{t}^k_{e_k;n_k} &= \big( \underbrace{t^k_1, \ldots, t^k_{e_k}}_{e_k \text{failure times}},
+\vec{t}^k_{e_k;n_k} &= \big( \underbrace{t^k_1, \ldots, t^k_{e_k}}_{e_k \text{failure times}},
                              \underbrace{\tpnow, \ldots, \tpnow}_{n_k-e_k \text{censored obs.}} \big)\,,
@@
 %          \prod_{i=1}^{e_k} f_k(t_i^k \mid \lambda_k) 
-f(\lambda_k\mid\nkz,\ykz,\mbf{t}^k_{e_k;n_k})
+f(\lambda_k\mid\nkz,\ykz,\vec{t}^k_{e_k;n_k})
  &\propto f(\lambda_k)
@@
 Conjugacy is preserved and we get 
-$\lambda_k\mid\nkz,\ykz,\mbf{t}^k_{e_k;n_k} \sim \ig(\nkn + 1, \nkn\ykn)$, where
+$\lambda_k\mid\nkz,\ykz,\vec{t}^k_{e_k;n_k} \sim \ig(\nkn + 1, \nkn\ykn)$, where
 \begin{linenomath*}
@@
 
-System survival calculated by %(see Risk Analysis paper eq. (7))
+The structure of complex systems can be visualized by reliability block diagrams,
+an example is given in Figure~***.
+Components are represented by boxes or nodes,
+and the system works when a path from the left end to the right exists
+which passes only through working components.
+In a system with $n$ components, the state of the components can be expressed by the state vector
+$\vec{x} = (x_1,x_2,\ldots,x_n) \in \{0,1\}^n$, with $x_i=1$ if the $i$th component functions 
+and $x_i=0$ if not.
+The structure function $\phi : \{0,1\}^n \rightarrow \{0,1\}$, defined for all possible $\vec{x}$, takes 
+the value 1 if the system functions and 0 if the system does not function for state vector $\vec{x}$
+\cite{BP75}.
+Most real-life systems are coherent,
+which means that $\phi(\vec{x})$ is non-decreasing in any of the components of $\vec{x}$,
+so system functioning cannot be improved by worse performance of one or more of its components.
+Furthermore, one can usually assume that $\phi(0, \ldots, 0) = 0$ and $\phi(1, \ldots, 1) = 1$.
+
+The survival signature \cite{2012:survsign} is a summary of the structure function
+for systems with $K$ groups of exchangeable components.
+Denoted by $\Phi(l_1,\ldots,l_K)$, with $l_k=0,1,\ldots,n_k$ for $k=1,\ldots,K$,
+it is defined as the probability for the event that the system functions
+given that precisely $l_k$ of its $n_k$ components of type $k$ function, for each $k\in \{1,\ldots,K\}$.
+Essentially, this creates a $K$-dimensional partition for the event $\Tsys > t$,
+such that $\Rsys(t) = P(\Tsys > t)$ can be calculated using the law of total probability,
+%System survival calculated by %(see Risk Analysis paper eq. (7))
 \begin{linenomath*}
 \begin{align}
-P(\Tsys > t) &= \sum_{l_1=0}^{n_1} \cdots \sum_{l_K=0}^{n_K} \Phi(l_1,\ldots,l_K) P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \\
-\intertext{ and assuming components of different types are independent,}
-             &= \sum_{l_1=0}^{n_1} \cdots \sum_{l_K=0}^{n_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K P(C^k_t = l_k)
+P(\Tsys > t) &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K)
+                                                                                  P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \nonumber\\
+             &= \sum_{l_1=0}^{n_1} \cdots \sum_{l_K=0}^{n_K} \Phi(l_1,\ldots,l_K) P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \nonumber\\
+%\intertext{ and assuming components of different types are independent,}
+             &= \sum_{l_1=0}^{n_1} \cdots \sum_{l_K=0}^{n_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K P(C^k_t = l_k)\,,
+\label{eq:sysrel-survsign}
 \end{align}
 \end{linenomath*}
-where the survival signature $\Phi(l_1,\ldots,l_K)$ is non-decreasing in each $l_k$ for coherent systems,
-and $P(C^k_t = l_k)$ is the (predictive) probability that exactly $l_k$ components of type $k$ function at time $t$.
-
-A priori, we have, for $l_k = 0,1,\ldots, n_k$,
-\begin{linenomath*}
-\begin{align}
-P(C^k_t = l_k\mid\nkz,\ykz)
- &= { n_k \choose l_k} \int [F_k(t \mid\lambda_k)]^{n_k-l_k}
-                        [1 - F_k(t \mid\lambda_k)]^{l_k} f_{\lambda_k}(\lambda_k\mid\nkz,\ykz) \dd \lambda_k
-\end{align}
-\end{linenomath*}
-under the assumption that components of the same type are independent given $\lambda_k$.
+where $P(C^k_t = l_k)$ is the (predictive) probability that exactly $l_k$ components of type $k$ function at time $t$,
+and the last equality holds as we assume that components of different types are independent.
+Note that for coherent systems,
+the survival signature $\Phi(l_1,\ldots,l_K)$ is non-decreasing in each $l_k$.
+%
+%A priori, we have, for $l_k = 0,1,\ldots, n_k$,
+%\begin{linenomath*}
+%\begin{align}
+%P(C^k_t = l_k\mid\nkz,\ykz)
+% &= { n_k \choose l_k} \int [F_k(t \mid\lambda_k)]^{n_k-l_k}
+%                        [1 - F_k(t \mid\lambda_k)]^{l_k} f_{\lambda_k}(\lambda_k\mid\nkz,\ykz) \dd \lambda_k
+%\end{align}
+%\end{linenomath*}
+%under the assumption that components of the same type are independent given $\lambda_k$.
 
@@
 
-For the situation with the system observed until $\tnow$, with data $\mbf{t}^k_{e_k;n_k}$,
-we need the posterior predictive probability $P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$.
-
-For $l_k > n_k - e_k$, we must have $P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k}) = 0$,
-as at most $n_k - e_k$ components can function for $t > \tnow$.
-
+In calculating the system reliability using \eqref{eq:sysrel-survsign},
+the component-specific predictive probabilities $P(C^k_t = l_k)$
+need to use all information available at time $\tnow$,
+which, in the Bayesian framework,
+are given by the posterior predictive distribution 
+$P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$, $l_k = 0, 1, \ldots, n_k-e_k$. %$k=1,\ldots, K$.
+(Remember that $e_k$ type $k$ components have failed by $\tnow$,
+such that there are at most $n_k-e_k$ working components at time $\tnow$.)
 %(Should one work with the subsystem consisting only of the non-failed $n_k - e_k$ components?)\\
-
-A posteriori, we have, for $l_k = 0,1,\ldots, n_k - e_k$,
+This posterior predictive distribution is obtained as
 \begin{linenomath*}
 \begin{align}
-P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})
- &= { n_k - e_k \choose l_k} \int [P_k(T \leq t \mid T > \tnow, \lambda_k)]^{n_k - e_k - l_k} \times \\ & \hspace*{2ex}
-                              [1 - P_k(T \leq t \mid T > \tnow, \lambda_k)]^{l_k}
-    f_{\lambda_k\mid\ldots}(\lambda_k\mid\nkz,\ykz,\mbf{t}^k_{e_k;n_k}) \dd \lambda_k
+\lefteqn{%
+P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})}\hspace*{5ex} \nonumber\\  %
+ &= { n_k - e_k \choose l_k} \int \big[P(T^k >    t \mid T^k > \tnow, \lambda_k)\big]^{l_k} \times \nonumber\\ & \hspace*{17ex}
+                                  \big[P(T^k \leq t \mid T^k > \tnow, \lambda_k)\big]^{n_k - e_k - l_k}
+    f(\lambda_k\mid\nkz,\ykz,\vec{t}^k_{e_k;n_k}) \dd \lambda_k
+\label{eq:postpredtnow}
+\end{align}
+\end{linenomath*}
+%
+Now, by the Weibull assumption \eqref{eq:weibullcdf}, we have
+\begin{linenomath*}
+\begin{align}
+P(T^k \leq t \mid T^k > \tnow, \lambda_k)
+ &= \frac{P(\tnow < T^k \leq t \mid\lambda_k)}{P(T^k > \tnow \mid \lambda_k)} \nonumber\\
+ &= \frac{F(t\mid\lambda_k) - F(\tnow\mid\lambda_k)}{1-F(\tnow\mid\lambda_k)} 
+% = \frac{e^{-\frac{(\tnow)^{\beta_k}}{\lambda_k}} - e^{-\frac{t^{\beta_k}}{\lambda_k}}}{e^{-\frac{(\tnow)^{\beta_k}}{\lambda_k}}}
+  = 1 - e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\,.
+\end{align}
+\end{linenomath*}
+%
+With this and the posterior \eqref{eq:ig-update-alpha} substituted into \eqref{eq:postpredtnow}, we get
+\begin{linenomath*}
+\begin{align}
+\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})}\hspace*{5ex} \\
+ &= { n_k - e_k \choose l_k} \int \Big[    e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\Big]^{l_k}
+                                  \Big[1 - e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\Big]^{n_k - e_k - l_k}\times\\&\hspace*{27ex}
+    \frac{\big(\nkn\ykn\big)^{\nkn + 1}}{\Gamma(\nkn+1)} \lambda_k^{-(\nkn + 1) - 1} e^{-\frac{\nkn\ykn}{\lambda_k}} \dd \lambda_k \\
+ &= { n_k - e_k \choose l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j { n_k - e_k - l_k \choose j} \frac{\big(\nkn\ykn\big)^{\nkn + 1}}{\Gamma(\nkn+1)} 
+    \times \\ & \hspace*{13ex}
+    \int \lambda_k^{-(\nkn + 1) - 1} \exp\Big\{-\frac{(l_k + j) (t^{\beta_k} - (\tnow)^{\beta_k}) + \nkn\ykn}{\lambda_k}\Big\} \dd \lambda_k\,.
+\end{align}
+\end{linenomath*}
+%
+The terms remaining under the integral form the core of an inverse gamma distribution \eqref{eq:ig-def}
+with parameters $\nkn + 1$ and $\nkn\ykn + (l_k + j) (t^{\beta_k} - (\tnow)^{\beta_k}))$,
+allowing us to solve the integral using the corresponding normalization constant.
+We thus have, for $l_k \in \{0,1,\ldots,n_k-e_k\}$,
+\begin{linenomath*}
+\begin{align}
+\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})} \\
+ &= { n_k - e_k \choose l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j { n_k - e_k - l_k \choose j}
+    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nkn + 1} \\
+ &= \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!}   
+    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nkn + 1} \\
+ &= \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!} \times \\ & \hspace*{10ex}  
+    \left(\frac{\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^{\beta_k} + (n_k-e_k)       (\tnow)^{\beta_k} }%
+               {\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^{\beta_k} + (n_k-e_k-l_k-j) (\tnow)^{\beta_k} + (l_k + j) t^{\beta_k} }\right)^{%
+    \nkz + e_k + 1} 
 \end{align}
@@
 
-Now,
-\begin{linenomath*}
-\begin{align}
-P_k(T \leq t \mid T > \tnow, \lambda_k)
- &= \frac{P_k(\tnow < T \leq t \mid\lambda_k)}{P_k(T > \tnow \mid \lambda_k)}
-  = \frac{F_k(t\mid\lambda_k) - F_k(\tnow\mid\lambda_k)}{1-F_k(\tnow\mid\lambda_k)} \\
- &= \frac{e^{-\frac{(\tnow)^\kappa}{\lambda_k}} - e^{-\frac{t^\kappa}{\lambda_k}}}{e^{-\frac{(\tnow)^\kappa}{\lambda_k}}}
-  = 1 - e^{-\frac{t^\kappa - (\tnow)^\kappa}{\lambda_k}}
-\end{align}
-\end{linenomath*}
+%Seen as function in $t$, we see that $t$ appears $n_k-e_k-l_k+1$ times,
+%once in each summand, in the denominator of the fraction powered to the $\nkn+1$,
+%and summands whith even $j$ are decreasing in $t$,
+%while summands whith odd $j$ are increasing in $t$.
+%Nevertheless, in total $P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$
+%must be decreasing in $t$, as the remaining $n_k-e_k$ components continue to age,
+%and so the probability that $l_k$ of them remain operational must decrease.
 
-With this and the posterior substituted in, we get
-\begin{linenomath*}
-\begin{align}
-\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})} \\
- &= { n_k - e_k \choose l_k} \int \Big[1 - e^{-\frac{t^\kappa - (\tnow)^\kappa}{\lambda_k}}\Big]^{n_k - e_k - l_k}
-                                  \Big[    e^{-\frac{t^\kappa - (\tnow)^\kappa}{\lambda_k}}\Big]^{l_k} \times \\ & \hspace*{28ex}
-    \frac{[\nkn\ykn]^{\nkn + 1}}{\Gamma(\nkn+1)} \lambda_k^{-(\nkn + 1) - 1} e^{-\frac{\nkn\ykn}{\lambda_k}} \dd \lambda_k \\
- &= { n_k - e_k \choose l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j { n_k - e_k - l_k \choose j} \frac{[\nkn\ykn]^{\nkn + 1}}{\Gamma(\nkn+1)} 
-    \times \\ & \hspace*{25ex}
-    \int \lambda_k^{-(\nkn + 1) - 1} e^{-\frac{(l_k + j) (t^\kappa - (\tnow)^\kappa) + \nkn\ykn}{\lambda_k}} \dd \lambda_k
-\end{align}
-\end{linenomath*}
-
-The terms remaining under the integral form the core of an $\ig(\nkn + 1, \nkn\ykn + (l_k + j) (t^\kappa - (\tnow)^\kappa))$,
-allowing us to solve the integral using the corresponding normalization constant.
-\begin{linenomath*}
-\begin{align}
-\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})} \\
- &= { n_k - e_k \choose l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j { n_k - e_k - l_k \choose j}
-    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) (t^\kappa - (\tnow)^\kappa)}\right)^{\nkn + 1} \\
- &= \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!}   
-    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) (t^\kappa - (\tnow)^\kappa)}\right)^{\nkn + 1} \\
- &= \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!} \times \\ & \hspace*{13ex}  
-    \left(\frac{\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^\kappa + (n_k-e_k) (\tnow)^\kappa }%
-               {\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^\kappa + (n_k-e_k-l_k-j) (\tnow)^\kappa + (l_k + j) t^\kappa }\right)^{%
-    \nkz + e_k + 1} 
-\end{align}
-\end{linenomath*}
-for $l_k \in \{0,1,\ldots,n_k-e_k\}$.
-
-We actually need to compute only those $P(C^k_t = l_k\mid \ldots)$ with $l_k$'s for which $\Phi(l_1,\ldots,l_K) > 0$.
-
-Seen as function in $t$, we see that $t$ appears $n_k-e_k-l_k+1$ times,
-once in each summand, in the denominator of the fraction powered to the $\nkn+1$,
-and summands whith even $j$ are decreasing in $t$,
-while summands whith odd $j$ are increasing in $t$.
-Nevertheless, in total $P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$
-must be decreasing in $t$, as the remaining $n_k-e_k$ components continue to age,
-and so the probability that $l_k$ of them remain operational must decrease.
+***need formal first-order stochastic dominance in $\ykz$ result for $P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$?
 
@@
 ***Set of priors $\MkZ$ defined by $(\nkz,\ykz) \in \PkZ = [\nkzl,\nkzu] \times [\ykzl,\ykzu]$.
+
+***We actually need to compute only those $P(C^k_t = l_k\mid \ldots)$ with $l_k$'s for which $\Phi(l_1,\ldots,l_K) > 0$.
 

### 2016-07-19 asce-paper.tex
Sec 4.4

@@
 \newcommand{\nkzfun}[1]{n\uz_{#1}}
+\newcommand{\nkzlfun}[1]{\ul{n}\uz_{#1}}
+\newcommand{\nkzufun}[1]{\ol{n}\uz_{#1}}
 
@@
 The structure of complex systems can be visualized by reliability block diagrams,
-an example is given in Figure~***.
+an example is given in Figure~\ref{fig:bridge-layout}.
 Components are represented by boxes or nodes,
@@
 (Remember that $e_k$ type $k$ components have failed by $\tnow$,
-such that there are at most $n_k-e_k$ working components at time $\tnow$.)
+such that there can be at most $n_k-e_k$ working components beyond time $\tnow$.)
 %(Should one work with the subsystem consisting only of the non-failed $n_k - e_k$ components?)\\
@@
 \begin{align}
-\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})}\hspace*{5ex} \\
+\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})}\hspace*{5ex} \nonumber\\
  &= { n_k - e_k \choose l_k} \int \Big[    e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\Big]^{l_k}
-                                  \Big[1 - e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\Big]^{n_k - e_k - l_k}\times\\&\hspace*{27ex}
-    \frac{\big(\nkn\ykn\big)^{\nkn + 1}}{\Gamma(\nkn+1)} \lambda_k^{-(\nkn + 1) - 1} e^{-\frac{\nkn\ykn}{\lambda_k}} \dd \lambda_k \\
+                                  \Big[1 - e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\Big]^{n_k - e_k - l_k}
+    \times \nonumber\\ & \hspace*{27ex}
+    \frac{\big(\nkn\ykn\big)^{\nkn + 1}}{\Gamma(\nkn+1)} \lambda_k^{-(\nkn + 1) - 1} e^{-\frac{\nkn\ykn}{\lambda_k}} \dd \lambda_k \nonumber\\
  &= { n_k - e_k \choose l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j { n_k - e_k - l_k \choose j} \frac{\big(\nkn\ykn\big)^{\nkn + 1}}{\Gamma(\nkn+1)} 
-    \times \\ & \hspace*{13ex}
+    \times \nonumber\\ & \hspace*{13ex}
     \int \lambda_k^{-(\nkn + 1) - 1} \exp\Big\{-\frac{(l_k + j) (t^{\beta_k} - (\tnow)^{\beta_k}) + \nkn\ykn}{\lambda_k}\Big\} \dd \lambda_k\,.
@@
 \begin{align}
-\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})} \\
+\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})} \nonumber\\
  &= { n_k - e_k \choose l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j { n_k - e_k - l_k \choose j}
-    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nkn + 1} \\
+    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nkn + 1} \nonumber\\
  &= \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!}   
-    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nkn + 1} \\
- &= \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!} \times \\ & \hspace*{10ex}  
+    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nkn + 1} \nonumber\\
+ &= \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!} \times \nonumber\\ & \hspace*{10ex}  
     \left(\frac{\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^{\beta_k} + (n_k-e_k)       (\tnow)^{\beta_k} }%
                {\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^{\beta_k} + (n_k-e_k-l_k-j) (\tnow)^{\beta_k} + (l_k + j) t^{\beta_k} }\right)^{%
-    \nkz + e_k + 1} 
+    \nkz + e_k + 1}.
+\label{eq:postpred-priorparams}
 \end{align}
 \end{linenomath*}
-
+%
+These posterior predictive probabilities can also be expressed as a cumulative probability mass function (cmf) 
+\begin{linenomath*}
+\begin{align}
+F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k}) = P(C^k_t \leq l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k}) 
+ = \sum_{j=0}^{l_k} P(C^k_t = j \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})\,.
+%F_{C^k_t}(l_k \mid \ldots) = P(C^k_t \leq l_k\mid\ldots) = \sum_{q=0}^{l_k} P(C^k_t = q\mid\ldots)\,,
+\end{align}
+\end{linenomath*}
 %Seen as function in $t$, we see that $t$ appears $n_k-e_k-l_k+1$ times,
@@
 
-***need formal first-order stochastic dominance in $\ykz$ result for $P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$?
-
 \subsection{Optimizing over Sets of Parameters}
@@
 
-***Set of priors $\MkZ$ defined by $(\nkz,\ykz) \in \PkZ = [\nkzl,\nkzu] \times [\ykzl,\ykzu]$.
-
-***We actually need to compute only those $P(C^k_t = l_k\mid \ldots)$ with $l_k$'s for which $\Phi(l_1,\ldots,l_K) > 0$.
-
-%I would think that
-%$\min / \max_{(\nkz,\ykz) \in \PkZ} P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$
-%must be solved by numeric optimization for each $k, l_k, t$ 
-%because of the alternating signs for the summands.
-%(In absolute terms, each summand is increasing in $\ykz$, but not monotone in $\nkz$.)
-
-%(Box-constraint optimization possible, e.g., with option \texttt{L-BFGS-B} of \texttt{optim} in \textbf{R}.)
-Similar to the considerations about $t$, as higher values for $\ykz$ mean higher expected lifetimes for the components,
-the larger $\ykz$, the higher the probability that many components survive
-($P(C^k_t = l_k\mid\ldots)$ high for large $l_k$)
-and, with that, the lower the probability that few or no components survive
-($P(C^k_t = l_k\mid\ldots)$ low for small $l_k$).
-
-In terms of the cumulative probability mass function (cmf) for $C^k_t$, which can be written as 
+Together with \eqref{eq:postpred-priorparams},
+\eqref{eq:sysrel-survsign} allows us to calculate the system reliability $\Rsys(t\mid t>\tnow)$
+for fixed prior parameters $(\nkz, \ykz)$, $k=1, \ldots, K$.
+In Section~\ref{sec:modforsurpr}, we argued for using sets of priors $\MZ$,
+which allow for vague and incomplete prior knowledge, and provide prior-data conflict sensitivity.
+%
+We will thus use, for each component type,
+a set of priors $\MkZ$ defined by varying $(\nkz,\ykz)$ in a prior parameter set $\PkZ = [\nkzl,\nkzu] \times [\ykzl,\ykzu]$,
+and we are interested in the bounds
+%This leads to a set of system reliability functions with the bounds
 \begin{linenomath*}
 \begin{align}
-%F_{C^k_t}(l_k \mid \nkz,\ykz, \mbf{t}^k_{e_k;n_k}) = P(C^k_t \leq l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k}) 
-% = \sum_{q=0}^{l_k} P(C^k_t = q\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})
-F_{C^k_t}(l_k \mid \ldots) = P(C^k_t \leq l_k\mid\ldots) = \sum_{q=0}^{l_k} P(C^k_t = q\mid\ldots)\,,
+\lRsys(t \mid t > \tnow) &= \min_{\PZi{1},\ldots,\PZi{K}} \Rsys\big(t \mid t > \tnow, \cup_{k=1}^K \{\PkZ, \vec{t}^k_{e_k;n_k}\}\big)\,,
+\label{eq:lrsysdef}\\
+\uRsys(t \mid t > \tnow) &= \max_{\PZi{1},\ldots,\PZi{K}} \Rsys\big(t \mid t > \tnow, \cup_{k=1}^K \{\PkZ, \vec{t}^k_{e_k;n_k}\}\big)\,,
+\label{eq:ursysdef}
 \end{align}
 \end{linenomath*}
-we therefore conclude that
-the lower cmf $\ul{F}(C^k_t = l_k\mid \ldots)$ must be obtained with the lower bounds for all $\ykz$, $k=1,\ldots,K$,
-and the upper cmf $\ol{F}(C^k_t = l_k\mid \ldots)$ must be obtained with the respective upper bounds.
+where we surpress in notation that $\lRsys(t \mid t > \tnow)$ and $\uRsys(t \mid t > \tnow)$
+depend on prior parameter sets and data.
 
-***proove rigorously (would need a kind of likelihood difference order)?
-%Do I get your comments right that based on lower and upper bounds
-%$\ul{P}(C^k_t = l_k\mid \ldots)$ and $\ol{P}(C^k_t = l_k\mid \ldots)$ for all $l_k = 0, 1, \ldots, n_k - e_k$,
-%we can easily get lower and upper bounds for the cdf $F_{C^k_t}(l_k \mid \ldots)$?
+\eqref{eq:lrsysdef} and \eqref{eq:ursysdef} seem to suggest that
+a full $2K$-dimensional box-constraint optimization is necessary,
+but this is not the case.
+Remember that $\Phi(l_1,\ldots,l_k)$ from \eqref{eq:sysrel-survsign} is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
+so if there is stochastic dominance in $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$,
+then there is, for each component type $k$,
+a prior parameter pair in $\PkZ$ that minimizes system reliability, and
+a prior parameter pair in $\PkZ$ that maximizes system reliability,
+independently of the other component types. 
+%such that system reliability is
+%minimized by a distribution that gives most weight to low values of $l_k$, and
+%maximized by a distribution that gives most weight to high values of $l_k$.
+Indeed, stochastic dominance in $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ is provided for $\ykz$.
+To see this, note that $\ykz$ gives the mean expected lifetime for type $k$ components.
+Thus, higher values for $\ykz$ mean higher expected lifetimes for the components,
+which in turn increases the probability that many components survive until time $t$,
+and with it, decreases the propability of few or no components surviving,
+so in total giving low probability weight for low values of $l_k$,
+and high probability weight for high values of $l_k$. 
+We therefore conclude that, for any fixed value of $\nkz$,
+the lower bound of $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for all $l_k$ is obtained with $\ykzu$, and
+the upper bound of $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for all $l_k$ is obtained with $\ykzl$.
 
-Furthermore, higher expected lifetimes for the components must mean
-a longer system survival, so in turn the $\ul{F}_{C^k_t}(l_k \mid \ldots)$'s
-should give us the lower bound for $P(\Tsys > t\mid\ldots)$,
-and the $\ol{F}_{C^k_t}(l_k \mid \ldots)$'s the upper bound.
-Note that e.g.\ $\ul{F}_{C^k_t}(l_k \mid \ldots)$ may, however, not correspond to a single parameter pair $(\nkz, \ykz)$.
-Also, in the system survival equation ($t > \tnow$)
+***need formal first-order stochastic dominance in $\ykz$ result for $P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$?
+I have it for inverse gamma posterior $f(\lambda_k\mid \nkz,\ykz, \vec{t}^k_{e_k;n_k})$,
+but not for posterior predictive***
+
+However, there is no corresponding reasoning for $\nkz$,
+such that different values of $\nkz$ may minimize (or maximize) $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ at different $l_k$'s.
+Therefore, the $\nkz$ values for lower and upper system reliability bounds are obtained by numeric optimization.
+%
+\iffalse %---------------------------
 \begin{linenomath*}
@@
  &= \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K
-    P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})
+    P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})
 \end{align}
@@
 (It would give us a lower bound for $\ul{P}(\Tsys > t\mid\ldots)$, however, but it might be very coarse.)
+%
+While it is clear that the lower bounds for $\ykz$ will lead to the lower system survival function,
+the role of $\nkz$ is not so clear.
+We therefore resort to numerical optimization of \eqref{eq:25} over $\{\nkz, k=1,\ldots,K\}$
+to obtain the lower bound for $P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)$.
+\fi %---------------------------
 
-Writing out Equation~\eqref{eq:25}, we get
+Writing out \eqref{eq:sysrel-survsign}, we get
+\begin{linenomath*}
+\begin{align}
+\lRsys(t \mid t > \tnow)
+ &= \min_{\PZi{1},\ldots,\PZi{K}} \Rsys\big(t \mid t > \tnow, \cup_{k=1}^K \{\PkZ, \vec{t}^k_{e_k;n_k}\}\big) \nonumber\\
+ &= \min_{\substack{\nkzfun{1} \in \left[\nkzlfun{1}, \nkzufun{1}\right]\\ \vdots\\ \nkzfun{K} \in \left[\nkzlfun{K}, \nkzufun{K}\right]}}
+    \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K P(C^k_t = l_k\mid\nkz,\ykzl, \mbf{t}^k_{e_k;n_k})\,,
+\end{align}
+\end{linenomath*}
+such that a $K$-dimensional box-constraint optimization is needed to obtain $\lRsys(t \mid t > \tnow)$.
+The result for $\uRsys(t \mid t > \tnow)$ is completely analogous.
+Computing time can furthermore be saved
+by computing only those $P(C^k_t = l_k\mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for $l_k$'s for which $\Phi(l_1,\ldots,l_K) > 0$.
+
+\iffalse %---------------------------
 \begin{linenomath*}
@@
 \end{linenomath*}
-
-While it is clear that the lower bounds for $\ykz$ will lead to the lower system survival function,
-the role of $\nkz$ is not so clear.
-We therefore resort to numerical optimization of \eqref{eq:25} over $\{\nkz, k=1,\ldots,K\}$
-to obtain the lower bound for $P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)$.
+\fi %---------------------------
 
@@
 
-***from poster or similar
+***from poster, bridge type system Fig.~\ref{fig:bridge-layout}, or brake system from ijar paper?
+
+we use box-constraint optimization with option \texttt{L-BFGS-B} of \texttt{optim} in \textsf{R}.
+
+\begin{figure}
+\centering
+\begin{tikzpicture}
+[type1/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
+ type2/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
+ type3/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
+ cross/.style={cross out,draw=red,very thick,minimum width=7mm, minimum height=5mm},
+ hv path/.style={thick, to path={-| (\tikztotarget)}},
+ vh path/.style={thick, to path={|- (\tikztotarget)}}]
+%\begin{scope}[scale=0.75]
+\node[type1] (T3)   at ( 5.6, 0) {T3};
+\node[type2] (T2)   at ( 2.8, 0) {T2};
+\node[type3] (T1-2) at ( 1.4, 1) {T1};
+\node[type3] (T1-3) at ( 1.4,-1) {T1};
+\node[type3] (T1-5) at ( 4.2, 1) {T1};
+\node[type3] (T1-6) at ( 4.2,-1) {T1};
+\coordinate (start) at (0  ,0);
+\coordinate (end)   at (6.3,0);
+\coordinate (bista) at (0.7,0);
+\coordinate (biend) at (4.9,0);
+\path (bista)     edge[hv path] (start)
+                  edge[vh path] (T1-2.west)
+                  edge[vh path] (T1-3.west)
+      (T1-2.east) edge[hv path] (T2.north)
+      (T1-3.east) edge[hv path] (T2.south)
+      (T2.north)  edge[vh path] (T1-5.west)
+      (T2.south)  edge[vh path] (T1-6.west)
+      (biend)     edge[vh path] (T1-5.east)
+                  edge[vh path] (T1-6.east)
+                  edge[hv path] (T3.west)
+      (T3.east)   edge[hv path] (end);
+%\end{scope}
+\end{tikzpicture}
+\caption{Reliability block diagram for a `bridge' system with three component types.}
+\label{fig:bridge-layout}
+\end{figure}
 
@@
 %
+\iffalse
 \section{Notation}
@@
 \end{tabular}
+\fi
 

### 2016-07-26 asce-paper.tex
abstract to 175 words

@@
 
-% slightly adapted ESREL abstract
+***Abstract must be 150--175 words long (this has 175), may not contain references or mathematics.
+
 \begin{abstract}
@@
 %
-A problem that then can arise is called prior-data conflict:
-from the viewpoint of the prior, the observed data seem very surprising,
-i.e., the information from data is in conflict with the prior assumptions.
-It has been recognised that models based on conjugate priors can be insensitive to prior-data conflict,
+A problem called prior-data conflict then can arise:
+observed data seem very surprising from the viewpoint of the prior,
+i.e., information from data is in conflict with prior assumptions.
+Models based on conjugate priors can be insensitive to prior-data conflict,
 in the sense that the spread of the posterior distribution does not increase in case of such a conflict,
-thus conveying a false sense of certainty by communicating that we can quantify the reliability of a system quite precisely when in fact we cannot.
+thus conveying a false sense of certainty.
 %
 We present an approach to mitigate this issue, by considering sets of prior distributions
-to model vague knowledge on component lifetimes,
-and study how surprisingly early or late component failures
-affect the prediction of the reliability of a system with arbitrary layout,
-making use of survival signature to characterise the system under study.
+to model limited knowledge on Weibull distributed component lifetimes,
+treating systems with arbitary layout using the survival signature.
 Our approach can be seen as a robust Bayesian procedure or imprecise probability method
-that appropriately reflects surprising data in the posterior system survival function or other posterior inferences.
+that reflects surprisingly early or late component failures
+by wider system reliability bounds.
+%We show how surprisingly early or late component failures
+%result in wider system reliability bounds.
+%
+%and study how surprisingly early or late component failures
+%affect the prediction of the reliability of a system with arbitrary layout,
+%making use of survival signature to characterise the system under study.
+%Our approach can be seen as a robust Bayesian procedure or imprecise probability method
+%that appropriately reflects surprising data in the posterior system reliability function.
 \end{abstract}
+% by communicating that we can quantify the reliability of a system quite precisely when in fact we cannot.
 
-\KeyWords{System Reliability, Imprecise Probability, Survival Signature, Robust Bayesian, Remaining Useful Life}
-
-***slightly adapted ESREL abstract, must be 150--175 words long (this has 226), may not contain references or mathematics.
+\KeyWords{System Reliability, Imprecise Probability, Survival Signature, Robust Bayesian Methods, Remaining Useful Life}
 

### 2016-07-26 isipta2015posterexamples.R
median system lifetime

@@ -59,5 +59,11 @@ fourKcornersSysrelPlot(tvec = postertvec1, rframe = postercorners1$lower, add = 
 fourKcornersSysrelPlot(tvec = postertvec1, rframe = postercorners1$upper, add = TRUE, col = rgb(16,16,115, max =255))
 #dev.off()
 
+# lower and upper median: region around 0.5
+posterpbox1[posterpbox1[,2] < 0.51 & posterpbox1[,2] > 0.49,]
+posterpbox1[posterpbox1[,3] < 0.51 & posterpbox1[,3] > 0.49,]
+# closest to 0.5
+posterpbox1[which.min(abs(posterpbox1[,2] - 0.5)),] # 8.10
+posterpbox1[which.min(abs(posterpbox1[,3] - 0.5)),] # 9.95
 
 #

### 2016-07-26 asce-paper.tex
rework of intro and some other tweaks suggested by Frank

@@
 This is usually done by determining the \emph{reliability function} $R(t)$,
-in other contexts also known as the \emph{survival function} $S(t)$,
+in other contexts also known as the \emph{survival function},
 giving the probability that the system has not failed by time $t$:
@@
 We assume that type $k$ component lifetimes $T_i^k$ ($i = 1, \ldots, n_k$)
-are Weibull distributed, with type-specific parameters $\beta_k$ (shape) and $\lambda_k$ (scale).
-***type-specific shape not implemented yet!***
+are Weibull distributed with type-specific parameters,
+where the shape parameter $\beta_k$ is known
+and the scale parameter $\lambda_k$ is unknown.
 
-Focusing on the prototype application,
+Focusing on a running system,
 we assume that our observations consist solely of the failure times of components in this system up to time $\tnow$,
@@
 This knowledge is encoded in form of a so-called prior distribution,
-a distribution on the parameters of the component lifetime distributions.
+which here, as we assume the shape parameter $\beta_k$ to be known,
+is a distribution on the scale parameter $\lambda_k$. %of the component lifetime distribution.
 Expert knowledge is especially important when there is very few data on the components (like in our scenario),
 as only with its help meaningful estimates for the system reliability can be made.
+%
+Due to the iterative nature of the Bayesian framework,
+it is also possible to use a set of posteriors based on component test data as the set of priors
+instead of a purely expert-based set of priors as discussed so far.
+The component test data may also contain right-censored observations,
+which can be treated in the same way as those from the running system
+(see Section~\ref{sec:lambdawithcens} for details).
 
-However, the choice for the prior distribution to encode the given expert knowledge is often debatable,
+The choice of prior distribution to encode given expert knowledge is often debatable,
 and a specific choice of prior is difficult to justify.
@@
 i.e., studying the effect of different choices of prior distribution on the quantities of interest
-(in our case, the system reliability function, which, in Bayesian terms, is a predictive distribution).
+(in our case, the system reliability function, which, in Bayesian terms, is a posterior predictive distribution).
 This idea has been explored in systematic sensitivity analysis, or robust Bayesian methods
@@
 while a large set will indicate that our knowledge about $\Tsys$ is rather shaky.
-
+%
 In line with imprecise or interval probability methods, we will thus have, for each $t$,
@@
 and an upper reliability $\uRsys(t) = \ol{P}(T_\text{sys} \geq t)$.
-We will explain in Sections~\ref{sec:modforsurpr} and *** how these bounds are obtained
-based on a set of prior distributions on the scale parameter of the component lifetime distribution.
+We will explain in Sections~\ref{sec:modforsurpr} and \ref{sec:robrel} how these bounds are obtained
+based on sets of prior distributions on the scale parameters of the component lifetime distributions.
 
@@
 (see Section~\ref{sec:modforsurpr} for more details).
-
-Due to the iterative nature of the Bayesian framework,
-it is possible to use a set of posteriors based on component test data as the set of priors
-instead of a purely expert-based set of priors as discussed so far.
-In that case, prior-data conflict sensitivity allows to uncover also a conflict between
+If a prior based on component test data is used,
+such prior-data conflict sensitivity furthermore allows to uncover a conflict between
 current observations in the running system and past observations from component tests.
@@
 
-***comment on shape parameter $\beta_k$ being fixed***
+***general methods (sets of conjugate priors, survival signature)
+can be used with other parametric component lifetime distributions
+that form a canonical exponential family
+(see, e.g., \citeNP[p.~202 and 272f]{2000:bernardosmith}, or \citeNP[p.~8]{diss}),
+such that conjugate prior can be constructed***
 
-We study the effect of surprisingly early or late component failures,
+***We study the effect of surprisingly early or late component failures,
 %on the system reliability prediction,
 showing that observations in conflict to prior assumptions
-indeed lead to more cautious system reliability predictions.
+indeed lead to more cautious system reliability predictions.***
 
@@
 In Section~\ref{sec:weibull}, we describe a Bayesian analysis for Weibull component lifetimes
+with fixed shape parameter
 and illustrate the issue of prior-data conflict.
@@
 showing how this mitigates the prior-data conflict issue for $\lambda_k$.
+Section~\ref{sec:robrel} then exploits this model to calculate system reliability bounds for a running system. 
+To this end, Bayesian estimation of $\lambda_k$ under right-censored observations is covered in Section~\ref{sec:lambdawithcens},
+followed by a brief introduction to the survival signature (Section~\ref{sec:sysrelwithsurvsign}).
+Section~\ref{sec:postpred} then details how gathered information on component lifetimes
+is transfomed to the necessary form for use within the survival signature framework,
+and Section~\ref{sec:optimize} explains how lower and upper bounds for $\Rsys(t \mid t > \tnow)$
+are obtained by efficiently optimizing over the parameter sets that define the sets of priors.
 ***
@@
 with density and cdf%
-\footnote{Our approach would be possible also for other parametric lifetime distributions
-that form a canonical exponential family
-(see, e.g., \citeNP[p.~202 and 272f]{2000:bernardosmith}, or \citeNP[p.~8]{diss}).}
 \begin{linenomath*}
@@
 
-\section{Models reflecting surprising data / Sets of Priors}
+\section{Models reflecting surprising data}
 \label{sec:modforsurpr}
@@
 the tractability of the update step
-(the posterior is again a parametric distribution)
+%(the posterior is again a parametric distribution)
 is a very attractive feature of the conjugate setting.
@@
 
+***if we would also wish to learn about the shape pm, we could follow
+standard Bayesian approaches and use a finite discrete distribution for beta - developing this together
+with suitable sets of priors for lambda, in particular to show the effect of prior-data conflict, is an interesting
+challenge for future research.
+
 \pagebreak

### 2016-07-26 asce-paper.tex
more minor tweaks

@@
 For this, we need the posterior predictive distribution
-of the number of components function at times $t > \tnow$,
+of the number of components that function at times $t > \tnow$,
 which we will derive in Section~\ref{sec:postpred}.
@@
 
-Consider observing a prototype system until $\tnow$,
+Consider observing a system until $\tnow$,
 where the system has $K$ different types of components,

### 2016-07-27 asce-paper.tex
elicitation section, start examples

@@
 \usepackage[usenames,dvipsnames]{xcolor}
+\usepackage{booktabs}
 \usepackage{url}
 \usepackage{tikz}
-\usetikzlibrary{shapes.misc,fit}
+%\usetikzlibrary{shapes.misc,fit}
+\usetikzlibrary{%
+   arrows,%
+   calc,%
+   fit,%
+   patterns,%
+   plotmarks,%
+   shapes.geometric,%
+   shapes.misc,%
+   shapes.symbols,%
+   shapes.arrows,%
+   shapes.callouts,%
+   shapes.multipart,%
+   shapes.gates.logic.US,%
+   shapes.gates.logic.IEC,%
+   er,%
+   automata,%
+   backgrounds,%
+   chains,%
+   topaths,%
+   trees,%
+   petri,%
+   mindmap,%
+   matrix,%
+   calendar,%
+   folding,%
+   fadings,%
+   through,%
+   patterns,%
+   positioning,%
+   scopes,%
+   decorations.fractals,%
+   decorations.shapes,%
+   decorations.text,%
+   decorations.pathmorphing,%
+   decorations.pathreplacing,%
+   decorations.footprints,%
+   decorations.markings,%
+   shadows}
 
@@
 showing how this mitigates the prior-data conflict issue for $\lambda_k$.
-Section~\ref{sec:robrel} then exploits this model to calculate system reliability bounds for a running system. 
-To this end, Bayesian estimation of $\lambda_k$ under right-censored observations is covered in Section~\ref{sec:lambdawithcens},
-followed by a brief introduction to the survival signature (Section~\ref{sec:sysrelwithsurvsign}).
-Section~\ref{sec:postpred} then details how gathered information on component lifetimes
-is transfomed to the necessary form for use within the survival signature framework,
-and Section~\ref{sec:optimize} explains how lower and upper bounds for $\Rsys(t \mid t > \tnow)$
-are obtained by efficiently optimizing over the parameter sets that define the sets of priors.
+Section~\ref{sec:robrel} then develops a method to calculate system reliability bounds
+for a running system based on sets of priors for $\lambda_k$. 
+%To this end, Bayesian estimation of $\lambda_k$ under right-censored observations is covered in Section~\ref{sec:lambdawithcens},
+%followed by a brief introduction to the survival signature (Section~\ref{sec:sysrelwithsurvsign}).
+%Section~\ref{sec:postpred} then details how gathered information on component lifetimes
+%is transfomed to the necessary form for use within the survival signature framework,
+%and Section~\ref{sec:optimize} explains how lower and upper bounds for $\Rsys(t \mid t > \tnow)$
+%are obtained by efficiently optimizing over the parameter sets that define the sets of priors.
+Section~\ref{sec:elicitation} discusses elicitation,
+by giving guidelines on how to choose prior parameter bounds
+that reflect expert information on components;
+Section~\ref{sec:examples} contains examples illustrating ***.
+Section~\ref{sec:concluding} concludes the paper by *** 
 ***
@@
 \label{eq:weibulldens}
-f(t_i^k \mid \lambda_k) &= \frac{\beta_k}{\lambda_k} (t_i^k)^{\beta_k-1} e^{-\frac{(t_i^k)^{\beta_k-1}}{\lambda_k}}\,, \\
+f(t_i^k \mid \lambda_k) &= \frac{\beta_k}{\lambda_k} (t_i^k)^{\beta_k-1} e^{-\frac{(t_i^k)^{\beta_k}}{\lambda_k}}\,, \\
 \label{eq:weibullcdf}
@@
 The structure of complex systems can be visualized by reliability block diagrams,
-an example is given in Figure~\ref{fig:bridge-layout}.
+an example is given in Figure~\ref{fig:brakesys-layout}.
 Components are represented by boxes or nodes,
@@
 Computing time can furthermore be saved
-by computing only those $P(C^k_t = l_k\mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for $l_k$'s for which $\Phi(l_1,\ldots,l_K) > 0$.
+by computing only those %$P(C^k_t = l_k\mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for $l_k$'s for which $\Phi(l_1,\ldots,l_K) > 0$
+summation terms for which $\Phi(l_1,\ldots,l_K) > 0$.
 
@@
 \section{Elicitation of prior parameter sets}
-
-*** prior via pseudo-observations, can contain censored pseudo-data
-
-*** cf paper from Frank \cite{1996:coolen::cens}
-
-\section{Examples}
-
-***from poster, bridge type system Fig.~\ref{fig:bridge-layout}, or brake system from ijar paper?
-
-we use box-constraint optimization with option \texttt{L-BFGS-B} of \texttt{optim} in \textsf{R}.
+\label{sec:elicitation}
+
+To represent expert knowledge on component failure times
+through bounds for $\ykz$ and $\nkz$,
+we can refer to the interpretations as given in Section~\ref{sec:weibull}:
+$\ykz$ is the prior expected value of $\lambda_k$,
+where $\lambda_k$ is linked to expected component lifetimes through \eqref{eq:lambdainterpret}.
+$\nkz$ can be seen as pseudocount, indicating how strong expert knwoledge is trusted
+in comparison to a sample of size $n$.
+Our approach allows the expert to give ranges $[\ykzl, \ykzu]$ and $[\nkzl, \nkzu]$
+instead of forcing a precise answer.
+
+It is also possible to directly link $\nkz$ and $\ykz$
+to observed lifetimes using a prior predictive distribution.
+Dropping the component index $k$ for ease of notation, this is given by
+\begin{linenomath*}
+\begin{align}
+f(t\mid \nz, \yz)
+ &= \int f(t\mid \lambda) f(\lambda\mid\nz,\yz) \dd \lambda \nonumber\\
+ &= \beta\, t^{\beta - 1}\, (\nz + 1) \frac{(\nz \yz)^{\nz + 1}}{(\nz \yz + t^\beta)^{\nz + 2}} \,.
+\label{eq:tpriopred}
+\end{align}
+\end{linenomath*}
+Replacing the prior parameters $\nz$ and $\yz$
+with their posterior counterparts $\nn$ and $\yn$ as defined in \eqref{eq:ig-update},
+the effect of virtual observations on \eqref{eq:tpriopred}, or the corresponding reliability function, can be determined.
+This allows to determine $\nz$ and $\yz$ through a number of `what-if' scenarios,
+by asking the expert to state what (s)he would expect to learn from observing certain virtual data.
+
+This strategy is known as pre-posterior analysis,
+being first advocated by \citeN[p.~19]{1965:good}.
+We recommend to check whether the effects of $\PkZ$ on the inference of interest
+(this may not always be the full reliability function)
+reasonably reflect an expert's beliefs before the data and in case some specific data become available,
+both data agreeing with initial beliefs and surprising data.
+Essentially, we advise to do an analysis like in our examples in Section~\ref{sec:examples} below,
+using hypothetical data.
+
+To elicit a meaningful prior distribution, or a set of prior distributions,
+it is important to ask questions which enable experts to stay close to their actual expertise.
+\citeN{1996:coolen::cens} discussed the possibility of generalizing the usual conjugate prior distributions,
+for parameters of exponential family models, by including pseudo-data which are right-censored.
+If the real data set contains such values, then such generalized priors do not lead to more computational complexities,
+while they can have several advantages.
+In addition to providing slightly more general classes of prior distributions through an additional hyperparameter,
+they may enable more realistic elicitation of expert judgements,
+for example if the expert has no experience with certain components past a specific life time.
+For more details we refer to \citeN{1996:coolen::cens},
+it should be noted that adopting such generalized prior distributions
+may also provide more flexibility for modelling the effects of prior-data conflict,
+this is left as a topic for future research.
 
@@
 \begin{tikzpicture}
-[type1/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
+[typeM/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=8mm}, %font=\footnotesize},
+ typeC/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=8mm}, %font=\footnotesize},
+ typeP/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=8mm}, %font=\footnotesize},
+ typeH/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=8mm}, %font=\footnotesize},
+ type1/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
  type2/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
@@
  vh path/.style={thick, to path={|- (\tikztotarget)}}]
-%\begin{scope}[scale=0.75]
-\node[type1] (T3)   at ( 5.6, 0) {T3};
-\node[type2] (T2)   at ( 2.8, 0) {T2};
-\node[type3] (T1-2) at ( 1.4, 1) {T1};
-\node[type3] (T1-3) at ( 1.4,-1) {T1};
-\node[type3] (T1-5) at ( 4.2, 1) {T1};
-\node[type3] (T1-6) at ( 4.2,-1) {T1};
-\coordinate (start) at (0  ,0);
-\coordinate (end)   at (6.3,0);
-\coordinate (bista) at (0.7,0);
-\coordinate (biend) at (4.9,0);
-\path (bista)     edge[hv path] (start)
-                  edge[vh path] (T1-2.west)
-                  edge[vh path] (T1-3.west)
-      (T1-2.east) edge[hv path] (T2.north)
-      (T1-3.east) edge[hv path] (T2.south)
-      (T2.north)  edge[vh path] (T1-5.west)
-      (T2.south)  edge[vh path] (T1-6.west)
-      (biend)     edge[vh path] (T1-5.east)
-                  edge[vh path] (T1-6.east)
-                  edge[hv path] (T3.west)
-      (T3.east)   edge[hv path] (end);
-%\end{scope}
+\begin{scope}[scale=1.5]
+\node[typeM] (M)    at ( 0  , 0  ) {M};
+\node[typeC] (C1)   at ( 1  , 1.5) {C1};
+\node[typeC] (C2)   at ( 1  , 0.5) {C2};
+\node[typeC] (C3)   at ( 1  ,-0.5) {C3};
+\node[typeC] (C4)   at ( 1  ,-1.5) {C4};
+\node[typeP] (P1)   at ( 2  , 1.5) {P1};
+\node[typeP] (P2)   at ( 2  , 0.5) {P2};
+\node[typeP] (P3)   at ( 2  ,-0.5) {P3};
+\node[typeP] (P4)   at ( 2  ,-1.5) {P4};
+\node[typeH] (H)    at ( 0  ,-1  ) {H};
+\coordinate (start)  at (-0.7, 0);
+\coordinate (startC) at ( 0.5, 0);
+\coordinate (startH) at (-0.4, 0);
+\coordinate (Hhop1)  at ( 0.4,-1);
+\coordinate (Hhop2)  at ( 0.6,-1);
+\coordinate (endP)   at ( 2.5, 0);
+\coordinate (end)    at ( 2.8, 0);
+\path (start)     edge[hv path] (M.west)
+      (M.east)    edge[hv path] (startC)
+      (startC)    edge[vh path] (C1.west)
+                  edge[vh path] (C2.west)
+                  edge[vh path] (C3.west)
+                  edge[vh path] (C4.west)
+      (C1.east)   edge[hv path] (P1.west)
+      (C2.east)   edge[hv path] (P2.west)
+      (C3.east)   edge[hv path] (P3.west)
+      (C4.east)   edge[hv path] (P4.west)
+      (endP)      edge[vh path] (P1.east)
+                  edge[vh path] (P2.east)
+                  edge[vh path] (P3.east)
+                  edge[vh path] (P4.east)
+                  edge[hv path] (end)
+      (startH)    edge[vh path] (H.west)
+      (H.east)    edge[hv path] (Hhop1)
+      (Hhop1)     edge[thick,out=90,in=90] (Hhop2)
+      (Hhop2)     edge[hv path] (P3.south)
+                  edge[hv path] (P4.north);
+\end{scope}
 \end{tikzpicture}
-\caption{Reliability block diagram for a `bridge' system with three component types.}
-\label{fig:bridge-layout}
+\caption{Reliability block diagram for a simplified automotive brake system.}
+\label{fig:brakesys-layout}
 \end{figure}
 
+\section{Examples}
+\label{sec:examples}
+
+%***brake system from ijar paper, Fig.~\ref{fig:brakesys-layout}
+As illustrative example, we consider a simplified automotive brake system with four types of component.
+The system layout is depicted in Figure~\ref{fig:brakesys-layout}.
+The master brake cylinder (M) activates all four wheel brake cylinders (C1 -- C4),
+which in turn actuate a braking pad assembly each (P1 -- P4).
+The hand brake mechanism (H) goes directly to the brake pad assemblies P3 and P4;
+the car brakes when at least one brake pad assembly is actuated.
+All values for $\Phi \not\in \{0,1\}$ for this system are given in Table~\ref{tab:brake-survsign}.
+
+\begin{table}
+\centering
+\begin{tabular}{cccclcccccl}
+  \toprule
+M & H & C & P & $\Phi$ & \quad & M & H & C & P & $\Phi$\\ 
+  \midrule
+1 & 0 & 1 & 1 & 0.25 & & 1 & 0 & 2 & 1 & 0.50 \\ 
+1 & 0 & 1 & 2 & 0.50 & & 1 & 0 & 2 & 2 & 0.83 \\ 
+1 & 0 & 1 & 3 & 0.75 & & 1 & 0 & 3 & 1 & 0.75 \\ 
+0 & 1 & 0 & 1 & 0.50 & & 1 & 1 & 0 & 1 & 0.50 \\ 
+0 & 1 & 0 & 2 & 0.83 & & 1 & 1 & 0 & 2 & 0.83 \\ 
+0 & 1 & 1 & 1 & 0.62 & & 1 & 1 & 1 & 1 & 0.62 \\ 
+0 & 1 & 1 & 2 & 0.92 & & 1 & 1 & 1 & 2 & 0.92 \\ 
+0 & 1 & 2 & 1 & 0.75 & & 1 & 1 & 2 & 1 & 0.75 \\ 
+0 & 1 & 2 & 2 & 0.97 & & 1 & 1 & 2 & 2 & 0.97 \\ 
+0 & 1 & 3 & 1 & 0.88 & & 1 & 1 & 3 & 1 & 0.88 \\ 
+   \bottomrule
+\end{tabular}
+\caption{Survival signature values $\not\in \{0,1\}$ for the simplified automotive brake system depicted in Figure~\ref{fig:brakesys-layout}.}
+\label{tab:brake-survsign}
+\end{table}
+
+***we use box-constraint optimization via option \texttt{L-BFGS-B} of \texttt{optim} in \textsf{R}.
+
 \section{Concluding Remarks}
+\label{sec:concluding}
 

### 2016-07-27 priorpredictive.R

@@ -1,0 +1,69 @@
+# --------------------------------------------------------------------------- #
+# ASCE-ASME paper - prior predictive for t
+# --------------------------------------------------------------------------- #
+
+# prior predictive density
+prpr <- function(t, n0, y0, beta = 2)
+  beta * t^(beta - 1) * (n0 + 1) * (n0 * y0)^(n0 + 1) * (n0 * y0 + t^beta)^(-n0 - 2)
+
+# prior predictive reliability function, works only for t vectors starting at 0
+prprR <- function(t, n0, y0, beta = 2){
+  dens <- prpr(t = t, n0 = n0, y0 = y0, beta = beta)
+  1-cumsum(dens)/(length(t)/max(t)) # divide by evaluation points per unit
+}
+
+nn <- function(n0, fts)
+  n0 + length(fts)
+
+yn <- function(n0, y0, fts, beta)
+  (n0*y0 + sum(fts^beta))/(n0 + length(fts))
+
+# -------------------------------------
+
+tvec <- seq(0, 10, length.out = 101)
+
+pr1 <- prpr(tvec, 2, failuretolambda(5,2), 2)
+pr2 <- prpr(tvec, 10, failuretolambda(5,2), 2)
+pr3 <- prpr(tvec, 2, failuretolambda(2,2), 2)
+#qplot(tvec, pr1, geom = "line")
+
+plot(tvec, pr1, type = "l")
+lines(tvec, pr2, col=2)
+lines(tvec, pr3, col=3)
+
+tvec <- seq(0, 10, length.out = 501)
+pr1n0 <- 1
+pr1y0 <- failuretolambda(5,2)
+fts1 <- rep(5, 5)
+pr1nn <- nn(pr1n0, fts1)
+pr1yn <- yn(2, failuretolambda(5,2), fts1, 2)
+pr1d <- prpr(tvec, pr1n0, pr1y0, 2)
+pr1r <- prprR(tvec, pr1n0, pr1y0, 2)
+pr1dp <- prpr(tvec, pr1nn, pr1yn, 2)
+pr1rp <- prprR(tvec, pr1nn, pr1yn, 2)
+plot(tvec, pr1r, type = "l", ylim=c(0,1), xlab="t", ylab="R(t)") # prior
+lines(tvec, pr1rp, col=2) # posterior
+
+# hazard
[…]

### 2016-07-27 weibull-sys-functions.R

@@ -154,7 +154,8 @@ sysrel <- function(n0y0, survsign, beta, fts, tnow, t, table = FALSE, nk = NULL,
   survsign2 <- survsign
   for (k in 1:K)
     survsign2 <- survsign2[survsign2[,k] <= (nk-ek)[k],]
-  survsign2 <- survsign2[survsign2$Probability > 0,]
+  if (dim(survsign2)[1] > 1)
+    survsign2 <- survsign2[survsign2$Probability > 0,]
   for (k in 1:K){ # for loop is probably slow
     survsign2$new <- NA
     newname <- paste("PCt",k,sep="")
@@ -292,7 +293,6 @@ sysrelLuck <- function(luckobjlist, survsign, beta, fts, tnow, t, returnasvec = 
 
 
 # calculates the the lower and upper system reliability function for vector of timepoints tvec
-# as grey area
 # luckobjlist list of K of prior luckmodel objetcs
 # survsign    data frame with the survival signature as output by computeSystemSurvivalSignature()
 # beta        vector of K fixed weibull shape parameters
@@ -332,6 +332,14 @@ plotSysrelPbox <- function(res, add = FALSE, ylim = c(0,1), xlab = "t", ylab = e
     upper[length(tvec)-t+1] <- res[t,3]
   }
   polygon(c(tvec, tvecrev), c(lower, upper), border = polygonBorderCol, col = polygonFillCol)
+}
+
+# produces survival signature matrix for one component of type "name",
+# for use in nonParBayesSystemInference()
+oneCompSurvSign <- function(name){
+  res <- data.frame(name=c(0,1), Probability=c(0,1))
+  names(res)[1] <- name
+  res
 }
 
 #

### 2016-07-27 figures3f.R
start example figures: prior predictive for components

@@ -1,0 +1,80 @@
+# --------------------------------------------------------------------------- #
+# ASCE-ASME paper - code for example figs
+# --------------------------------------------------------------------------- #
+
+source("weibull-sys-functions.R")
+source("plotdefs.R")
+
+br <- graph.formula(s -- M -- C1:C2:C3:C4, P1:P2:P3:P4 -- t,
+                    C1 -- P1, C2 -- P2, C3 -- P3, C4 -- P4, s -- H -- P3:P4)
+br <- setCompTypes(br, list("M"=c("M"), "H"=c("H"), "C"=c("C1", "C2", "C3", "C4"), "P"=c("P1", "P2", "P3", "P4")))
+brsysign <- computeSystemSurvivalSignature(br)
+brMpr <- LuckModel(n0 = c(2,5),  y0 = c(failuretolambda(5,2.5), failuretolambda(8,2.5)))
+brHpr <- LuckModel(n0 = c(1,10), y0 = c(failuretolambda(2,1),   failuretolambda(20,1)))
+brCpr <- LuckModel(n0 = c(1,5),  y0 = c(failuretolambda(8,2),   failuretolambda(10,2)))
+brPpr <- LuckModel(n0 = c(1,10), y0 = c(failuretolambda(3,1.5), failuretolambda(4,1.5)))
+brpr <- list(brMpr, brHpr, brCpr, brPpr)
+brprtvec <- seq(0, 15, length.out=201)
+brprnk <- c(1, 1, 4, 4)
+brbeta <- c(2.5, 1, 2, 1.5)
+brfts0 <- list(NULL, NULL, NULL, NULL)
+# components
+brMprrel <- sysrelPbox(luckobjlist = list(brpr[[1]]), survsign = oneCompSurvSign("M"), nk = 1,
+                       beta = brbeta[1], fts = list(NULL), tnow = 0, tvec = brprtvec, prior = TRUE)
+brHprrel <- sysrelPbox(luckobjlist = list(brpr[[2]]), survsign = oneCompSurvSign("H"), nk = 1,
+                       beta = brbeta[2], fts = list(NULL), tnow = 0, tvec = brprtvec, prior = TRUE)
+brCprrel <- sysrelPbox(luckobjlist = list(brpr[[3]]), survsign = oneCompSurvSign("C"), nk = 1,
+                       beta = brbeta[3], fts = list(NULL), tnow = 0, tvec = brprtvec, prior = TRUE)
[…]

### 2016-07-27 plotdefs.R

@@ -4,6 +4,7 @@
 
 bottomlegend <- theme(legend.position = 'bottom', legend.direction = 'horizontal', legend.title = element_blank())
 rightlegend <- theme(legend.title = element_blank())
+nolegend <- guides(linetype="none", fill="none", group="none", colour="none")
 ijarcols <- c("#b2df8a", "#1f78b4")
 ijarcol <- scale_colour_manual(values = ijarcols)
 ijarfill <- scale_fill_manual(values = ijarcols)

### 2016-07-27 priorpredictive.R

@@ -2,24 +2,6 @@
 # ASCE-ASME paper - prior predictive for t
 # --------------------------------------------------------------------------- #
 
-# prior predictive density
-prpr <- function(t, n0, y0, beta = 2)
-  beta * t^(beta - 1) * (n0 + 1) * (n0 * y0)^(n0 + 1) * (n0 * y0 + t^beta)^(-n0 - 2)
-
-# prior predictive reliability function, works only for t vectors starting at 0
-prprR <- function(t, n0, y0, beta = 2){
-  dens <- prpr(t = t, n0 = n0, y0 = y0, beta = beta)
-  1-cumsum(dens)/(length(t)/max(t)) # divide by evaluation points per unit
-}
-
-nn <- function(n0, fts)
-  n0 + length(fts)
-
-yn <- function(n0, y0, fts, beta)
-  (n0*y0 + sum(fts^beta))/(n0 + length(fts))
-
-# -------------------------------------
-
 tvec <- seq(0, 10, length.out = 101)
 
 pr1 <- prpr(tvec, 2, failuretolambda(5,2), 2)

### 2016-07-27 weibull-sys-functions.R

@@ -334,6 +334,45 @@ plotSysrelPbox <- function(res, add = FALSE, ylim = c(0,1), xlab = "t", ylab = e
   polygon(c(tvec, tvecrev), c(lower, upper), border = polygonBorderCol, col = polygonFillCol)
 }
 
+# -------------------------------------
+
+# prior predictive density
+prpr <- function(t, n0, y0, beta = 2)
+  beta * t^(beta - 1) * (n0 + 1) * (n0 * y0)^(n0 + 1) * (n0 * y0 + t^beta)^(-n0 - 2)
+
+# prior predictive reliability function, works only for t vectors starting at 0
+prprR <- function(t, n0, y0, beta = 2){
+  dens <- prpr(t = t, n0 = n0, y0 = y0, beta = beta)
+  1-cumsum(dens)/(length(t)/max(t)) # divide by evaluation points per unit
+}
+
+nn <- function(n0, fts)
+  n0 + length(fts)
+
+yn <- function(n0, y0, fts, beta, n = length(fts), tnow = max(fts))
+  (n0*y0 + (n - length(fts))*tnow^beta + sum(fts^beta))/(n0 + length(fts))
+# set fts = NULL when no failures occurred
+
+# prior predictive reliability function, works only for t vectors starting at 0
+prprRluck <- function(tvec, luckobj, beta = 2){
+  l1 <- prprR(tvec, n0(luckobj)[1], y0(luckobj)[1], beta)
+  l2 <- prprR(tvec, n0(luckobj)[2], y0(luckobj)[1], beta)
+  u1 <- prprR(tvec, n0(luckobj)[1], y0(luckobj)[2], beta)
+  u2 <- prprR(tvec, n0(luckobj)[2], y0(luckobj)[2], beta)
+  data.frame(tvec = tvec, lower = pmin(l1, l2), upper = pmax(u1, u2))
+}
+
+# posterior predictive reliability function, works only for t vectors starting at 0
+# checking only the four corners of the posterior parameter set
+poprRluck <- function(tvec, luckobj, beta = 2, fts, n, tnow){
+  l1 <- prprR(tvec, nn(n0(luckobj)[1], fts), yn(n0(luckobj)[1], y0(luckobj)[1], fts, beta, n, tnow), beta)
[…]

### 2016-07-28 asce-paper.tex
start example figures: prior predictive for components
example figures and basic text for example section

@@
 
+\newcommand{\El}{\ul{\operatorname{E}}}
+\newcommand{\Eu}{\ol{\operatorname{E}}}
+
 \def\yz{y\uz}
@@
 \end{linenomath*}
-where $\lambda_k > 0$ and $t > 0$.%
-\footnote{The shape parameter $\beta_k$ determines whether the hazard rate is increasing ($\beta_k > 1$)
+where $\lambda_k > 0$ and $t > 0$.
+
+The shape parameter $\beta_k$ determines whether the hazard rate is increasing ($\beta_k > 1$)
 or decreasing ($\beta_k < 1$) over time.
-For $\beta_k=1$, we obtain the Exponential distribution with constant hazard rate as a special case.
-The value for $\beta_k$ will thus often be clear from practical considerations.}
+For $\beta_k=1$, one obtains the Exponential distribution with constant hazard rate as a special case.
+The value for $\beta_k$ will often be clear from practical considerations.
+
 The scale parameter $\lambda_k$ can be interpreted through the relation
@@
 
+We have implemented the method in \textsf{R},
+using box-constraint optimization via option \texttt{L-BFGS-B} of \texttt{optim},
+and pan to release a package containing the code to reproduce all results and figures
+for the examples in Section~\ref{sec:examples}.
+
 \section{Elicitation of prior parameter sets}
@@
  type3/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
- cross/.style={cross out,draw=red,very thick,minimum width=7mm, minimum height=5mm},
+ cross/.style={cross out,draw=red,very thick,minimum width=9mm, minimum height=7mm},
  hv path/.style={thick, to path={-| (\tikztotarget)}},
  vh path/.style={thick, to path={|- (\tikztotarget)}}]
-\begin{scope}[scale=1.5]
+\begin{scope}[xscale=1.5, yscale=1.2]
 \node[typeM] (M)    at ( 0  , 0  ) {M};
@@
 \node[typeC] (C2)   at ( 1  , 0.5) {C2};
+\node[cross]        at ( 1  , 0.5) {};
 \node[typeC] (C3)   at ( 1  ,-0.5) {C3};
+\node[cross]        at ( 1  ,-0.5) {};
 \node[typeC] (C4)   at ( 1  ,-1.5) {C4};
@@
 \node[typeP] (P2)   at ( 2  , 0.5) {P2};
+\node[cross]        at ( 2  , 0.5) {};
 \node[typeP] (P3)   at ( 2  ,-0.5) {P3};
+\node[cross]        at ( 2  ,-0.5) {};
 \node[typeP] (P4)   at ( 2  ,-1.5) {P4};
@@
 \end{tikzpicture}
-\caption{Reliability block diagram for a simplified automotive brake system.}
+\caption{Reliability block diagram for a simplified automotive brake system,
+with those components marked that we assume to fail.}
 \label{fig:brakesys-layout}
@@
 As illustrative example, we consider a simplified automotive brake system with four types of component.
-The system layout is depicted in Figure~\ref{fig:brakesys-layout}.
 The master brake cylinder (M) activates all four wheel brake cylinders (C1 -- C4),
@@
 the car brakes when at least one brake pad assembly is actuated.
-All values for $\Phi \not\in \{0,1\}$ for this system are given in Table~\ref{tab:brake-survsign}.
+The system layout is depicted in Figure~\ref{fig:brakesys-layout},
+with those components marked that we assume to fail in each of the three cases studied below.
+The values for $\Phi \not\in \{0,1\}$ for the complete system are given in Table~\ref{tab:brake-survsign}.
 
@@
 
-***we use box-constraint optimization via option \texttt{L-BFGS-B} of \texttt{optim} in \textsf{R}.
+We will use same prior setting with three different data scenarios,
+where we observe failure times in accordance with prior expectations in the first case,
+surprisingly early failures in the second case, and
+surprisingly late failures in the third case.
+In each case, we assume that C2, C3, P2 and P3 fail, vary only the failure times,
+and study their effect on the system reliability.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{fig4}
+\caption{Sets of prior predictive reliability functions for the four component types,
+illustrating the choice of prior parameter sets $\PkZ$.}
+\label{fig:brake-comppriors}
+\end{figure}
+
+The prior assumptions for the four component types are visualized in Figure~\ref{fig:brake-comppriors},
+the corresponding prior parameter sets $\PkZ$, $k=\text{M}, \text{H}, \text{C}, \text{P}$
+are given in Table~\ref{tab:priorparamsets},
+where $\El[T_i^k]$ and $\Eu[T_i^k]$ give lower and upper bound for expected component lifetimes,
+which then have been transformed to bounds for the scale parameter using \eqref{eq:lambdainterpret}.
+%For the prior parameter sets $\PZi{\text{M}}$
+
+\begin{table}
+\centering
+\begin{tabular}{crrrrrrr}
+  \toprule
+$k$ & $\beta_k$ & $\El[T_i^k]$ & $\Eu[T_i^k]$ & $\ykzl$ & $\ykzu$ & $\nkzl$ & $\nkzu$ \\
+  \midrule
+M & $2.5$ & $5$\rule{1.5ex}{0ex} & $ 8$\rule{1.5ex}{0ex} & $75.4$ & $244.1$ & $2$\rule{1ex}{0ex} & $ 5$\rule{1ex}{0ex} \\
+H & $1.2$ & $2$\rule{1.5ex}{0ex} & $20$\rule{1.5ex}{0ex} & $ 2.5$ & $ 39.2$ & $1$\rule{1ex}{0ex} & $10$\rule{1ex}{0ex} \\
+C & $2  $ & $8$\rule{1.5ex}{0ex} & $10$\rule{1.5ex}{0ex} & $81.5$ & $127.3$ & $1$\rule{1ex}{0ex} & $ 5$\rule{1ex}{0ex} \\
+P & $1.5$ & $3$\rule{1.5ex}{0ex} & $ 4$\rule{1.5ex}{0ex} & $ 6.1$ & $  9.3$ & $1$\rule{1ex}{0ex} & $10$\rule{1ex}{0ex} \\
+  \bottomrule
+\end{tabular}
+\caption{Prior parameter sets for the four component types.}
+\label{tab:priorparamsets}
+\end{table}
+
+In the first case, we observe $t_1^\text{C} = 6$, $t_2^\text{C} = 7$, $t_1^\text{P} = 3$, $t_2^\text{P} = 4$,
+and observe the running system until $\tnow = 8$,
+i.e., $t_1^\text{M} = t_1^\text{H} = t_3^\text{C} = t_4^\text{C} = t_3^\text{P} = t_4^\text{P} = 8^+$.
+***Notation as ordered, not to component numbers***
+These observations correspond more or less to prior expectations,
+and the corresponding posterior predictive component distributions are given in Figure~\ref{fig:comppost-1}.
+***some discussion***
+
+\begin{figure}
+\includegraphics[width=\textwidth]{fig5a}
+\caption{Sets of posterior predictive reliability functions for the four component types
+for observations in line with prior expectations.}
+\label{fig:comppost-1}
+\end{figure}
+
+For the second case, with $t_1^\text{C} = 1$, $t_2^\text{C} = 2$, $t_1^\text{P} = 0.5$, $t_2^\text{P} = 1$
+and $\tnow = 2$, we assume to observe surprisingly early failures;
+the corresponding posterior predictive component distributions are given in Figure~\ref{fig:comppost-2}.
+***some discussion***
+
+\begin{figure}
+\includegraphics[width=\textwidth]{fig6a}
+\caption{Sets of posterior predictive reliability functions for the four component types
+for surprisingly early failures.}
+\label{fig:comppost-2}
+\end{figure}
+
+For the third case, we assume to observe surprisingly late failures,
+namely $t_1^\text{C} = 11$, $t_2^\text{C} = 12$, $t_1^\text{P} = 8$, $t_2^\text{P} = 9$, and $\tnow = 12$;
+the corresponding posterior predictive component distributions are given in Figure~\ref{fig:comppost-3}.
+***some discussion***
+
+\begin{figure}
+\includegraphics[width=\textwidth]{fig7a}
+\caption{Sets of posterior predictive reliability functions for the four component types
+for surprisingly late failures.}
+\label{fig:comppost-3}
+\end{figure}
+
+Figure~\ref{fig:brake-sysrels} depicts the set of prior system reliability functions,
+together with the sets of posterior system reliabilty function for the three cases.
+***some discussion***
+
+\begin{figure}
+\includegraphics[width=\textwidth]{fig8}
+\caption{Sets of prior and posterior system reliability functions for the three cases.*** }
+\label{fig:brake-sysrels}
+\end{figure}
 

### 2016-07-28 figures3f.R

@@ -5,20 +5,34 @@
 source("weibull-sys-functions.R")
 source("plotdefs.R")
 
+# full system for prior
 br <- graph.formula(s -- M -- C1:C2:C3:C4, P1:P2:P3:P4 -- t,
                     C1 -- P1, C2 -- P2, C3 -- P3, C4 -- P4, s -- H -- P3:P4)
 br <- setCompTypes(br, list("M"=c("M"), "H"=c("H"), "C"=c("C1", "C2", "C3", "C4"), "P"=c("P1", "P2", "P3", "P4")))
 brsysign <- computeSystemSurvivalSignature(br)
-brMpr <- LuckModel(n0 = c(2,5),  y0 = c(failuretolambda(5,2.5), failuretolambda(8,2.5)))
-brHpr <- LuckModel(n0 = c(1,10), y0 = c(failuretolambda(2,1),   failuretolambda(20,1)))
+
+# reduced system for posterior: we assume that C2, C3, P2 and P3 have failed
+brpos <- graph.formula(s -- M -- C1:C4, P1:P4 -- t,
+                       C1 -- P1, C4 -- P4, s -- H -- P4)
+brpos <- setCompTypes(brpos, list("M"=c("M"), "H"=c("H"), "C"=c("C1", "C4"), "P"=c("P1", "P4")))
+brpossysign <- computeSystemSurvivalSignature(brpos)
+
+# prior param sets
 brCpr <- LuckModel(n0 = c(1,5),  y0 = c(failuretolambda(8,2),   failuretolambda(10,2)))
+brHpr <- LuckModel(n0 = c(1,10), y0 = c(failuretolambda(2,1.2), failuretolambda(20,1.2)))
+brMpr <- LuckModel(n0 = c(2,5),  y0 = c(failuretolambda(5,2.5), failuretolambda(8,2.5)))
 brPpr <- LuckModel(n0 = c(1,10), y0 = c(failuretolambda(3,1.5), failuretolambda(4,1.5)))
-brpr <- list(brMpr, brHpr, brCpr, brPpr)
-brprtvec <- seq(0, 15, length.out=201)
-brprnk <- c(1, 1, 4, 4)
-brbeta <- c(2.5, 1, 2, 1.5)
+brpr <- list(brCpr, brHpr, brMpr, brPpr)
+brprnk <- c(4, 1, 1, 4)
+brbeta <- c(2, 1.2, 2.5, 1.5)
 brfts0 <- list(NULL, NULL, NULL, NULL)
[…]

### 2016-07-28 weibull-sys-functions.R

@@ -157,10 +157,10 @@ sysrel <- function(n0y0, survsign, beta, fts, tnow, t, table = FALSE, nk = NULL,
   if (dim(survsign2)[1] > 1)
     survsign2 <- survsign2[survsign2$Probability > 0,]
   for (k in 1:K){ # for loop is probably slow
-    survsign2$new <- NA
-    newname <- paste("PCt",k,sep="")
+    survsign2$tmp <- NA
+    tmpname <- paste("PCt",k,sep="")
     ncols <- length(survsign2)
-    names(survsign2) <- c(names(survsign2)[-ncols], newname)
+    names(survsign2) <- c(names(survsign2)[-ncols], tmpname)
     for (i in 1:dim(survsign2)[1]){
       survsign2[i,ncols] <- postpredC(n0y0 = n0y0[[k]], beta = beta[k], n = nk[k],
                                       fts = fts[[k]], tnow = tnow, t = t, l = survsign2[i,k], prior = prior)

### 2016-07-29 figures3f.R
imprecision plot

@@ -246,4 +246,20 @@ fig8
 pdf("fig8.pdf", width=8, height=6)
 fig8
 dev.off()
+
+# plot of sysrel prior / posterior imprecision
+fig9 <- ggplot(br4df, aes(x = tvec)) + theme_bw() + ylim(0, 1) + ijarcol + #ijarfill + 
+#  geom_ribbon(aes(ymin = lower, ymax = upper, group = Item, colour = Item, fill = Item), alpha = 0.5) +
+#  geom_line(aes(y = lower, group = Item, colour = Item)) + 
+  geom_line(aes(y = upper-lower, group = interaction(Item, Panel), colour = Item, lty = Panel)) + # facet_wrap(~Panel, nrow=2) + 
+  xlab(expression(t)) + ylab(bquote(bar(R)[sys](t) - ~underline(R)[sys](t)))
+fig9
+
+#setEPS()
+#postscript("fig9.eps",width=8,height=6)
+pdf("fig9.pdf", width=6, height=3)
+fig9
+dev.off()
+
+
 #

### 2016-07-29 asce-paper.tex
imprecision plot
work on examples and examples section

@@
 
+\newcommand{\ykzfun}[1]{y\uz_{#1}}
+\newcommand{\ykzlfun}[1]{\ul{y}\uz_{#1}}
+\newcommand{\ykzufun}[1]{\ol{y}\uz_{#1}}
+
 \def\nz{n\uz}
@@
 that reflect expert information on components;
-Section~\ref{sec:examples} contains examples illustrating ***.
+Section~\ref{sec:examples} contains examples illustrating the merits of our method.
 Section~\ref{sec:concluding} concludes the paper by *** 
 ***
-
-%In the last section, we will briefly describe
-%how the approach can be generalized to arbitrary system structures
-%using the survival signature \cite{2012:survsign},
-%which allows for different types of components and
-%the inclusion of data from component tests, as in \citeNP{2014:bayessurvsign}.
-%Information on the distribution of component failure times $T_i$,
-%where $i = 1, \ldots, n$ if the system consists of $n$ components,
-%can then be used to derive the distribution of $T_\text{sys}$.
 
@@
 \caption{Reliability block diagram for a simplified automotive brake system,
-with those components marked that we assume to fail.}
+with those components marked that we assume to fail in the three scenarios.}
 \label{fig:brakesys-layout}
@@
 
-We will use same prior setting with three different data scenarios,
-where we observe failure times in accordance with prior expectations in the first case,
-surprisingly early failures in the second case, and
-surprisingly late failures in the third case.
-In each case, we assume that C2, C3, P2 and P3 fail, vary only the failure times,
-and study their effect on the system reliability.
-
-\begin{figure}
-\includegraphics[width=\textwidth]{fig4}
-\caption{Sets of prior predictive reliability functions for the four component types,
-illustrating the choice of prior parameter sets $\PkZ$.}
-\label{fig:brake-comppriors}
-\end{figure}
-
-The prior assumptions for the four component types are visualized in Figure~\ref{fig:brake-comppriors},
-the corresponding prior parameter sets $\PkZ$, $k=\text{M}, \text{H}, \text{C}, \text{P}$
-are given in Table~\ref{tab:priorparamsets},
-where $\El[T_i^k]$ and $\Eu[T_i^k]$ give lower and upper bound for expected component lifetimes,
-which then have been transformed to bounds for the scale parameter using \eqref{eq:lambdainterpret}.
-%For the prior parameter sets $\PZi{\text{M}}$
-
+We will use same prior setting (described in Section~\ref{sec:ex-prior})
+and combine it with three different data scenarios,
+where we observe failure times in accordance with prior expectations in the first case (Section~\ref{sec:ex-case1}),
+surprisingly early failures in the second case (Section~\ref{sec:ex-case2}), and
+surprisingly late failures in the third case (Section~\ref{sec:ex-case3}).
+In each case, we assume that C2, C3, P2 and P3 fail, only varying the failure times,
+and study the effect of learning about these failures on the component level.
+%and for the running system.
+Effects on posterior reliability bounds for the running system
+are then discussed for all three cases in Section~\ref{sec:ex-sysrel}.
+
+\subsection{Prior assumptions}
+\label{sec:ex-prior}
+
+The prior assumptions, which we can imagine to be determined by an expert,
+or by a combination of expert knowledge and component test data,
+are given by the prior parameter sets $\PkZ$, $k=\text{M}, \text{H}, \text{C}, \text{P}$,
+as described in Table~\ref{tab:priorparamsets}.
+There, $\El[T_i^k]$ and $\Eu[T_i^k]$ give the lower and upper bound for expected component lifetimes, respectively,
+which then have been transformed to bounds for the scale parameter using \eqref{eq:lambdainterpret},
+resulting in $\ykzl$ and $\ykzu$.
+For example, according to the expert, the mean time to failure for component type M is between 5 and 8 time units,
+leading to $\ykzlfun{\text{M}} = 75.4$ and $\ykzufun{\text{M}} = 244.1$,
+and the expert considers his knowledge on these expected lifetime bounds
+as having the strength of at least 2 and at most 5 observations.  
 \begin{table}
@@
 \end{table}
+%For the prior parameter sets $\PZi{\text{M}}$
+
+These prior assumptions for the four component types are visualized in Figure~\ref{fig:brake-comppriors},
+showing the sets of reliability functions corresponding to the prior predictive density \eqref{eq:tpriopred}.
+The figure thus displays the bounds for the probability that a single component,
+having been put under risk at time $0$, will have failed by time $t$.
+The top left graph in Figure~\ref{fig:brake-sysrels} shows what the prior assumptions on components
+signify for the system, depicting the prior bounds for the system reliability %before the system has started
+on a scale of time elapsed since system startup.
+For example, the prior probability of the system to survive until time $10$ is between $***$ and $***$.
+%calender time scale, where $t = 0$ is the time when the system starts to run.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{fig4}
+\caption{Sets of prior predictive reliability functions for the four component types,
+illustrating the choice of prior parameter sets $\PkZ$.}
+\label{fig:brake-comppriors}
+\end{figure}
+
+\subsection{Case 1: failure times as expected}
+\label{sec:ex-case1}
 
@@
 i.e., $t_1^\text{M} = t_1^\text{H} = t_3^\text{C} = t_4^\text{C} = t_3^\text{P} = t_4^\text{P} = 8^+$.
-***Notation as ordered, not to component numbers***
+%***Notation as ordered, not to component numbers***
+(Note that we number component failure times by order, not by component number in the system layout.)
 These observations correspond more or less to prior expectations,
 and the corresponding posterior predictive component distributions are given in Figure~\ref{fig:comppost-1}.
-***some discussion***
+In analogue to Figure~\ref{fig:brake-comppriors},
+Figure~\ref{fig:comppost-1} displays the bounds for the probability that a single component,
+having been put under risk at time $0$, will have failed by time $t$,
+after having seen these (partly censored) observations.
+For easy comparisons, Figure~\ref{fig:comppost-1} also contains the prior bounds from Figure~\ref{fig:brake-comppriors}.
 
@@
 
+We see that the graphs for M and H do not change dramatically,
+as there is only one component of each in the system to learn from.
+For C, the bounds have considerably narrowed,
+showing the effect of having seen the four observations
+$t_1^\text{C} = 6$, $t_2^\text{C} = 7$, $t_3^\text{C} = t_4^\text{C} = 8^+$.
+The bounds for P have not narrowed as much;
+this is due to the two right-censored observations $t_3^\text{P} = t_4^\text{P} = 8^+$;
+from the prior assumptions, surviving past time 8 is already quite unusual.
+
+\subsection{Case 2: surprisingly early failure times}
+\label{sec:ex-case2}
+
 For the second case, with $t_1^\text{C} = 1$, $t_2^\text{C} = 2$, $t_1^\text{P} = 0.5$, $t_2^\text{P} = 1$
@@
 
+\subsection{Case 3: surprisingly late failure times}
+\label{sec:ex-case3}
+
 For the third case, we assume to observe surprisingly late failures,
@@
 
+\subsection{Reliability bounds for the running system}
+\label{sec:ex-sysrel}
+
 Figure~\ref{fig:brake-sysrels} depicts the set of prior system reliability functions,
-together with the sets of posterior system reliabilty function for the three cases.
+together with the sets of posterior system reliability function for the three cases.
 ***some discussion***
@@
 
+Figure~\ref{fig:brake-sysrels-imprecision} shows $\uRsys(t) - \lRsys(t)$ ***
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{fig9}
+\caption{Imprecision of prior and posterior system reliability sets.*** }
+\label{fig:brake-sysrels-imprecision}
+\end{figure}
+
 \section{Concluding Remarks}
@@
 challenge for future research.
+
+***acknowledgements
 

### 2016-07-29 figures3f.R

@@ -53,22 +53,23 @@ fig3 <- ggplot(brprdf, aes(x = tvec)) + theme_bw() + ijarcol + ijarfill + ylim(0
 fig3
 
 # component reliability functions using the prior predictive
-prprtvec <- seq(0, 20, length.out=501)
-prprC <- prprRluck(prprtvec, brpr[[1]], beta = brbeta[1])
-prprH <- prprRluck(prprtvec, brpr[[2]], beta = brbeta[2])
-prprM <- prprRluck(prprtvec, brpr[[3]], beta = brbeta[3])
-prprP <- prprRluck(prprtvec, brpr[[4]], beta = brbeta[4])
+prprtvec <- seq(0, 20, length.out=301)
+prprC <- prprRluck(prprtvec, brpr[[1]], beta = brbeta[1], n0gridlen = 2000)
+prprH <- prprRluck(prprtvec, brpr[[2]], beta = brbeta[2], n0gridlen = 2000)
+prprM <- prprRluck(prprtvec, brpr[[3]], beta = brbeta[3], n0gridlen = 2000)
+prprP <- prprRluck(prprtvec, brpr[[4]], beta = brbeta[4], n0gridlen = 2000)
 prprdf <- rbind(data.frame(prprM, Part = "M", Item = "Prior"), data.frame(prprH, Part = "H", Item = "Prior"),
                 data.frame(prprC, Part = "C", Item = "Prior"), data.frame(prprP, Part = "P", Item = "Prior"))
 prprdf$Item <- ordered(prprdf$Item, levels=c("Prior", "Posterior"))
 prprdf$Part <- ordered(prprdf$Part, levels=c("M", "H", "C", "P"))
 prprdf$lower[prprdf$lower < 0] <- 0
+prprdf$upper[prprdf$upper > 1] <- 1
 fig4 <- ggplot(prprdf, aes(x = tvec)) + theme_bw() + ijarcol + ijarfill + ylim(0, 1) +  
   geom_ribbon(aes(ymin = lower, ymax = upper, group = Item, colour = Item, fill = Item), alpha = 0.5) +
   geom_line(aes(y = lower, group = Item, colour = Item)) + 
   geom_line(aes(y = upper, group = Item, colour = Item)) + 
   facet_wrap(~Part, nrow=2) + xlab(expression(t)) + ylab(expression(R(t))) + rightlegend #nolegend 
-fig4
[…]

### 2016-07-29 weibull-sys-functions.R

@@ -341,34 +341,67 @@ prpr <- function(t, n0, y0, beta = 2)
   beta * t^(beta - 1) * (n0 + 1) * (n0 * y0)^(n0 + 1) * (n0 * y0 + t^beta)^(-n0 - 2)
 
 # prior predictive reliability function, works only for t vectors starting at 0
-prprR <- function(t, n0, y0, beta = 2){
-  dens <- prpr(t = t, n0 = n0, y0 = y0, beta = beta)
+prprRold <- function(t, n0, y0, beta = 2){
+  dens <- pmax(prpr(t = t, n0 = n0, y0 = y0, beta = beta), 0)
   1-cumsum(dens)/(length(t)/max(t)) # divide by evaluation points per unit
 }
 
-nn <- function(n0, fts)
-  n0 + length(fts)
-
-yn <- function(n0, y0, fts, beta, n = length(fts), tnow = max(fts))
-  (n0*y0 + (n - length(fts))*tnow^beta + sum(fts^beta))/(n0 + length(fts))
-# set fts = NULL when no failures occurred
-
-# prior predictive reliability function, works only for t vectors starting at 0
-prprRluck <- function(tvec, luckobj, beta = 2){
-  l1 <- prprR(tvec, n0(luckobj)[1], y0(luckobj)[1], beta)
-  l2 <- prprR(tvec, n0(luckobj)[2], y0(luckobj)[1], beta)
-  u1 <- prprR(tvec, n0(luckobj)[1], y0(luckobj)[2], beta)
-  u2 <- prprR(tvec, n0(luckobj)[2], y0(luckobj)[2], beta)
-  data.frame(tvec = tvec, lower = pmin(l1, l2), upper = pmax(u1, u2))
+# prior predictive reliability function with numerical integration
+prprR <- function(t, n0, y0, beta = 2){
+  1 - sapply(t, function(sgt) integrate(f = prpr, lower = 1e-5, upper = sgt, n0 = n0, y0 = y0, beta = beta)$value)
 }
 
+# prior predictive reliability function with numerical integration, with loop to see where the problem is
+prprRloop <- function(t, n0, y0, beta = 2){
+  res <- numeric(length(t))
+  for (i in 1:length(t)){
+    sgt <- t[i]
+    cat(i, ": t = ", sgt, "\n")
+    res[i] <- 1 - integrate(f = prpr, lower = 1e-5, upper = sgt, n0 = n0, y0 = y0, beta = beta)$value
+  }
+  res
+}
+
[…]

### 2016-07-29 asce-paper.tex
finishing work on examples and examples section

@@
 
-\title{Notes for ISIPTA poster}
-\author{Gero Walter, Frank P.A. Coolen, Simme Douwe Flapper}
-
 \begin{document}
-\title{ROBUST BAYESIAN RELIABILITY FOR COMPLEX SYSTEMS\\ or \ldots}
+\title{ROBUST BAYESIAN RELIABILITY FOR COMPLEX SYSTEMS UNDER PRIOR-DATA CONFLICT}
 
@@
 Eindhoven University of Technology, Eindhoven, The Netherlands.
-E-mail: g.walter@tue.nl.},
+E-mail: g.walter@tue.nl. Corresponding author.},
 \ Ph.D.
@@
 \ Ph.D.
-\\
-and ???
 }
@@
 
-Invited for special issue ``The treatment of uncertainty in risk and reliability modelling and decision making''
-(special issue code SI022A), guest editors Luca Podolfillini, Bruno Sudret, Enrico Zio,
-in ASCE-ASME Journal of Risk and Uncertainty in Engineering Systems: Part A (Civil Engineering)
-
-***``For most ASCE journals, the maximum number of words and word-equivalents is 10,000 for technical papers''
-
-***Abstract must be 150--175 words long (this has 175), may not contain references or mathematics.
-
+%Invited for special issue ``The treatment of uncertainty in risk and reliability modelling and decision making''
+%(special issue code SI022A), guest editors Luca Podolfillini, Bruno Sudret, Enrico Zio,
+%in ASCE-ASME Journal of Risk and Uncertainty in Engineering Systems: Part A (Civil Engineering)
+%
+%***``For most ASCE journals, the maximum number of words and word-equivalents is 10,000 for technical papers''
+%***Abstract must be 150--175 words long (this has 175), may not contain references or mathematics.
+%
 \begin{abstract}
@@
 on a scale of time elapsed since system startup.
-For example, the prior probability of the system to survive until time $10$ is between $***$ and $***$.
+For example, the prior probability of the system to survive until time $10$ is between $0.03$\% and $6.91$\%.
 %calender time scale, where $t = 0$ is the time when the system starts to run.
@@
 \caption{Sets of posterior predictive reliability functions for the four component types
-for observations in line with prior expectations.}
+for observations in line with prior expectations (case~1).}
 \label{fig:comppost-1}
@@
 this is due to the two right-censored observations $t_3^\text{P} = t_4^\text{P} = 8^+$;
-from the prior assumptions, surviving past time 8 is already quite unusual.
+from the viewpoint of the prior, surviving past time 8 is already quite unusual.
 
@@
 
-For the second case, with $t_1^\text{C} = 1$, $t_2^\text{C} = 2$, $t_1^\text{P} = 0.5$, $t_2^\text{P} = 1$
-and $\tnow = 2$, we assume to observe surprisingly early failures;
+For the second case, with $t_1^\text{C} = 1$, $t_2^\text{C} = 2$, $t_1^\text{P} = 0.25$, $t_2^\text{P} = 0.5$
+and $\tnow = 2$ (so $t_1^\text{M} = t_1^\text{H} = t_3^\text{C} = t_4^\text{C} = t_3^\text{P} = t_4^\text{P} = 2^+$),
+we assume to observe surprisingly early failures;
 the corresponding posterior predictive component distributions are given in Figure~\ref{fig:comppost-2}.
-***some discussion***
-
+%
 \begin{figure}
@@
 \caption{Sets of posterior predictive reliability functions for the four component types
-for surprisingly early failures.}
+for surprisingly early failures (case~2).}
 \label{fig:comppost-2}
 \end{figure}
+%
+Having observed the system only until $t = 2$, our data is not very informative,
+such that prior and posterior predictive reliability bounds are very similar.
+For C, the effect of the early failures is however still visible,
+and posterior imprecision, i.e., the range between lower and upper posterior bound, is notably larger
+as compared to prior imprecision, and substantially larger that posterior imprecision in case~1.
+The effect for P is less pronounced,
+mainly because observing $\vec{t}^\text{P} = (0.25, 0.5, 2^+, 2^+)$ for P is not as extreme
+as observing $\vec{t}^\text{C} = (1, 2, 2^+, 2^+)$ for C.
 
@@
 For the third case, we assume to observe surprisingly late failures,
-namely $t_1^\text{C} = 11$, $t_2^\text{C} = 12$, $t_1^\text{P} = 8$, $t_2^\text{P} = 9$, and $\tnow = 12$;
+namely $t_1^\text{C} = 11$, $t_2^\text{C} = 12$, $t_1^\text{P} = 8$, $t_2^\text{P} = 9$,
+and $\tnow = 12$ (so $t_1^\text{M} = t_1^\text{H} = t_3^\text{C} = t_4^\text{C} = t_3^\text{P} = t_4^\text{P} = 12^+$);
 the corresponding posterior predictive component distributions are given in Figure~\ref{fig:comppost-3}.
-***some discussion***
-
+%
 \begin{figure}
@@
 \caption{Sets of posterior predictive reliability functions for the four component types
-for surprisingly late failures.}
+for surprisingly late failures (case~3).}
 \label{fig:comppost-3}
 \end{figure}
+%
+Having observed the system for a much longer time than in case 2,
+our data is much more informative,
+resulting in considerable differences between prior and posterior bounds. %predictive reliability
+The effect of these surprisingly late failures is most prominent for P,
+with a set considerably shifted to the right and having very wide posterior bounds.
+The posterior set for C also indicates that,
+after having seen these late failures, we expect type C components to fail much later.
+This effect is also visible for M and H,
+but is weaker for them as there is only one component of each in the system.
 
@@
 
-Figure~\ref{fig:brake-sysrels} depicts the set of prior system reliability functions,
-together with the sets of posterior system reliability function for the three cases.
-***some discussion***
-
 \begin{figure}
 \includegraphics[width=\textwidth]{fig8}
-\caption{Sets of prior and posterior system reliability functions for the three cases.*** }
+\caption{Sets of prior and posterior system reliability functions for the three cases
+on a time showing time elapsed since system startup.}
 \label{fig:brake-sysrels}
 \end{figure}
-
-Figure~\ref{fig:brake-sysrels-imprecision} shows $\uRsys(t) - \lRsys(t)$ ***
-
+%
+Figure~\ref{fig:brake-sysrels} depicts the set of prior system reliability functions,
+together with the sets of posterior system reliability function for the three cases,
+on a scale of elapsed time since system startup.
+Due to this time scale, posterior system reliability is 1 at $\tnow$,
+as we know that the system has survived until $\tnow = 8, 2, 12$ in each of the three cases.
+For all three cases, the posterior bounds drop faster after $\tnow$ than the prior bounds drop after $t = 0$
+since the components in the system have aged until $\tnow$ and so are expected to fail sooner.
+In the case of surprisingly early failures, posterior bounds are mostly within prior bounds,
+this is due to $\tnow$ being close to $0$ and weakly informative data in this scenario;
+the posterior bounds are nevertheless wider than those for case~1;
+posterior bounds are widest for case~3.
+%
 \begin{figure}
-\centering
-\includegraphics[width=0.8\textwidth]{fig9}
-\caption{Imprecision of prior and posterior system reliability sets.*** }
+%\centering
+\includegraphics[width=\textwidth]{fig9}
+\caption{Imprecision of prior and posterior system reliability sets.}
 \label{fig:brake-sysrels-imprecision}
 \end{figure}
+%
+This most visible in Figure~\ref{fig:brake-sysrels-imprecision},
+which shows $\uRsys(t) - \lRsys(t)$, the difference between upper and lower bound
+of prior and posterior system reliability.
+The left panel shows imprecision on the scale of elapsed time since system startup like in Figure~\ref{fig:brake-sysrels};
+the right panel instead on the scale of prospective time,
+indicating how far in the future periods are for which estimation of system reliability is most uncertain.
+We see that posterior imprecision is indeed considerably lower in case~1,
+where we had observed failures more or less like expected.
+On a prospective timescale, we see that periods of heightened uncertainty are closer to the present for the posteriors,
+while uncertainty is considerably reduced for periods further in the future.
+%This has interesting indications for maintenance planning,
+%where uncertainty about system failure in the near future
 

### 2016-07-29 figures3f.R

@@ -132,7 +132,7 @@ dev.off()
 
 
 # data 2: early failure times ---------------------------------------------------------------- #
-brfts2 <- list(c(1, 2), NULL, NULL, c(0.5, 1))
+brfts2 <- list(c(1, 2), NULL, NULL, c(0.25, 0.5))
 tnow2 <- 2
 
 # components posterior # CHMP
@@ -253,16 +253,32 @@ fig8
 dev.off()
 
 # plot of sysrel prior / posterior imprecision
-fig9 <- ggplot(br4df, aes(x = tvec)) + theme_bw() + ylim(0, 1) + ijarcol + #ijarfill + 
-#  geom_ribbon(aes(ymin = lower, ymax = upper, group = Item, colour = Item, fill = Item), alpha = 0.5) +
-#  geom_line(aes(y = lower, group = Item, colour = Item)) + 
-  geom_line(aes(y = upper-lower, group = interaction(Item, Panel), colour = Item, lty = Panel)) + # facet_wrap(~Panel, nrow=2) + 
-  xlab(expression(t)) + ylab(bquote(bar(R)[sys](t) - ~underline(R)[sys](t)))
+brpost1e <- brpost1
+brpost1e[,1] <- brpost1e[,1] - tnow1
+brpost2e <- brpost2
+brpost2e[,1] <- brpost2e[,1] - tnow2
+brpost3e <- brpost3
+brpost3e[,1] <- brpost3e[,1] - tnow3
+br5df <- rbind(data.frame(br4df, Panel2 = "Elapsed time"),
+               data.frame(brprio,  Panel = "Prior", Item = "Prior", Panel2 = "Prospective time"),
+               #data.frame(brprio,  Panel = "Failures as expected", Item = "Prior", Panel2 = "Prospective time"),
+               data.frame(brpost1e, Panel = "Failures as expected", Item = "Posterior", Panel2 = "Prospective time"),
+               #data.frame(brprio,  Panel = "Surprisingly early failures", Item = "Prior", Panel2 = "Prospective time"),
+               data.frame(brpost2e, Panel = "Surprisingly early failures", Item = "Posterior", Panel2 = "Prospective time"),
+               #data.frame(brprio,  Panel = "Surprisingly late failures", Item = "Prior", Panel2 = "Prospective time"),
[…]

### 2016-07-29 asce-paper.tex
conclusions and acknowledgements

@@
 %
-We present an approach to mitigate this issue, by considering sets of prior distributions
+An approach to mitigate this issue is presented, by considering sets of prior distributions
 to model limited knowledge on Weibull distributed component lifetimes,
 treating systems with arbitary layout using the survival signature.
-Our approach can be seen as a robust Bayesian procedure or imprecise probability method
+This approach can be seen as a robust Bayesian procedure or imprecise probability method
 that reflects surprisingly early or late component failures
@@
 
-***need formal first-order stochastic dominance in $\ykz$ result for $P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$?
-I have it for inverse gamma posterior $f(\lambda_k\mid \nkz,\ykz, \vec{t}^k_{e_k;n_k})$,
-but not for posterior predictive***
-
+%***need formal first-order stochastic dominance in $\ykz$ result for $P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$?
+%I have it for inverse gamma posterior $f(\lambda_k\mid \nkz,\ykz, \vec{t}^k_{e_k;n_k})$,
+%but not for posterior predictive***
+%
 However, there is no corresponding reasoning for $\nkz$,
@@
     \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K P(C^k_t = l_k\mid\nkz,\ykzl, \mbf{t}^k_{e_k;n_k})\,,
+\label{eq:sysrel-optim-n0}
 \end{align}
@@
 
-***if we would also wish to learn about the shape pm, we could follow
-standard Bayesian approaches and use a finite discrete distribution for beta - developing this together
-with suitable sets of priors for lambda, in particular to show the effect of prior-data conflict, is an interesting
-challenge for future research.
-
-***acknowledgements
-
-\pagebreak
+In this paper we presented a robust Bayesian approach to reliability estimation for systems of arbitrary layout,
+and showed how the use of sets of prior distributions results in increased imprecision,
+i.e., more cautious probability statements, in case of prior-data conflict (cases~2 and 3 in Section~\ref{sec:examples}),
+while giving more precise reliability bounds when prior and data are in agreement (case~1 in Section~\ref{sec:examples}).
+The parameters through which prior information is encoded have a clear interpretation
+and are thus easily elicited, either directly or with help of the prior predictive \eqref{eq:tpriopred}.
+Calculation of lower and upper predictive system reliability bounds is tractable,
+requiring only a simple $K$-dimensional box-constrained optimization in Equation~\eqref{eq:sysrel-optim-n0}.
+
+We think that increased imprecision is an appropriate tool for mirroring prior-data conflict
+when considering sets of priors as is done in both the robust Bayesian and imprecise probability framework.
+We want to emphazise, however, that this tool may be useful already
+for just highlighting `conflict' between multiple information sources,
+and that we do not think that the resulting set of posteriors,
+although it can form a meaningful basis, must necessarily be used
+for all consequential inferences, as a strict Bayesian would posit.
+We believe an analyst is free to reconsider any aspect of a model
+(of which the choice of prior can be seen to form a part) after seeing the data,
+and so may use our method only for becoming aware of a conflict between prior and data.
+
+The robust Bayesian setting we employed provides many further modelling opportunities
+beyond the explicit reaction to prior-data conflict.
+These opportunities have not yet been explored and
+provide a wide field for further research.
+An example is our currently ongoing investigation into
+extending the present model to allow also for an appropriate reflection of very strong agreement between prior and data
+\cite{ipmu2016}.
+
+There are many aspects to further develop in our analysis and modeling.
+Straightforward to implement is, e.g., the analysis of the effect of replacing failed components
+in the system on system reliability bounds. %the reliability quantification $[\lRsys(t \mid T > \tnow), \uRsys(t \mid T > \tnow)]$.
+Criteria for the trade-off between the cost of replacement and the gain in reliability
+would have to be adapted for the interval output of our model,
+leading to very interesting research questions.
+%
+To estimate the shape parameters $\beta_k$ together with the scale parameters $\lambda_k$,
+one could follow standard Bayesian approaches and use a finite discrete distribution for $\beta_k$.
+Developing this together with suitable sets of priors for $\lambda_k$,
+in particular to show the effect of prior-data conflict, is another interesting challenge for future research.
+%
+Another further important aspect in system reliability we have not accounted for yet
+is the possibility of common-cause failures,
+i.e., failure events where several components fail at the same time due to a shared or common root cause.
+This could be done by combining the common-cause failure model approaches
+of \citeN{Troffaes2014a} and \citeN{2015:coolen-commoncause}.
+
+On a more abstract level, the choice for the set of prior parameters
+(generating the set of prior component failure distributions) as $[\nkzl, \nkzu] \times [\ykzl, \ykzu]$
+has the advantage of allowing for easy elicitation and tractable inferences,
+but it may not be suitable to reflect certain kinds of prior knowledge.
+Also, as studied in \cite{Walter2011a} and \cite[\S 3.1]{diss},
+the shape of the prior parameter set has a crucial influence on model behaviour
+like the severity of prior-data conflict reaction.
+As noted in \cite[pp.~66f]{diss},
+more general prior parameter set shapes are possible in principle,
+but may be more difficult to elicit and make calculations more complex.
+
+\section*{Acknowledgements}
+
+Gero Walter was supported by the DINALOG project CAMPI
+(``Coordinated Advanced Maintenance and Logistics Planning for the Process Industries'').
+
+%\pagebreak
 %

### 2016-07-29 asce-paper.tex
eliminating a few we's

@@
 but there is some information about failure times for the components the system is made of.
-We are able to analyse systems of arbitrary system structures, %layout of components,
+The proposed method allows to analyse systems of arbitrary system structures, %layout of components,
 i.e., any combination and nesting of series, parallel, k-out-of-n, or bridge-type arrangements,
@@
 i.e., to follow the same failure time distribution.
-We denote components of group $k$ as \emph{type $k$ components},
-and assume independence between component types,
-such that failure times of components of different types are independent.
-We assume that type $k$ component lifetimes $T_i^k$ ($i = 1, \ldots, n_k$)
-are Weibull distributed with type-specific parameters,
+Components of group $k$ are denoted as \emph{type $k$ components},
+and are assumed to be independent from components of other types.
+%such that failure times of components of different types are independent.
+Type $k$ component lifetimes $T_i^k$ ($i = 1, \ldots, n_k$)
+are assumed as Weibull distributed with type-specific parameters,
 where the shape parameter $\beta_k$ is known
@@
 Focusing on a running system,
-we assume that our observations consist solely of the failure times of components in this system up to time $\tnow$,
+we assume that observations consist solely of the failure times of components in this system up to time $\tnow$,
 such that the failure times of components that have not failed by $\tnow$ are right-censored,
@@
 This knowledge is encoded in form of a so-called prior distribution,
-which here, as we assume the shape parameter $\beta_k$ to be known,
+which here, as the shape parameter $\beta_k$ is assumed to be known,
 is a distribution on the scale parameter $\lambda_k$. %of the component lifetime distribution.
-Expert knowledge is especially important when there is very few data on the components (like in our scenario),
+Expert knowledge is especially important when there is very few data on the components, %(like in our scenario),
 as only with its help meaningful estimates for the system reliability can be made.
@@
 
-The work we present here can be seen as belonging to the robust Bayesian approach,
-as our work uses sets of priors. However, our focus and interpretation is slightly different,
+The work presented here can be seen as belonging to the robust Bayesian approach
+since it uses sets of priors. However, our focus and interpretation is slightly different,
 as we consider the result of our procedure, sets of reliability functions, as the proper result,
@@
 Indeed, the system reliability function $\Rsys(t)$ is a collection of probability statements,
-and a small set for $\Rsys(t)$ will indicate that we can quantify the reliability of the system quite precisely,
-while a large set will indicate that our knowledge about $\Tsys$ is rather shaky.
-%
-In line with imprecise or interval probability methods, we will thus have, for each $t$,
+and a small set for $\Rsys(t)$ will indicate that the reliability of the system can be can quantified quite precisely,
+while a large set will indicate that available knowledge about $\Tsys$ is rather shaky.
+%
+In line with imprecise or interval probability methods, the method provides, for each $t$,
 a lower reliability $\lRsys(t) = \ul{P}(T_\text{sys} \geq t)$,
 and an upper reliability $\uRsys(t) = \ol{P}(T_\text{sys} \geq t)$.
-We will explain in Sections~\ref{sec:modforsurpr} and \ref{sec:robrel} how these bounds are obtained
+Sections~\ref{sec:modforsurpr} and \ref{sec:robrel} will explain how these bounds are obtained
 based on sets of prior distributions on the scale parameters of the component lifetime distributions.
 
-The central merit of our method is that it adequately reflects prior-data conflict
+The central merit of the proposed method is that it adequately reflects prior-data conflict
 (see, e.g., \citeNP{2006:evans}),
@@
 and observed behaviour of components in the system under study.
-As we will show in Section~\ref{sec:weibull}, when taking the standard choice of a conjugate prior,
+As will be shown in Section~\ref{sec:weibull}, when taking the standard choice of a conjugate prior,
 prior-data conflict is ignored, as the spread of the posterior distribution does not increase in case of such a conflict,
 ultimately conveying a false sense of certainty
-by communicating that we can quantify the reliability of a system quite precisely when in fact we can not.
-%
-In contrast, our method will indicate prior-data conflict by wider bounds for $\Rsys(t)$.
+by communicating that the reliability of a system can be quantified quite precisely when in fact it can not.
+%
+In contrast, the proposed method will indicate prior-data conflict by wider bounds for $\Rsys(t)$.
 This behaviour is obtained by a specific choice for the set of priors (see \citeNP{Walter2009a} and \citeNP{diss} \S 3.1.4)

### 2016-07-29 asce-paper.tex
more we's, final pass

@@
 by use of the survival signature \cite{2012:survsign}.
+In doing so, the present paper extends similar previous work
+which focused on a simple parallel system with homogeneous components \cite{2015:walter}.
 In this paper, we assume that components can be divided into $K$ different groups,
@@
 
-This work extends \ldots ***
-
-***general methods (sets of conjugate priors, survival signature)
-can be used with other parametric component lifetime distributions
-that form a canonical exponential family
-(see, e.g., \citeNP[p.~202 and 272f]{2000:bernardosmith}, or \citeNP[p.~8]{diss}),
-such that conjugate prior can be constructed***
-
-***We study the effect of surprisingly early or late component failures,
-%on the system reliability prediction,
-showing that observations in conflict to prior assumptions
-indeed lead to more cautious system reliability predictions.***
-
 The paper is organized as follows.
-In Section~\ref{sec:weibull}, we describe a Bayesian analysis for Weibull component lifetimes
-with fixed shape parameter
-and illustrate the issue of prior-data conflict.
+In Section~\ref{sec:weibull}, a Bayesian analysis for Weibull component lifetimes
+with fixed shape parameter is describe,
+illustrating the issue of prior-data conflict.
 Section~\ref{sec:modforsurpr} then details the use of sets of priors
@@
 by giving guidelines on how to choose prior parameter bounds
-that reflect expert information on components;
-Section~\ref{sec:examples} contains examples illustrating the merits of our method.
-Section~\ref{sec:concluding} concludes the paper by *** 
-***
+that reflect expert information on components.
+Section~\ref{sec:examples} contains examples illustrating the merits of our method,
+by studying the effect of surprisingly early or late component failures,
+showing that observations in conflict to prior assumptions
+indeed lead to more cautious system reliability predictions.
+Section~\ref{sec:concluding} concludes the paper by summarizing results
+and indicating avenues for further research.
 
@@
 
-We consider a system with components of $k=1,\ldots,K$ different types;
+Consider a system with components of $k=1,\ldots,K$ different types;
 for each type $k$, there are $n_k$ exchangeable components in the system.
@@
 For encoding expert knowledge about the reliability of the components,
-we need to assign a prior distribution over the scale parameter $\lambda_k$.
+one needs to assign a prior distribution over the scale parameter $\lambda_k$.
 A convenient choice is to use the inverse Gamma distribution,
@@
 and is steeper than the prior (so the pdf is more pointed),
-thus conveying a false sense of certainty about $\lambda$.%
-\footnote{This is a general problem in Bayesian analysis with canonical conjugate priors.
-For such priors, the same update formula \eqref{eq:ig-update} applies,
-and so conflict is averaged out, for details see \citeN{Walter2009a} and \citeN[\S 3.1.4 and \S A.1.2]{diss}.}
+thus conveying a false sense of certainty about $\lambda$.
 We would obtain almost the same %values of $\nfun{2}$ and $\yfun{2}$, and so the same 
@@
 It seems unreasonable to make the same probability statements on component lifetimes in these two fundamentally different scenarios.
+
+Note that this is a general problem in Bayesian analysis with canonical conjugate priors.
+For such priors, the same update formula \eqref{eq:ig-update} applies,
+and so conflict is averaged out, for details see \citeN{Walter2009a} and \citeN[\S 3.1.4 and \S A.1.2]{diss}.
 %
@@
 this corresponds to $[\yzl,\yzu] = [103.13, 154.06]$.
-We also choose $[\nzl,\nzu] =[2, 5]$,
-so we value our prior information as equivalent to having seen two to five observations.
+Choosing $[\nzl,\nzu] =[2, 5]$
+means to value this information on mean component lifetimes as equivalent to having seen two to five observations.
 Compare now the set of posteriors obtained from observing
@@
 and $t_1 = 10$, $t_2 = 11$, see Figure~\ref{fig:setofpost-pdc-nopdc} (right).
-We now have a clear difference between the two scenarios of
+There is now a clear difference between the two scenarios of
 observations in line with expectations and observations in conflict.
@@
 
-We now consider a system of arbitrary layout,
+Consider now a system of arbitrary layout,
 consisting of components of $K$ types.
@@
                                   \big[P(T^k \leq t \mid T^k > \tnow, \lambda_k)\big]^{n_k - e_k - l_k}
-    f(\lambda_k\mid\nkz,\ykz,\vec{t}^k_{e_k;n_k}) \dd \lambda_k
+    f(\lambda_k\mid\nkz,\ykz,\vec{t}^k_{e_k;n_k}) \dd \lambda_k\,.
 \label{eq:postpredtnow}
@@
 %
-Now, by the Weibull assumption \eqref{eq:weibullcdf}, we have
+Now, by the Weibull assumption \eqref{eq:weibullcdf}, one has
 \begin{linenomath*}
@@
 %
-With this and the posterior \eqref{eq:ig-update-alpha} substituted into \eqref{eq:postpredtnow}, we get
+With this and the posterior \eqref{eq:ig-update-alpha} substituted into \eqref{eq:postpredtnow}, this gives
 \begin{linenomath*}
@@
 with parameters $\nkn + 1$ and $\nkn\ykn + (l_k + j) (t^{\beta_k} - (\tnow)^{\beta_k}))$,
-allowing us to solve the integral using the corresponding normalization constant.
+allowing to solve the integral using the corresponding normalization constant.
 We thus have, for $l_k \in \{0,1,\ldots,n_k-e_k\}$,
@@
 Together with \eqref{eq:postpred-priorparams},
-\eqref{eq:sysrel-survsign} allows us to calculate the system reliability $\Rsys(t\mid t>\tnow)$
+\eqref{eq:sysrel-survsign} allows to calculate the system reliability $\Rsys(t\mid t>\tnow)$
 for fixed prior parameters $(\nkz, \ykz)$, $k=1, \ldots, K$.
@@
 a set of priors $\MkZ$ defined by varying $(\nkz,\ykz)$ in a prior parameter set $\PkZ = [\nkzl,\nkzu] \times [\ykzl,\ykzu]$,
-and we are interested in the bounds
+and the objective is to obtain the bounds
 %This leads to a set of system reliability functions with the bounds
@@
 \end{linenomath*}
-where we surpress in notation that $\lRsys(t \mid t > \tnow)$ and $\uRsys(t \mid t > \tnow)$
+where we suppress in notation that $\lRsys(t \mid t > \tnow)$ and $\uRsys(t \mid t > \tnow)$
 depend on prior parameter sets and data.
@@
 and high probability weight for high values of $l_k$. 
-We therefore conclude that, for any fixed value of $\nkz$,
+Therefore, for any fixed value of $\nkz$, 
 the lower bound of $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for all $l_k$ is obtained with $\ykzu$, and
 the upper bound of $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for all $l_k$ is obtained with $\ykzl$.
-
+%
 %***need formal first-order stochastic dominance in $\ykz$ result for $P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$?
@@
 %
-However, there is no corresponding reasoning for $\nkz$,
+There is however no corresponding result for $\nkz$,
 such that different values of $\nkz$ may minimize (or maximize) $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ at different $l_k$'s.
@@
 
-Writing out \eqref{eq:sysrel-survsign}, we get
+Writing out \eqref{eq:sysrel-survsign}, one obtains
 \begin{linenomath*}
@@
 
-We have implemented the method in \textsf{R},
+We have implemented the method in the statistical computing environment \textsf{R} \cite{R},
 using box-constraint optimization via option \texttt{L-BFGS-B} of \texttt{optim},
-and pan to release a package containing the code to reproduce all results and figures
-for the examples in Section~\ref{sec:examples}.
+and intend to release a package containing functions and code to reproduce all results and figures
+for the examples in Section~\ref{sec:examples} below.
 
@@
 through bounds for $\ykz$ and $\nkz$,
-we can refer to the interpretations as given in Section~\ref{sec:weibull}:
+one can refer to the interpretations as given in Section~\ref{sec:weibull}:
 $\ykz$ is the prior expected value of $\lambda_k$,
 where $\lambda_k$ is linked to expected component lifetimes through \eqref{eq:lambdainterpret}.
-$\nkz$ can be seen as pseudocount, indicating how strong expert knwoledge is trusted
+$\nkz$ can be seen as pseudocount, indicating how strong expert knowledge is trusted
 in comparison to a sample of size $n$.
-Our approach allows the expert to give ranges $[\ykzl, \ykzu]$ and $[\nkzl, \nkzu]$
-instead of forcing a precise answer.
+Crucially, the approach allows the expert to give ranges $[\ykzl, \ykzu]$ and $[\nkzl, \nkzu]$
+instead of requiring a precise answer.
 
@@
 %***brake system from ijar paper, Fig.~\ref{fig:brakesys-layout}
-As illustrative example, we consider a simplified automotive brake system with four types of component.
+As illustrative example, consider a simplified automotive brake system with four types of component.
 The master brake cylinder (M) activates all four wheel brake cylinders (C1 -- C4),
@@
 
-We will use same prior setting (described in Section~\ref{sec:ex-prior})
-and combine it with three different data scenarios,
-where we observe failure times in accordance with prior expectations in the first case (Section~\ref{sec:ex-case1}),
+A fixed prior setting, described in Section~\ref{sec:ex-prior},
+will be combined with three different data scenarios,
+where one observes failure times in accordance with prior expectations in the first case (Section~\ref{sec:ex-case1}),
 surprisingly early failures in the second case (Section~\ref{sec:ex-case2}), and
 surprisingly late failures in the third case (Section~\ref{sec:ex-case3}).
-In each case, we assume that C2, C3, P2 and P3 fail, only varying the failure times,
-and study the effect of learning about these failures on the component level.
+In each case, it is assumed that C2, C3, P2 and P3 fail, only the failure times are varied,
+investigating the effect of learning about these failures on the component level.
 %and for the running system.
@@
 
-The prior assumptions, which we can imagine to be determined by an expert,
+The prior assumptions, which one can imagine to be determined by an expert,
 or by a combination of expert knowledge and component test data,
@@
 \caption{Sets of prior predictive reliability functions for the four component types,
-illustrating the choice of prior parameter sets $\PkZ$.}
+illustrating the choice of prior parameter sets $\PkZ$, $k=\text{M}, \text{H}, \text{C}, \text{P}$.}
 \label{fig:brake-comppriors}
@@
 %***Notation as ordered, not to component numbers***
-(Note that we number component failure times by order, not by component number in the system layout.)
+(Note that component failure times are numbered by order, not by component number in the system layout.)
 These observations correspond more or less to prior expectations,
@@
 %
-Having observed the system only until $t = 2$, our data is not very informative,
+Having observed the system only until $t = 2$, the data are not very informative,
 such that prior and posterior predictive reliability bounds are very similar.
@@
 The effect for P is less pronounced,
-mainly because observing $\vec{t}^\text{P} = (0.25, 0.5, 2^+, 2^+)$ for P is not as extreme
+mainly because observing $\vec{t}^\text{P} = (0.25, 0.5, 2^+, 2^+)$ for P is less extreme
 as observing $\vec{t}^\text{C} = (1, 2, 2^+, 2^+)$ for C.
@@
 Having observed the system for a much longer time than in case 2,
-our data is much more informative,
+the data contain now much more information,
 resulting in considerable differences between prior and posterior bounds. %predictive reliability
@@
 The posterior set for C also indicates that,
-after having seen these late failures, we expect type C components to fail much later.
+after having seen these late failures, one expects type C components to fail much later.
 This effect is also visible for M and H,
@@
 Due to this time scale, posterior system reliability is 1 at $\tnow$,
-as we know that the system has survived until $\tnow = 8, 2, 12$ in each of the three cases.
+as it is known that the system has survived until $\tnow = 8, 2, 12$ in case 1,2,3, respectively.
 For all three cases, the posterior bounds drop faster after $\tnow$ than the prior bounds drop after $t = 0$
@@
 The left panel shows imprecision on the scale of elapsed time since system startup like in Figure~\ref{fig:brake-sysrels};
-the right panel instead on the scale of prospective time,
+the right panel shows imprecision on the scale of prospective time instead,
 indicating how far in the future periods are for which estimation of system reliability is most uncertain.
-We see that posterior imprecision is indeed considerably lower in case~1,
-where we had observed failures more or less like expected.
-On a prospective timescale, we see that periods of heightened uncertainty are closer to the present for the posteriors,
+Posterior imprecision is indeed considerably lower in case~1,
+where failure times were more or less like expected.
+On the prospective timescale, one can see that periods of heightened uncertainty are closer to the present for the posteriors,
 while uncertainty is considerably reduced for periods further in the future.
@@
 
-The robust Bayesian setting we employed provides many further modelling opportunities
+The employed robust Bayesian setting provides many further modelling opportunities
 beyond the explicit reaction to prior-data conflict.
@@
 There are many aspects to further develop in our analysis and modeling.
-Straightforward to implement is, e.g., the analysis of the effect of replacing failed components
+The general approaches used in this paper,
+namely the use of sets of conjugate priors for component lifetime models
+and the survival signature to calculate the system reliability
+can be used with other parametric component lifetime distributions
+that form a canonical exponential family,
+since for such distributions, a canonical conjugate prior
+using the same canonical parameters $\nz$ and $\yz$ can be constructed,
+for details see, e.g., \citeN[p.~202 and 272f]{2000:bernardosmith}, or \citeN[p.~8]{diss}.
+%
+Likewise straightforward to implement is, e.g., the analysis of the effect of replacing failed components
 in the system on system reliability bounds. %the reliability quantification $[\lRsys(t \mid T > \tnow), \uRsys(t \mid T > \tnow)]$.
@@
 leading to very interesting research questions.
-%
+
 To estimate the shape parameters $\beta_k$ together with the scale parameters $\lambda_k$,
@@
 in particular to show the effect of prior-data conflict, is another interesting challenge for future research.
-%
+
 Another further important aspect in system reliability we have not accounted for yet

### 2016-07-29 asce-paper.tex
double space for submission
final edits for submission

@@
-\documentclass[Journal,SectionNumbers,SingleSpace,InsideFigs]{ascelike}
+\documentclass[Journal,SectionNumbers,InsideFigs]{ascelike}
+%\documentclass[Journal,SectionNumbers,SingleSpace,InsideFigs]{ascelike}
 
@@
 to model limited knowledge on Weibull distributed component lifetimes,
-treating systems with arbitary layout using the survival signature.
+treating systems with arbitrary layout using the survival signature.
 This approach can be seen as a robust Bayesian procedure or imprecise probability method
@@
 \section{Introduction}
-
+\label{sec:intro}
+%
 In reliability engineering, a central task is to describe the reliability of a complex system.
@@
 giving the probability that the system has not failed by time $t$:
+\begin{linenomath*}
 \begin{align}
@@
 \end{align}
+\end{linenomath*}
 where $\Tsys$ is the random variable giving the failure time of the system. %

### 2016-08-09 asce-paper.tex
changes required by editorial manager

@@
 
+%\usepackage{hyperref}
 %\usepackage[bookmarks]{hyperref}
-\usepackage[colorlinks=true,citecolor=red,linkcolor=black]{hyperref}
+%\usepackage[colorlinks=true,citecolor=red,linkcolor=black]{hyperref}
 
@@
 \thanks{
+Postdoctoral Researcher,
 School of Industrial Engineering,
 Eindhoven University of Technology, Eindhoven, The Netherlands.
-E-mail: g.walter@tue.nl. Corresponding author.},
+E-mail: g.m.walter@tue.nl. Corresponding author.},
 \ Ph.D.
@@
 \thanks{
+Professor,
 Department of Mathematical Sciences,

### 2016-09-15 asce-paper.tex
some typos discovered at re-read

@@
 In Section~\ref{sec:weibull}, a Bayesian analysis for Weibull component lifetimes
-with fixed shape parameter is describe,
+with fixed shape parameter is described,
 illustrating the issue of prior-data conflict.
@@
 $\yn$ is a weighted average of the prior parameter $\yz$ and the maximum likelihood (ML) estimator $\taut/n$,
-with weights $\nz$ and $n$, respectively.
+with weights proportional to $\nz$ and $n$, respectively.
 $\nz$ can thus be interpreted as a prior strength or pseudocount,
@@
 namely the use of sets of conjugate priors for component lifetime models
-and the survival signature to calculate the system reliability
+and the survival signature to calculate the system reliability,
 can be used with other parametric component lifetime distributions

### 2016-10-25 weibull-sys-functions.R
bug in postpredC, need to redo calculations when submitting

@@ -65,7 +65,7 @@ postpredC <- function(n0y0, beta, n, fts, tnow, t, l, prior = FALSE){
     stop("l can be at most n-e")
   nn <- n0y0[1] + e
   if(!prior)
-    nnyn <- n0y0[1]*n0y0[2] + (n-e)*tnow + sum(fts^beta)
+    nnyn <- n0y0[1]*n0y0[2] + (n-e)*(tnow^beta) + sum(fts^beta)
   else
     nnyn <- n0y0[1]*n0y0[2]
   j <- seq(0, n-e-l)

### 2017-05-31 answer-to-reviewers.tex
setup answer to reviewers

\documentclass[Journal,SectionNumbers,InsideFigs]{ascelike}
%\documentclass[Journal,SectionNumbers,SingleSpace,InsideFigs]{ascelike}

%\usepackage{subfigure}
%\usepackage{epsfig}
%\usepackage{timesmt}

\usepackage[utf8]{inputenc}
\usepackage[OT1]{fontenc}
\usepackage{graphicx}
\usepackage[english]{babel}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}

\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{booktabs}
\usepackage{url}
\usepackage{tikz}
%\usetikzlibrary{shapes.misc,fit}
\usetikzlibrary{%
   arrows,%
   calc,%
   fit,%
   patterns,%
   plotmarks,%
   shapes.geometric,%
   shapes.misc,%
   shapes.symbols,%
   shapes.arrows,%
   shapes.callouts,%
   shapes.multipart,%
   shapes.gates.logic.US,%
   shapes.gates.logic.IEC,%
   er,%
   automata,%
   backgrounds,%
   chains,%
   topaths,%
   trees,%
   petri,%
   mindmap,%
   matrix,%
   calendar,%
   folding,%
   fadings,%
   through,%
   patterns,%
   positioning,%
   scopes,%
   decorations.fractals,%
   decorations.shapes,%
   decorations.text,%
   decorations.pathmorphing,%
   decorations.pathreplacing,%
   decorations.footprints,%
   decorations.markings,%
   shadows}

\usepackage{lineno} % comment this out to get line number again
%\usepackage{hyperref}
\usepackage[bookmarks]{hyperref}
%\usepackage[colorlinks=true,citecolor=red,linkcolor=black]{hyperref}

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}
\newcommand{\posrealszero}{\reals_{\ge 0}}
\newcommand{\naturals}{\mathbb{N}}

\newcommand{\dd}{\,\mathrm{d}}

\newcommand{\mbf}[1]{\mathbf{#1}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\renewcommand{\vec}[1]{{\bm#1}}

\newcommand{\uz}{^{(0)}} % upper zero
\newcommand{\un}{^{(n)}} % upper n
\newcommand{\ui}{^{(i)}} % upper i

\newcommand{\ul}[1]{\underline{#1}}
\newcommand{\ol}[1]{\overline{#1}}

\newcommand{\Rsys}{R_\text{sys}}
\newcommand{\lRsys}{\ul{R}_\text{sys}}
\newcommand{\uRsys}{\ol{R}_\text{sys}}

\newcommand{\Fsys}{F_\text{sys}}
\newcommand{\lFsys}{\ul{F}_\text{sys}}
\newcommand{\uFsys}{\ol{F}_\text{sys}}

\def\Rsys{R_\text{sys}}
\def\Tsys{T_\text{sys}}

\newcommand{\E}{\operatorname{E}}
\newcommand{\V}{\operatorname{Var}}
\newcommand{\wei}{\operatorname{Wei}} % Weibull Distribution
\newcommand{\ig}{\operatorname{IG}}   % Inverse Gamma Distribution

\newcommand{\El}{\ul{\operatorname{E}}}
\newcommand{\Eu}{\ol{\operatorname{E}}}

\def\yz{y\uz}
\def\yn{y\un}
%\def\yi{y\ui}
\newcommand{\yfun}[1]{y^{({#1})}}
\newcommand{\yfunl}[1]{\ul{y}^{({#1})}}
\newcommand{\yfunu}[1]{\ol{y}^{({#1})}}

\def\ykz{y\uz_k}
\def\ykn{y\un_k}

\def\yzl{\ul{y}\uz}
\def\yzu{\ol{y}\uz}
\def\ynl{\ul{y}\un}
\def\ynu{\ol{y}\un}
\def\yil{\ul{y}\ui}
\def\yiu{\ol{y}\ui}

\def\ykzl{\ul{y}\uz_k}
\def\ykzu{\ol{y}\uz_k}
\def\yknl{\ul{y}\un_k}
\def\yknu{\ol{y}\un_k}

\newcommand{\ykzfun}[1]{y\uz_{#1}}
\newcommand{\ykzlfun}[1]{\ul{y}\uz_{#1}}
\newcommand{\ykzufun}[1]{\ol{y}\uz_{#1}}

\def\nz{n\uz}
\def\nn{n\un}
%\def\ni{n\ui}
\newcommand{\nfun}[1]{n^{({#1})}}
\newcommand{\nfunl}[1]{\ul{n}^{({#1})}}
\newcommand{\nfunu}[1]{\ol{n}^{({#1})}}

\def\nkz{n\uz_k}
\def\nkn{n\un_k}
\newcommand{\nkzfun}[1]{n\uz_{#1}}
\newcommand{\nkzlfun}[1]{\ul{n}\uz_{#1}}
\newcommand{\nkzufun}[1]{\ol{n}\uz_{#1}}

\def\nzl{\ul{n}\uz}
\def\nzu{\ol{n}\uz}
\def\nnl{\ul{n}\un}
\def\nnu{\ol{n}\un}
\def\nil{\ul{n}\ui}
\def\niu{\ol{n}\ui}

\def\nkzl{\ul{n}\uz_k}
\def\nkzu{\ol{n}\uz_k}
\def\nknl{\ul{n}\un_k}
\def\nknu{\ol{n}\un_k}

\def\taut{\tau(\vec{t})}
\def\ttau{\tilde{\tau}}
\def\ttaut{\ttau(\vec{t})}

\def\MZ{\mathcal{M}\uz}
\def\MN{\mathcal{M}\un}

\def\MkZ{\mathcal{M}\uz_k}
\def\MkN{\mathcal{M}\un_k}

\def\PkZ{\Pi\uz_k}
\def\PkN{\Pi\un_k}
\newcommand{\PZi}[1]{\Pi\uz_{#1}}

\def\tnow{t_\text{now}}
\def\tpnow{t^+_\text{now}}

\newcommand{\comments}[1]{{\small\color{gray} #1}}

\newtheorem{example}{Example}

\allowdisplaybreaks

\begin{document}
\title{RESPONSE TO REVIEWERS' COMMENTS TO OUR MANUSCRIPT RUENG-211}

\author{
Gero Walter%
\thanks{
Postdoctoral Researcher,
School of Industrial Engineering,
Eindhoven University of Technology, Eindhoven, The Netherlands.
E-mail: g.m.walter@tue.nl. Corresponding author.},
\ Ph.D.
\\
and
Frank P.A. Coolen%
\thanks{
Professor,
Department of Mathematical Sciences,
Durham University, Durham, United Kingdom.
E-mail: frank.coolen@durham.ac.uk.},
\ Ph.D.
}

\maketitle

\begin{abstract}
We would like to thank the two anonymous reviewers for their detailed and constructive comments,
and their overall positive votum.
We reproduce their comments here verbatim,
and have numbered the reviewers' comments and questions to allow for easy referencing. 
Our answers are interlaced and typeset in \emph{italic}.
\end{abstract}

\section{Reviewer 1}

\section{Reviewer 2}

\end{document}

### 2017-05-31 answer-to-reviewers.tex
comments reviewer 1 part 1

@@
-\documentclass[Journal,SectionNumbers,InsideFigs]{ascelike}
-%\documentclass[Journal,SectionNumbers,SingleSpace,InsideFigs]{ascelike}
+%\documentclass[Journal,SectionNumbers,InsideFigs]{ascelike}
+\documentclass[Journal,SectionNumbers,SingleSpace,InsideFigs]{ascelike}
 
@@
 
-\section{Reviewer 1}
+\section*{Reviewer 1}
 
-\section{Reviewer 2}
+The authors presented an approach to mitigate the issue of prior-data conflict.
+The idea is to consider sets of prior distributions to model limited knowledge on Weibull distributed component lifetimes,
+and then to model the systems with arbitrary layout using the survival signature.
+As mentioned by the authors the calculation of lower and upper predictive system reliability bounds is tractable.
+
+\smallskip
+
+\emph{***Drop notion of `mitigate', replace with `highlight' / etc? (appears in abstract and end of introduction only) ***\\
+We present a method that explicitly shows, through imprecision in the inferences, when prior and data vary substantially.}
+
+The manuscript is well written, clear and complete. The manuscript is ready to be published.
+However, the authors might want to consider to comment about:
+\begin{enumerate}
+\item how this approach performs compared with existing and traditional approaches
+
+\smallskip
+
+\empħ{We discuss our changes related to existing and traditional approaches in the answers to Reviewer 2's comments below.}
+
+\item are any numerical approaches that can be used to perform system reliability based on the survival signature
+or consider arbitrary distributions for the component failure time?
+\smallskip
+
+\empħ{We are not sure if we have understood this comment well.
+The survival signature allows to calculate the system reliability for arbitrary component lifetime distributions,
+as is clear from Equation~(13), this is explained in detail in the cited reference (Coolen and Coolen-Maturi 2012).
+We have added a sentence to emphasize this fact.}
+\end{enumerate}
+
+Furthermore, at page 15 the authors make a statement that this method has been implemented in R
+and it is intended to be released as a package. Is the code already available?
+
+\section*{Reviewer 2}
 

### 2017-05-31 asce-paper.tex
changes for arxiv submission
setup answer to reviewers
comments reviewer 1 part 1

@@
 
+\usepackage{lineno} % comment this out to get line number again
 %\usepackage{hyperref}
-%\usepackage[bookmarks]{hyperref}
+\usepackage[bookmarks]{hyperref}
 %\usepackage[colorlinks=true,citecolor=red,linkcolor=black]{hyperref}
@@
 %
-An approach to mitigate this issue is presented, by considering sets of prior distributions
+An approach to mitigate/highlight*** this issue is presented, by considering sets of prior distributions
 to model limited knowledge on Weibull distributed component lifetimes,
@@
 for the scale parameter $\lambda_k$ of the Weibull distribution,
-showing how this mitigates the prior-data conflict issue for $\lambda_k$.
+showing how this mitigates / highlights*** the prior-data conflict issue for $\lambda_k$.
 Section~\ref{sec:robrel} then develops a method to calculate system reliability bounds
@@
 
+\newpage
 \section{Robust Reliability for Complex Systems via the Survival Signature}
@@
 and the last equality holds as we assume that components of different types are independent.
+Equation~\ref{eq:sysrel-survsign} shows that the survival signature allows to calculate the system reliability $P(\Tsys > t)$
+for arbitrary component failure time distributions,
+as the probabilities $P(C^k_t = l_k)$ can be determined from any failure time distribution.
 Note that for coherent systems,
 the survival signature $\Phi(l_1,\ldots,l_K)$ is non-decreasing in each $l_k$.
+
 %
@@
 
+\newpage
 \section{Concluding Remarks}

### 2017-05-31 answer-to-reviewers.tex
comments reviewer 1 finished, start comments reviewer 2

@@
 
-\empħ{We discuss our changes related to existing and traditional approaches in the answers to Reviewer 2's comments below.}
+\emph{We discuss our changes related to existing and traditional approaches in the answers to Reviewer 2's comments below.}
 
@@
 or consider arbitrary distributions for the component failure time?
+
 \smallskip
 
-\empħ{We are not sure if we have understood this comment well.
+\emph{We are not sure if we have understood this comment well.
 The survival signature allows to calculate the system reliability for arbitrary component lifetime distributions,
@@
 
+\smallskip
+
+\emph{Yes, it was our intention to provide an \textsf{R} package when we submitted the manuscript.
+A package for calculating survival signatures called \texttt{ReliabilityTheory} is available,
+but for other computations, we were not able to provide a package yet. %Unfortunately, the first author's ***
+However, well-commented code for all computations and fugures is available upon request,
+and is also in the github repository
+\texttt{http://www.github.com/geeeero/asce-asme2016}.***}
+
 \section*{Reviewer 2}
 
+The paper is well written and interesting enough.
+Nonetheless, the products of research are not really new in the fields of Bayesian analysis and reliability analysis.
+In my view, there is a deep lack of bibliographical review,
+and the subject is not sufficiently argued by a detailed case-study
+(typically, there is no real expert information for the case-study considered, and the authors make purely subjective assumptions).
+The Weibull distribution (which is in fact simplified to the Weibull one) is clearly very usual,
+and the conjugate priors and virtual data are usual tools.
+The authors do not detail formally what is a prior-data conflict, while several definitions exist.
+
+\smallskip
+
+\emph{There are several issues here:}
+\begin{enumerate}
+\item \emph{Contrary to the reviewer's suggestion, the work presented in this paper is novel.
+First, prior-data conflict within imprecise probability has not yet been presented within a reliability context.
+Secondly, the combination of imprecise probability methods that can reflect prior data conflict with the survival signature,
+enabling far more large-scale applications than without the use of the survival signature, is novel.}
+\item \emph{Deep lack of bibliographic review:
+there is very little work thus far on imprecise probability methods for prior data conflict, indeed we have referred to it.
+However, as is also clear from the reviewer's later comments,
+the suggestion is probably to extend on literature for prior data conflict in PRECISE Bayesian analysis.
+The paper already contained a clear argument on why precise probabilistic (Bayesian) methods struggle to reflect,
+and deal with, prior-data conflict, while imprecise methods, as shown, can do so in an intuitively attractive way,
+namely by increasing imprecision for an event of interest.
+Nevertheless, the reviewer has pointed us to some interesting papers, for which we are grateful.
+We have included a brief mentioning of two of the suggested papers,
+Bousquet (2008) and O'Hagan and Perrichi (2012), in the introductory section.}
+\item \emph{Detail (or define?) what a prior-data conflict is:
+A formal definition of prior-data conflict for our imprecise probability approach is given in Walter and Augustin (2009, Definition~6). 
+Our approach departs from precise Bayesian methods for identifying prior-data conflict (or agreement)
+by *** ***
+Frank: this is a somewhat interesting point.
+In our case, it effectively is SHOWN by the method when increased imprecision occurs
+which I think is far more attractive than one of the many possible `definitions'.
+But perhaps adding a sentence to the end section (as suggested just above) about possible further research into this may be good.}
+\end{enumerate}
+
 \end{document}

### 2017-05-31 asce-paper.tex
comments reviewer 1 finished, start comments reviewer 2

@@
 current observations in the running system and past observations from component tests.
+
+The topic of prior-data conflict or agreement has of course received attention within the precise Bayesian statistics framework.
+For example, \citeN{2008:bousquet} proposed a method for diagnostics of agreement or disagreement between the prior and data,
+based on a ratio of Kullback-Leibler divergences.
+\citeN{2012:ohagan-pericchi} propose the use of heavy-tailed distributions which,
+in case of conflict between multiple sources of prior information,
+typically provide more weight to one or more of these, when combined with the data,
+than would happen with more commonly used prior distributions.
+While such approaches have some interesting features, e.g. through the quantification of level of disagreement,
+they do not resolve the fundamental issue commented on here,
+namely that the end result of the Bayesian inference remains a single-valued probability
+which is a weighted average of the prior and data inputs.
 
@@
 
+***(we could add something more, e.g.
+that it is interesting for future research to investigate measures of prior-data conflict based on imprecise probabilistic inference or so, perhaps in the concluding remarks section, but I am not sure if that is really needed)***
+
 There are many aspects to further develop in our analysis and modeling.

### 2017-06-04 answer-to-reviewers.tex
finishing comments reviewer 2

@@
 but for other computations, we were not able to provide a package yet. %Unfortunately, the first author's ***
-However, well-commented code for all computations and fugures is available upon request,
-and is also in the github repository
+However, well-commented code for all computations and figures is available upon request,
+and can also be found in the github repository
 \texttt{http://www.github.com/geeeero/asce-asme2016}.***}
@@
 First, prior-data conflict within imprecise probability has not yet been presented within a reliability context.
-Secondly, the combination of imprecise probability methods that can reflect prior data conflict with the survival signature,
+Secondly, the combination of imprecise probability methods that can reflect prior-data conflict with the survival signature,
 enabling far more large-scale applications than without the use of the survival signature, is novel.}
 \item \emph{Deep lack of bibliographic review:
-there is very little work thus far on imprecise probability methods for prior data conflict, indeed we have referred to it.
+there is very little work thus far on imprecise probability methods for prior-data conflict, indeed we have referred to it.
 However, as is also clear from the reviewer's later comments,
-the suggestion is probably to extend on literature for prior data conflict in PRECISE Bayesian analysis.
+the suggestion is probably to extend on literature for prior-data conflict in PRECISE Bayesian analysis.
 The paper already contained a clear argument on why precise probabilistic (Bayesian) methods struggle to reflect,
@@
 \item \emph{Detail (or define?) what a prior-data conflict is:
-A formal definition of prior-data conflict for our imprecise probability approach is given in Walter and Augustin (2009, Definition~6). 
-Our approach departs from precise Bayesian methods for identifying prior-data conflict (or agreement)
-by *** ***
-Frank: this is a somewhat interesting point.
-In our case, it effectively is SHOWN by the method when increased imprecision occurs
-which I think is far more attractive than one of the many possible `definitions'.
-But perhaps adding a sentence to the end section (as suggested just above) about possible further research into this may be good.}
+A formal definition of prior-data conflict in the imprecise probability context is given in Definition~6
+of Walter and Augustin (2009), which we cite in both the Introduction and in Section~3.
+Crucially, our approach is different from precise Bayesian methods for identifying prior-data conflict (or agreement).
+As we explain in Section~3,
+the magnitude of the set of posteriors, as compared to the magnitude of the set of priors,
+reflects the degree of prior-data conflict.
+Prior-data conflict is present when imprecision increases,
+and we think this is a far more attractive notion than any of the many possible definitions in precise Bayesian approaches.
+We have included a short discussion about possible further research into measuring prior-data conflict
+based on imprecise probabilistic inference.}
+\end{enumerate}
+
+The main advantage of this article is that it clearly presents Bayesian robustness (except the decision-theoretical part,
+which is a bit prejudicial), which can be valuable for engineers.
+Therefore the authors should provide, in my view, a more detailed presentation of prior-data conflicts,
+provide more details about the reality of their case-study and go to the final applicability of their methodology.
+A very good point is the production of a software package, but no detail is given about the name and the availability.
+
+\smallskip
+
+\emph{We do not really understand the `except' bit of the first sentence.
+The main issue here is that we do NOT present a case study, and indeed make this already very clear in the text.
+We mention explicitly `examples illustrating' at the end of Section~1,
+and at the start of Section~6, and at the start of Section~6.1 it is clear that these are not really elicited expert opinions.
+On software, please see our comment to Reviewer~1's last question.}
+
+\smallskip
+
+Here are some comments on the text:
+
+\begin{enumerate}
+\item Abstract: The term "straightforward" is to be relaxed, since prior elicitation is clearly not easy to conduct in practice.
+This sentence is contradictory with l.~52, for instance.
+I suspect that the authors are too optimistic since the Weibull case with a known shape parameter is very simplistic.
+
+\smallskip
+\emph{Yes, we agree that the inclusion of expert knowledege is straightforward only in the mathematical sense,
+and have replaced `straightforward' in line 3 of the abstract by `possible'.}
+
+\smallskip
+\item L.~32: Could you define formally what is a ``survival signature''?
+
+\smallskip
+\emph{The survival signature is explained and defined in Section~4.2, ``System Reliability using the Survival Signature'',
+more details are given in the reference Coolen and Coolen-Maturi (2012) cited in line~32 and in Section~4.2.
+As mentioned in our answers to Reviewer 1's comments,
+we have added a sentence to Section~4.2 highlighing the usefulness of the survival signature.}
+
+\smallskip
+\item L.~40 and following. Actually, up to a given parameterisation, all models are exponential since the shape parameters are known.
+According to my experience, this situation appears scarcely.
+This is the first reason why I have doubts on the reality of the motivating case-study (this motivation could besides appear within the Abtract).
+The authors could have a fair description of their model by noticing it.
+
+\smallskip
+\emph{Again, our paper is not a case study.
+The example is chosen to highlight the approach through a simple model, that can be widely understood.
+It being simple does not mean it is not relevant!
+Of course, more complicated models will be of interest for later research building on this,
+in particular towards larger real world applications,
+but the system failure time distribution here is already quite complex as we only make the model assumption at component level.}
+
+\smallskip
+\item P.~6: It is more traditional to use the Gamma prior for 1/lambda rather than the inverse Gamma prior on lambda.
+The reason is that the virtual size $\nz$ can be in fact equal to $a$ (and not $a-1$),
+since it should be possible to have $a<1$ and get a proper prior
+(typically, an expert information could be considered as providing as much information as 1/2 real observation).
+I am not convinced by the choice $\nz=a-1$.
+Besides, a clearer interpretation of the conjugate prior (for all models allowing conjugate priors)
+is the virtual data posterior prior (using an original noninformative Jeffreys prior). See [1] for details and reference therein.
+
+\smallskip
+\emph{Our parametrisation is chosen in order to facilitate the novel prior-data conflict method in the imprecise probabilistic approach.
+We can allow a very small weight of the expert judgements but this would not illustrate (strong) prior data conflict well:
+in order to have prior-data conflict one needs pretty informative priors.
+We do not expand on the non-informative case as that is explicitly not of interest here.}
+
+\smallskip
+\item P.~7: I understand the comparison made by the authors about the prior-data conflict.
+But it can be explained uniquely in terms of posterior sensitivity to a very small amount of virtual (hypothetical) or real data.
+In fact, this is a bit unfair in my view to examine the prior impact alone,
+then the prior and data impact through the posterior, for data which are not sampled by fixed ....as other prior guesses.
+I think that the authors should read more deeply the literature dedicated to prior-data conflict
+(not only the paper by Evans \& Moshonov, but others [2,3]) and summarize their conclusions:
+the conflict can be detected on the sample space, or in the parameter space.
+In the first solution (chosen by Evans \& Moshonov), a conflict can be not detected when the dimension increases,
+because of the possible presence of ancillary statistics.
+Since the authors are working only on a very simplified class of models,
+for which the statistics are exhaustive, this problem remains underlying.
+Furthermore, a large part of the literature is dedicated to create priors
+that lead to robust conclusion in the sense a conflict is removed [4].
+In [3], the symmetric notion of prior-data agreement examines the case of non-conjugate Weibull models,
+and it could give ideas to the authors for improving this part of the article
+(and possibly the conclusion about giving more flexibility to priors;
+it seems that the virtual size $\nz$ could be a useful calibration lever, to modulate for removing a possible conflict).
+
+\smallskip
+\emph{This all comes down again to what one can do within the precise Bayesian framework,
+which remains limited---the authors have certainly read the literature well (see the thesis Walter (2013), e.g.),
+but the reviewer seems to miss the key point:
+the imprecise framework deals fundamentally different with information and prior-data conflict,
+and we claim and illustrate that this has advantages.
+Note also that ``modulating $\nz$'' is not allowed in a careful (precise) Bayesian analysis:
+it would make the prior dependent on the data and as such go against the fundamental principles,
+although of course it is regularly done (e.g. `empirical Bayes') and it seems that researchers get away with this.
+It must be emphasized that the method we present does not make the set of priors dependent on the data
+and as such is fundamentally sound from the (robust) Bayesian perspective.}
+
+\smallskip
+\item P.~10 and Figure~2: It could be interesting to see (graphically) the difference between the approach of the authors
+with a hierarchically Bayesian approach using uniform distributions between the bounds.
+I am not sure that the difference are really high.
+
+\smallskip
+\emph{We do not think it would be that interesting to see any precise distribution in this plot, as it is all about the imprecision.}
+
+\smallskip
+\item L.~270: Place "Equations" before (19) and (20).
+
+\smallskip
+\emph{Yes, thanks, we have done so now.}
+
+\smallskip
+\item L.~293: Of which package do you talk? Other precisions from the submission?
+
+\smallskip
+\emph{Please see our comment to Reviewer~1's last question. We have changed the wording at the end of Section~4 accordingly.}
+
+\smallskip
+\item L.~342: ``One can imagine'' is a bit surprising,
+since it tends to show that the considered case-study was not really examined using expert sollicitation.
+Could the authors give more détails about the questioning,
+or the assumptions made to admit that the results could very likely be arising from real experts?
+
+\smallskip
+\emph{As commented above, we do not present a case study here, and have expressed that very clearly before.}
+
+\smallskip
+\item Section~7: At the image of the full paper, this section is well written and interesting.
+But I think that the authors should be more precise when they talk about the (more reasonable) case of two-parameter Weibull distributions.
+There is a huge work on non-conjugate priors, and I think that the authors could refer to the work evoked hereinbefore,
+among others, to discuss the nature of what could be a good prior for such models.
+
+\smallskip
+\emph{As we point out in Section~7, the paper should be seen as a starting point for more complex and intricate modelling and analysis,
+and that further research would be needed, where the usually used discrete priors for the shape parameter would be a possible starting point.
+However, a more detailed discussion on priors suitable for an imprecise probability approach is out of scope in our view,
+since the requirements for an imprecise modelling approach depart markedly from those in a precise Bayesian approach.}
 \end{enumerate}

### 2017-06-04 asce-paper.tex
finishing comments reviewer 2

@@
 it is therefore often necessary to also include expert information in the analysis,
-which is straightforward in the Bayesian approach by using an informative prior distribution.
+which is possible in the Bayesian approach by using an informative prior distribution.
 %
@@
 
-\eqref{eq:lrsysdef} and \eqref{eq:ursysdef} seem to suggest that
+Equations~\eqref{eq:lrsysdef} and \eqref{eq:ursysdef} seem to suggest that
 a full $2K$-dimensional box-constraint optimization is necessary,
@@
 We have implemented the method in the statistical computing environment \textsf{R} \cite{R},
-using box-constraint optimization via option \texttt{L-BFGS-B} of \texttt{optim},
-and intend to release a package containing functions and code to reproduce all results and figures
-for the examples in Section~\ref{sec:examples} below.
+using box-constraint optimization via option \texttt{L-BFGS-B} of \texttt{optim}.
+Code for reproducing all results and figures for the examples in Section~\ref{sec:examples} below is available upon request.
+%and can also be found in the github repository \texttt{http://www.github.com/geeeero/asce-asme2016}.
 
@@
 \cite{ipmu2016}.
-
-***(we could add something more, e.g.
-that it is interesting for future research to investigate measures of prior-data conflict based on imprecise probabilistic inference or so, perhaps in the concluding remarks section, but I am not sure if that is really needed)***
+Another interesting avenue for future research may be to
+investigate measures of prior-data conflict based on imprecise probabilistic inference.
+These measures could be based on changes in imprecision for certain key probabilities,
+like the system reliability at a prescribed mission time.
 

### 2017-06-05 answer-to-reviewers.tex
formatting done, now work on embedding fonts in figures

@@
 \thanks{
-Postdoctoral Researcher,
 School of Industrial Engineering,
 Eindhoven University of Technology, Eindhoven, The Netherlands.
-E-mail: g.m.walter@tue.nl. Corresponding author.},
-\ Ph.D.
+E-mail: g.m.walter@tue.nl. Corresponding author.}
 \\
@@
 \thanks{
-Professor,
 Department of Mathematical Sciences,
 Durham University, Durham, United Kingdom.
-E-mail: frank.coolen@durham.ac.uk.},
-\ Ph.D.
+E-mail: frank.coolen@durham.ac.uk.}
 }
@@
 As mentioned by the authors the calculation of lower and upper predictive system reliability bounds is tractable.
-
-\smallskip
-
-\emph{***Drop notion of `mitigate', replace with `highlight' / etc? (appears in abstract and end of introduction only) ***\\
-We present a method that explicitly shows, through imprecision in the inferences, when prior and data vary substantially.}
-
 The manuscript is well written, clear and complete. The manuscript is ready to be published.
@@
 and can also be found in the github repository
-\texttt{http://www.github.com/geeeero/asce-asme2016}.***}
+\texttt{http://www.github.com/geeeero/asce-asme2016}.}
 
@@
 \smallskip
-\emph{As commented above, we do not present a case study here, and have expressed that very clearly before.}
+\emph{As commented above, we do not present a case study here, and have expressed that very clearly in the paper.}
 

### 2017-06-05 asce-paper.tex
formatting done, now work on embedding fonts in figures

@@
-\documentclass[Journal,SectionNumbers,InsideFigs]{ascelike}
-%\documentclass[Journal,SectionNumbers,SingleSpace,InsideFigs]{ascelike}
-
-%\usepackage{subfigure}
-%\usepackage{epsfig}
-%\usepackage{timesmt}
-
+\documentclass[Journal,letterpaper]{ascelike-new}
+%\documentclass[Journal,SectionNumbers,InsideFigs]{ascelike}
+%% Please choose the appropriate document class option:
+% "Journal" produces double-spaced manuscripts for ASCE journals.
+% "NewProceedings" produces single-spaced manuscripts for ASCE conference proceedings.
+% "Proceedings" produces older-style single-spaced manuscripts for ASCE conference proceedings. 
+%
+%% For more details and options, please see the notes in the ascelike-new.cls file.
+
+% Some useful packages...
 \usepackage[utf8]{inputenc}
 \usepackage[OT1]{fontenc}
+\usepackage{lmodern}
 \usepackage{graphicx}
 \usepackage[english]{babel}
-
+\usepackage[figurename=Fig.,labelfont=bf,labelsep=period]{caption}
+\usepackage{subcaption}
 \usepackage{amsmath}
@@
 \usepackage{bm}
-
-\usepackage[usenames,dvipsnames]{xcolor}
 \usepackage{booktabs}
@@
    shadows}
-
-\usepackage{lineno} % comment this out to get line number again
-%\usepackage{hyperref}
-\usepackage[bookmarks]{hyperref}
-%\usepackage[colorlinks=true,citecolor=red,linkcolor=black]{hyperref}
-
+%\usepackage{lineno} % comment this out to get line number again
+\usepackage{newtxtext,newtxmath}
+%\usepackage[bookmarks]{hyperref}
+\usepackage[colorlinks=true,citecolor=red,linkcolor=black]{hyperref}
+
+% Shortcuts...
 \newcommand{\reals}{\mathbb{R}}
@@
 
-\allowdisplaybreaks
-
+%\allowdisplaybreaks
+%
+% Please add the first author's last name here for the footer:
+\NameTag{Walter, \today}
+% Note that this is not displayed if the NoPageNumbers option is used
+% in the documentclass declaration.
+%
 \begin{document}
@@
 
-\author{
-Gero Walter%
-\thanks{
-Postdoctoral Researcher,
+\author[1]{Gero Walter}
+\author[2]{Frank P.A. Coolen}
+
+\affil[1]{%
 School of Industrial Engineering,
 Eindhoven University of Technology, Eindhoven, The Netherlands.
-E-mail: g.m.walter@tue.nl. Corresponding author.},
-\ Ph.D.
-\\
-and
-Frank P.A. Coolen%
-\thanks{
-Professor,
+E-mail: g.m.walter@tue.nl.}
+\affil[2]{%
 Department of Mathematical Sciences,
 Durham University, Durham, United Kingdom.
-E-mail: frank.coolen@durham.ac.uk.},
-\ Ph.D.
-}
+E-mail: frank.coolen@durham.ac.uk.}
 
@@
 
-%Invited for special issue ``The treatment of uncertainty in risk and reliability modelling and decision making''
-%(special issue code SI022A), guest editors Luca Podolfillini, Bruno Sudret, Enrico Zio,
-%in ASCE-ASME Journal of Risk and Uncertainty in Engineering Systems: Part A (Civil Engineering)
-%
-%***``For most ASCE journals, the maximum number of words and word-equivalents is 10,000 for technical papers''
-%***Abstract must be 150--175 words long (this has 175), may not contain references or mathematics.
-%
 \begin{abstract}
@@
 %
-An approach to mitigate/highlight*** this issue is presented, by considering sets of prior distributions
+An approach to highlight this issue is presented, by considering sets of prior distributions
 to model limited knowledge on Weibull distributed component lifetimes,
@@
 by wider system reliability bounds.
-%We show how surprisingly early or late component failures
-%result in wider system reliability bounds.
-%
-%and study how surprisingly early or late component failures
-%affect the prediction of the reliability of a system with arbitrary layout,
-%making use of survival signature to characterise the system under study.
-%Our approach can be seen as a robust Bayesian procedure or imprecise probability method
-%that appropriately reflects surprising data in the posterior system reliability function.
 \end{abstract}
-% by communicating that we can quantify the reliability of a system quite precisely when in fact we cannot.
-
-\KeyWords{System Reliability, Imprecise Probability, Survival Signature, Robust Bayesian Methods, Remaining Useful Life}
+
+%\KeyWords{System Reliability, Imprecise Probability, Survival Signature, Robust Bayesian Methods, Remaining Useful Life}
 
@@
 for the scale parameter $\lambda_k$ of the Weibull distribution,
-showing how this mitigates / highlights*** the prior-data conflict issue for $\lambda_k$.
+showing how this highlights the prior-data conflict issue for $\lambda_k$.
 Section~\ref{sec:robrel} then develops a method to calculate system reliability bounds
@@
 \begin{table}
+\caption{Survival signature values $\not\in \{0,1\}$ for the simplified automotive brake system depicted in Figure~\ref{fig:brakesys-layout}.}
+\label{tab:brake-survsign}
 \centering
@@
 0 & 1 & 0 & 2 & 0.83 & & 1 & 1 & 0 & 2 & 0.83 \\ 
-0 & 1 & 1 & 1 & 0.62 & & 1 & 1 & 1 & 1 & 0.62 \\ 
-0 & 1 & 1 & 2 & 0.92 & & 1 & 1 & 1 & 2 & 0.92 \\ 
-0 & 1 & 2 & 1 & 0.75 & & 1 & 1 & 2 & 1 & 0.75 \\ 
-0 & 1 & 2 & 2 & 0.97 & & 1 & 1 & 2 & 2 & 0.97 \\ 
-0 & 1 & 3 & 1 & 0.88 & & 1 & 1 & 3 & 1 & 0.88 \\ 
+0 & 1 & 1 & 1 & 0.50 & & 1 & 1 & 1 & 1 & 0.62 \\ 
+0 & 1 & 1 & 2 & 0.83 & & 1 & 1 & 1 & 2 & 0.92 \\ 
+0 & 1 & 2 & 1 & 0.50 & & 1 & 1 & 2 & 1 & 0.75 \\ 
+0 & 1 & 2 & 2 & 0.83 & & 1 & 1 & 2 & 2 & 0.97 \\ 
+0 & 1 & 3 & 1 & 0.50 & & 1 & 1 & 3 & 1 & 0.88 \\ 
+0 & 1 & 3 & 2 & 0.83 \\
+0 & 1 & 4 & 1 & 0.50 \\
+0 & 1 & 4 & 2 & 0.83 \\
    \bottomrule
 \end{tabular}
-\caption{Survival signature values $\not\in \{0,1\}$ for the simplified automotive brake system depicted in Figure~\ref{fig:brakesys-layout}.}
-\label{tab:brake-survsign}
 \end{table}
@@
 
-\subsection{Prior assumptions}
+\subsection{Prior Assumptions}
 \label{sec:ex-prior}
@@
 \begin{table}
+\caption{Prior parameter sets for the four component types.}
+\label{tab:priorparamsets}
 \centering
@@
 \end{tabular}
-\caption{Prior parameter sets for the four component types.}
-\label{tab:priorparamsets}
 \end{table}
@@
 
-\subsection{Case 1: failure times as expected}
+\subsection{Case 1: Failure Times as Expected}
 \label{sec:ex-case1}
@@
 
-\subsection{Case 2: surprisingly early failure times}
+\subsection{Case 2: Surprisingly Early Failure Times}
 \label{sec:ex-case2}
@@
 
-\subsection{Case 3: surprisingly late failure times}
+\subsection{Case 3: Surprisingly Late Failure Times}
 \label{sec:ex-case3}
@@
 
-\subsection{Reliability bounds for the running system}
+\subsection{Reliability Bounds for the Running System}
 \label{sec:ex-sysrel}

### 2017-06-05 fig3.tex
formatting done, now work on embedding fonts in figures

--- 2017-06-05 asce-paper.tex
@@
-\documentclass[Journal,letterpaper]{ascelike-new}
-%\documentclass[Journal,SectionNumbers,InsideFigs]{ascelike}
-%% Please choose the appropriate document class option:
-% "Journal" produces double-spaced manuscripts for ASCE journals.
-% "NewProceedings" produces single-spaced manuscripts for ASCE conference proceedings.
-% "Proceedings" produces older-style single-spaced manuscripts for ASCE conference proceedings. 
-%
-%% For more details and options, please see the notes in the ascelike-new.cls file.
-
+\documentclass{minimal}
+%\documentclass[Journal,letterpaper]{ascelike-new}
 % Some useful packages...
@@
 \usepackage{newtxtext,newtxmath}
+\usepackage[paperwidth=2.3in,paperheight=2in,margin=0.1in]{geometry}
 %\usepackage[bookmarks]{hyperref}
-\usepackage[colorlinks=true,citecolor=red,linkcolor=black]{hyperref}
+%\usepackage[colorlinks=true,citecolor=red,linkcolor=black]{hyperref}
 
-% Shortcuts...
-\newcommand{\reals}{\mathbb{R}}
-\newcommand{\posreals}{\reals_{>0}}
-\newcommand{\posrealszero}{\reals_{\ge 0}}
-\newcommand{\naturals}{\mathbb{N}}
-
-\newcommand{\dd}{\,\mathrm{d}}
-
-\newcommand{\mbf}[1]{\mathbf{#1}}
-\newcommand{\bs}[1]{\boldsymbol{#1}}
-\renewcommand{\vec}[1]{{\bm#1}}
-
-\newcommand{\uz}{^{(0)}} % upper zero
-\newcommand{\un}{^{(n)}} % upper n
-\newcommand{\ui}{^{(i)}} % upper i
-
-\newcommand{\ul}[1]{\underline{#1}}
-\newcommand{\ol}[1]{\overline{#1}}
-
-\newcommand{\Rsys}{R_\text{sys}}
-\newcommand{\lRsys}{\ul{R}_\text{sys}}
-\newcommand{\uRsys}{\ol{R}_\text{sys}}
-
-\newcommand{\Fsys}{F_\text{sys}}
-\newcommand{\lFsys}{\ul{F}_\text{sys}}
-\newcommand{\uFsys}{\ol{F}_\text{sys}}
-
-\def\Rsys{R_\text{sys}}
-\def\Tsys{T_\text{sys}}
-
-\newcommand{\E}{\operatorname{E}}
-\newcommand{\V}{\operatorname{Var}}
-\newcommand{\wei}{\operatorname{Wei}} % Weibull Distribution
-\newcommand{\ig}{\operatorname{IG}}   % Inverse Gamma Distribution
-
-\newcommand{\El}{\ul{\operatorname{E}}}
-\newcommand{\Eu}{\ol{\operatorname{E}}}
-
-\def\yz{y\uz}
-\def\yn{y\un}
-%\def\yi{y\ui}
-\newcommand{\yfun}[1]{y^{({#1})}}
-\newcommand{\yfunl}[1]{\ul{y}^{({#1})}}
-\newcommand{\yfunu}[1]{\ol{y}^{({#1})}}
-
-\def\ykz{y\uz_k}
-\def\ykn{y\un_k}
-
-\def\yzl{\ul{y}\uz}
-\def\yzu{\ol{y}\uz}
-\def\ynl{\ul{y}\un}
-\def\ynu{\ol{y}\un}
-\def\yil{\ul{y}\ui}
-\def\yiu{\ol{y}\ui}
-
-\def\ykzl{\ul{y}\uz_k}
-\def\ykzu{\ol{y}\uz_k}
-\def\yknl{\ul{y}\un_k}
-\def\yknu{\ol{y}\un_k}
-
-\newcommand{\ykzfun}[1]{y\uz_{#1}}
-\newcommand{\ykzlfun}[1]{\ul{y}\uz_{#1}}
-\newcommand{\ykzufun}[1]{\ol{y}\uz_{#1}}
-
-\def\nz{n\uz}
-\def\nn{n\un}
-%\def\ni{n\ui}
-\newcommand{\nfun}[1]{n^{({#1})}}
-\newcommand{\nfunl}[1]{\ul{n}^{({#1})}}
-\newcommand{\nfunu}[1]{\ol{n}^{({#1})}}
-
-\def\nkz{n\uz_k}
-\def\nkn{n\un_k}
-\newcommand{\nkzfun}[1]{n\uz_{#1}}
-\newcommand{\nkzlfun}[1]{\ul{n}\uz_{#1}}
-\newcommand{\nkzufun}[1]{\ol{n}\uz_{#1}}
-
-\def\nzl{\ul{n}\uz}
-\def\nzu{\ol{n}\uz}
-\def\nnl{\ul{n}\un}
-\def\nnu{\ol{n}\un}
-\def\nil{\ul{n}\ui}
-\def\niu{\ol{n}\ui}
-
-\def\nkzl{\ul{n}\uz_k}
-\def\nkzu{\ol{n}\uz_k}
-\def\nknl{\ul{n}\un_k}
-\def\nknu{\ol{n}\un_k}
-
-\def\taut{\tau(\vec{t})}
-\def\ttau{\tilde{\tau}}
-\def\ttaut{\ttau(\vec{t})}
-
-\def\MZ{\mathcal{M}\uz}
-\def\MN{\mathcal{M}\un}
-
-\def\MkZ{\mathcal{M}\uz_k}
-\def\MkN{\mathcal{M}\un_k}
-
-\def\PkZ{\Pi\uz_k}
-\def\PkN{\Pi\un_k}
-\newcommand{\PZi}[1]{\Pi\uz_{#1}}
-
-\def\tnow{t_\text{now}}
-\def\tpnow{t^+_\text{now}}
-
-\newcommand{\comments}[1]{{\small\color{gray} #1}}
-
-\newtheorem{example}{Example}
-
-%\allowdisplaybreaks
-%
-% Please add the first author's last name here for the footer:
-\NameTag{Walter, \today}
-% Note that this is not displayed if the NoPageNumbers option is used
-% in the documentclass declaration.
-%
 \begin{document}
-\title{ROBUST BAYESIAN RELIABILITY FOR COMPLEX SYSTEMS UNDER PRIOR-DATA CONFLICT}
-
-\author[1]{Gero Walter}
-\author[2]{Frank P.A. Coolen}
-
-\affil[1]{%
-School of Industrial Engineering,
-Eindhoven University of Technology, Eindhoven, The Netherlands.
-E-mail: g.m.walter@tue.nl.}
-\affil[2]{%
-Department of Mathematical Sciences,
-Durham University, Durham, United Kingdom.
-E-mail: frank.coolen@durham.ac.uk.}
-
-\maketitle
-
-\begin{abstract}
-In reliability engineering, data about failure events is often scarce.
-To arrive at meaningful estimates for the reliability of a system,
-it is therefore often necessary to also include expert information in the analysis,
-which is possible in the Bayesian approach by using an informative prior distribution.
-%
-A problem called prior-data conflict then can arise:
-observed data seem very surprising from the viewpoint of the prior,
-i.e., information from data is in conflict with prior assumptions.
-Models based on conjugate priors can be insensitive to prior-data conflict,
-in the sense that the spread of the posterior distribution does not increase in case of such a conflict,
-thus conveying a false sense of certainty.
-%
-An approach to highlight this issue is presented, by considering sets of prior distributions
-to model limited knowledge on Weibull distributed component lifetimes,
-treating systems with arbitrary layout using the survival signature.
-This approach can be seen as a robust Bayesian procedure or imprecise probability method
-that reflects surprisingly early or late component failures
-by wider system reliability bounds.
-\end{abstract}
-
-%\KeyWords{System Reliability, Imprecise Probability, Survival Signature, Robust Bayesian Methods, Remaining Useful Life}
-
-\section{Introduction}
-\label{sec:intro}
-%
-In reliability engineering, a central task is to describe the reliability of a complex system.
-This is usually done by determining the \emph{reliability function} $R(t)$,
-in other contexts also known as the \emph{survival function},
-giving the probability that the system has not failed by time $t$:
-\begin{linenomath*}
-\begin{align}
-\Rsys(t) = P(\Tsys \geq t)\,,
-\end{align}
-\end{linenomath*}
-where $\Tsys$ is the random variable giving the failure time of the system. %
-%\footnote{}
-Based on the distribution of $\Tsys$, which can also be expressed
-in terms of the cumulative distribution function $F_\text{sys}(t) = 1 - \Rsys(t)$,
-%the density $p_\text{sys}(t)$ or the hazard rate $\lambda_\text{sys}(t)$,
-decisions about, e.g., scheduling of maintenance work can be made.
-
-Often, there is no failure data for the system itself
-(e.g., if the system is a prototype, or the system is used under unique circumstances),
-but there is some information about failure times for the components the system is made of.
-The proposed method allows to analyse systems of arbitrary system structures, %layout of components,
-i.e., any combination and nesting of series, parallel, k-out-of-n, or bridge-type arrangements,
-by use of the survival signature \cite{2012:survsign}.
-In doing so, the present paper extends similar previous work
-which focused on a simple parallel system with homogeneous components \cite{2015:walter}.
-In this paper, we assume that components can be divided into $K$ different groups,
-and components within each group $k$ ($k=1, \ldots, K$) can be assumed to be exchangeable,
-i.e., to follow the same failure time distribution.
-Components of group $k$ are denoted as \emph{type $k$ components},
-and are assumed to be independent from components of other types.
-%such that failure times of components of different types are independent.
-Type $k$ component lifetimes $T_i^k$ ($i = 1, \ldots, n_k$)
-are assumed as Weibull distributed with type-specific parameters,
-where the shape parameter $\beta_k$ is known
-and the scale parameter $\lambda_k$ is unknown.
-
-Focusing on a running system,
-we assume that observations consist solely of the failure times of components in this system up to time $\tnow$,
-such that the failure times of components that have not failed by $\tnow$ are right-censored,
-and calculate $\Rsys(t \mid t > \tnow) = P(\Tsys \geq t \mid t > \tnow)$,
-which can be used to determine the remaining useful life of the system
-(in short RUL, see, e.g., \citeNP{2014:rul-review}).
-%This sparse information is complemented by expert information on component lifetimes $T_i^k$.
-
-The Bayesian approach allows to base estimation of the component failure distributions
-on both data and further knowledge not given by the data,
-the latter usually provided in the form of expert knowledge.
-This knowledge is encoded in form of a so-called prior distribution,
-which here, as the shape parameter $\beta_k$ is assumed to be known,
-is a distribution on the scale parameter $\lambda_k$. %of the component lifetime distribution.
-Expert knowledge is especially important when there is very few data on the components, %(like in our scenario),
-as only with its help meaningful estimates for the system reliability can be made.
-%
-Due to the iterative nature of the Bayesian framework,
-it is also possible to use a set of posteriors based on component test data as the set of priors
-instead of a purely expert-based set of priors as discussed so far.
-The component test data may also contain right-censored observations,
-which can be treated in the same way as those from the running system
-(see Section~\ref{sec:lambdawithcens} for details).
-
-The choice of prior distribution to encode given expert knowledge is often debatable,
-and a specific choice of prior is difficult to justify.
-A way to deal with this is to employ sensitivity analysis,
-i.e., studying the effect of different choices of prior distribution on the quantities of interest
-(in our case, the system reliability function, which, in Bayesian terms, is a posterior predictive distribution).
-This idea has been explored in systematic sensitivity analysis, or robust Bayesian methods
-(for an overview on this approach, see, e.g.,
-\citeNP{1994:berger} or \citeNP{2000:rios}). %\citeNP{2005:ruggeri}, \citeNP{2000:bergerinsuaruggeri}
-
-The work presented here can be seen as belonging to the robust Bayesian approach
-since it uses sets of priors. However, our focus and interpretation is slightly different,
-as we consider the result of our procedure, sets of reliability functions, as the proper result,
-while a robust Bayesian would base his analyses on a single reliability function from the set
-in case (s)he was able to conclude that quantities of interest are not `too sensitive' to the choice of prior.
-In contrast, our viewpoint is rooted in the theory of imprecise or interval probability \cite{1991:walley,itip},
-where sets of distributions are used to express the precision of probability statements themselves:
-the smaller the set, the more precise the probability statement.
-Indeed, the system reliability function $\Rsys(t)$ is a collection of probability statements,
-and a small set for $\Rsys(t)$ will indicate that the reliability of the system can be can quantified quite precisely,
-while a large set will indicate that available knowledge about $\Tsys$ is rather shaky.
-%
-In line with imprecise or interval probability methods, the method provides, for each $t$,
-a lower reliability $\lRsys(t) = \ul{P}(T_\text{sys} \geq t)$,
-and an upper reliability $\uRsys(t) = \ol{P}(T_\text{sys} \geq t)$.
-Sections~\ref{sec:modforsurpr} and \ref{sec:robrel} will explain how these bounds are obtained
-based on sets of prior distributions on the scale parameters of the component lifetime distributions.
-
-The central merit of the proposed method is that it adequately reflects prior-data conflict
-(see, e.g., \citeNP{2006:evans}),
-i.e.\ the conflict that can arise between prior assumptions on component lifetimes
-and observed behaviour of components in the system under study.
-As will be shown in Section~\ref{sec:weibull}, when taking the standard choice of a conjugate prior,
-prior-data conflict is ignored, as the spread of the posterior distribution does not increase in case of such a conflict,
-ultimately conveying a false sense of certainty
-by communicating that the reliability of a system can be quantified quite precisely when in fact it can not.
-%
-In contrast, the proposed method will indicate prior-data conflict by wider bounds for $\Rsys(t)$.
-This behaviour is obtained by a specific choice for the set of priors (see \citeNP{Walter2009a} and \citeNP{diss} \S 3.1.4)
-which leads to larger sets of posterior distributions when prior knowledge and data are in conflict
-(see Section~\ref{sec:modforsurpr} for more details).
-If a prior based on component test data is used,
-such prior-data conflict sensitivity furthermore allows to uncover a conflict between
-current observations in the running system and past observations from component tests.
-
-The topic of prior-data conflict or agreement has of course received attention within the precise Bayesian statistics framework.
-For example, \citeN{2008:bousquet} proposed a method for diagnostics of agreement or disagreement between the prior and data,
-based on a ratio of Kullback-Leibler divergences.
-\citeN{2012:ohagan-pericchi} propose the use of heavy-tailed distributions which,
-in case of conflict between multiple sources of prior information,
-typically provide more weight to one or more of these, when combined with the data,
-than would happen with more commonly used prior distributions.
-While such approaches have some interesting features, e.g. through the quantification of level of disagreement,
-they do not resolve the fundamental issue commented on here,
-namely that the end result of the Bayesian inference remains a single-valued probability
-which is a weighted average of the prior and data inputs.
-
-The paper is organized as follows.
-In Section~\ref{sec:weibull}, a Bayesian analysis for Weibull component lifetimes
-with fixed shape parameter is described,
-illustrating the issue of prior-data conflict.
-Section~\ref{sec:modforsurpr} then details the use of sets of priors
-for the scale parameter $\lambda_k$ of the Weibull distribution,
-showing how this highlights the prior-data conflict issue for $\lambda_k$.
-Section~\ref{sec:robrel} then develops a method to calculate system reliability bounds
-for a running system based on sets of priors for $\lambda_k$. 
-%To this end, Bayesian estimation of $\lambda_k$ under right-censored observations is covered in Section~\ref{sec:lambdawithcens},
-%followed by a brief introduction to the survival signature (Section~\ref{sec:sysrelwithsurvsign}).
-%Section~\ref{sec:postpred} then details how gathered information on component lifetimes
-%is transfomed to the necessary form for use within the survival signature framework,
-%and Section~\ref{sec:optimize} explains how lower and upper bounds for $\Rsys(t \mid t > \tnow)$
-%are obtained by efficiently optimizing over the parameter sets that define the sets of priors.
-Section~\ref{sec:elicitation} discusses elicitation,
-by giving guidelines on how to choose prior parameter bounds
-that reflect expert information on components.
-Section~\ref{sec:examples} contains examples illustrating the merits of our method,
-by studying the effect of surprisingly early or late component failures,
-showing that observations in conflict to prior assumptions
-indeed lead to more cautious system reliability predictions.
-Section~\ref{sec:concluding} concludes the paper by summarizing results
-and indicating avenues for further research.
-
-\section{Bayesian Analysis of Weibull Lifetimes}
-\label{sec:weibull}
-
-Consider a system with components of $k=1,\ldots,K$ different types;
-for each type $k$, there are $n_k$ exchangeable components in the system.
-For each type $k$ component, we assume for its lifetime $T_i^k$ ($i=1,\ldots,n_k$, $k = 1, \ldots, K$)
-a Weibull distribution with fixed shape parameter $\beta_k > 0$,
-in short $T_i^k \mid \lambda_k \sim \wei(\beta_k,\lambda_k)$,
-with density and cdf%
-\begin{linenomath*}
-\begin{align}
-\label{eq:weibulldens}
-f(t_i^k \mid \lambda_k) &= \frac{\beta_k}{\lambda_k} (t_i^k)^{\beta_k-1} e^{-\frac{(t_i^k)^{\beta_k}}{\lambda_k}}\,, \\
-\label{eq:weibullcdf}
-F(t_i^k \mid \lambda_k) &= 1 - e^{-\frac{(t_i^k)^{\beta_k}}{\lambda_k}} = P(T_i^k \leq t_i^k \mid \lambda_k)\,,
-\end{align}
-\end{linenomath*}
-where $\lambda_k > 0$ and $t > 0$.
-
-The shape parameter $\beta_k$ determines whether the hazard rate is increasing ($\beta_k > 1$)
-or decreasing ($\beta_k < 1$) over time.
-For $\beta_k=1$, one obtains the Exponential distribution with constant hazard rate as a special case.
-The value for $\beta_k$ will often be clear from practical considerations.
-
-The scale parameter $\lambda_k$ can be interpreted through the relation
-\begin{linenomath*}
-\begin{align}
-\E[T_i^k \mid \lambda_k] &= \lambda_k^{1/\beta_k}\, \Gamma(1 + 1/\beta_k)\,.
-\label{eq:lambdainterpret}
-\end{align}
-\end{linenomath*}
-For encoding expert knowledge about the reliability of the components,
-one needs to assign a prior distribution over the scale parameter $\lambda_k$.
-A convenient choice is to use the inverse Gamma distribution,
-commonly parametrized in terms of the hyperparameters $a_k > 0$ and $b_k > 0$:
-%Conjugate prior is $\lambda_k \sim \ig(a_k,b_k)$:
-\begin{linenomath*}
-\begin{align}
-f(\lambda_k\mid a_k,b_k) &= \frac{(b_k)^{a_k}}{\Gamma(a_k)} \lambda_k^{-a_k -1} e^{-\frac{b_k}{\lambda_k}}
-\label{eq:ig-def}
-\end{align}
-\end{linenomath*}
-in short, $\lambda_k \mid a_k, b_k \sim \ig(a_k,b_k)$.
-The inverse Gamma is convenient because it is a conjugate prior,
-i.e., the posterior obtained by Bayes' rule is again inverse Gamma and thus easily tractable;
-the prior parameters only need to be updated to obtain the posterior parameters.
-
-In the standard Bayesian approach, 
-one has to fix a prior by choosing values for $a_k$ and $b_k$
-to encode specific prior information about component lifetimes.
-In our imprecise approach, we allow instead these parameters
-to vary in a set, this is advantageous also
-because expert knowledge is often vague,
-and it is difficult for the expert(s) to pin down precise hyperparameter values.
-For the definition of the hyperparameter set,
-we use however a parametrization in terms of $\nz > 1$ and $\yz > 0$ instead of $a_k$ and $b_k$,
-where we drop the index $k$ for the discussion about the prior model in the following,
-keeping in mind that each component type will have its own specific parameters.
-We use
-%\begin{linenomath*}
-%\begin{align}
-$\nz = a - 1$ and
-%&
-$\yz = b / \nz$,
-%\end{align}
-%\end{linenomath*}
-where $\yz$ can be interpreted as the prior guess for the scale parameter $\lambda$,
-as $\E[\lambda\mid\nz,\yz] = \yz$.
-This parametrization also makes the nature of the combination
-of prior information and data through Bayes' rule more clear:
-After observing $n$ component lifetimes $\vec{t} = (t_1, \ldots, t_n)$,
-the updated parameters are
-\begin{linenomath*}
-\begin{align}
-\nn &= \nz + n\,, 
-&
-\yn &=  \frac{\nz \yz + \taut}{\nz + n}\,,
-\label{eq:ig-update}
-\end{align}
-\end{linenomath*}
-where $\taut = \sum_{i=1}^n (t_i)^\beta$. %
-%\footnote{
-We thus have
-\begin{linenomath*}
-\begin{align}
-\lambda \mid \nz, \yz, \vec{t} \sim \ig(\nz + n + 1, \nz \yz + \taut). %}
-\label{eq:ig-update-alpha}
-\end{align}
-\end{linenomath*}
-%In terms of canonical parameters $\nkz$ and $\ykz$, we assume $\lambda_k \mid \nkz,\ykz \sim \ig(\nkz + 1, \nkz\ykz)$.
-From the simple update rule \eqref{eq:ig-update}, we see that
-$\yn$ is a weighted average of the prior parameter $\yz$ and the maximum likelihood (ML) estimator $\taut/n$,
-with weights proportional to $\nz$ and $n$, respectively.
-$\nz$ can thus be interpreted as a prior strength or pseudocount,
-indicating how much our prior guess should weigh against the $n$ observations.
-Furthermore, $\V[\lambda\mid\nz,\yz] = (\yz)^2 / (1 - 1/\nz)$,
-so for fixed $\yz$, the higher $\nz$,
-the more probability mass is concentrated around $\yz$. %$p(\lambda\mid\nz,\yz)$
-
-However, the weighted average structure for $\yn$
-is behind the problematic behaviour in case of prior-data conflict.
-Assume that from expert knowledge we expect
-to have a mean component lifetime of 9 weeks.
-Using \eqref{eq:lambdainterpret}, with $\beta=2$ we obtain $\yz = 103.13$.
-We choose $\nz = 2$, so our prior guess for the mean component lifetime
-counts like having two observations with this mean.
-If we now have a sample of two observations
-with surprisingly early failure times $t_1 = 1$ and $t_2 = 2$,
-using \eqref{eq:ig-update} we get $\nfun{2} = 4$
-and $\yfun{2} = \frac{1}{4}(2 \cdot 103.13 + 1^2 + 2^2) = 52.82$,
-so our posterior expectation for the scale parameter $\lambda$ is $52.82$,
-equivalent to a mean component lifetime of $6.44$ weeks.
-The posterior standard deviation (sd) for $\lambda$ is $60.99$.
-Compared to the prior standard deviation of $145.85$,
-the posterior expresses now more confidence that mean lifetimes are around $\yfun{2} = 52.82$
-than the prior had about $\yz = 103.13$.
-This irritating conclusion is illustrated in Figure~\ref{fig:weibull-pdc};
-the posterior cdf is shifted halfway towards the values for $\lambda$
-that the two observations suggest
-(the ML estimator for $\lambda$ would be $2.5$),
-and is steeper than the prior (so the pdf is more pointed),
-thus conveying a false sense of certainty about $\lambda$.
-We would obtain almost the same %values of $\nfun{2}$ and $\yfun{2}$, and so the same 
-posterior distribution
-if we had assumed the mean component lifetime to be 7 weeks (so $\yz = 62.39$),
-and observed lifetimes $t_1 = 6$, $t_2 = 7$ in line with our expectations.
-It seems unreasonable to make the same probability statements on component lifetimes in these two fundamentally different scenarios.
-
-Note that this is a general problem in Bayesian analysis with canonical conjugate priors.
-For such priors, the same update formula \eqref{eq:ig-update} applies,
-and so conflict is averaged out, for details see \citeN{Walter2009a} and \citeN[\S 3.1.4 and \S A.1.2]{diss}.
-%
-%\iffalse
-\begin{figure}
-\centering
-\includegraphics[width=0.8\textwidth]{fig1}
-\caption{Prior and posterior cdf for $\lambda$ given surprising observations;
-the conflict between prior assumptions and data is averaged out,
-with a more pointed posterior giving a false sense of certainty.}
-\label{fig:weibull-pdc}
-\end{figure}
-%\fi
-
-\section{Models reflecting surprising data}
-\label{sec:modforsurpr}
-
-Despite this issue of ignoring prior-data conflict,
-the tractability of the update step
-%(the posterior is again a parametric distribution)
-is a very attractive feature of the conjugate setting.
-As was shown by \citeN{Walter2009a} (see also \citeNP{diss}, \S 3.1),
-it is possible to retain tractability and to have a meaningful reaction to prior-data conflict
-when using sets of priors generated by varying both $\nz$ and $\yz$.
-Then, the magnitude of the set of posteriors,
-and with it the precision of posterior probability statements,
-will be sensitive to the degree of prior-data conflict,
-i.e.\ leading to more cautious probability statements when prior-data conflict occurs.
-
-Instead of a single prior guess $\yz$ for the mean component lifetimes,
-we will now assume a range of prior guesses $[\yzl, \yzu]$, and also a range $[\nzl, \nzu]$ of pseudocounts,
-i.e., we now consider the set of priors
-\begin{linenomath*}
-\begin{align}
-\MZ := \{ f(\lambda\mid\nz,\yz) \mid \nz \in [\nzl, \nzu], \yz \in [\yzl, \yzu] \}
-\label{eq:setofpriors}
-\end{align}
-\end{linenomath*}
-to express our prior knowledge about component lifetimes.
-Each of the priors $f(\lambda\mid\nz,\yz)$ is then updated to the posterior
-$f(\lambda\mid\nz,\yz,\vec{t}) = f(\lambda\mid\nn,\yn)$
-by using \eqref{eq:ig-update},
-such that the set of posteriors $\MN$ can be written as
-$\MN = \{ f(\lambda\mid\nn,\yn) \mid \nz \in [\nzl, \nzu], \yz \in [\yzl, \yzu] \}$.
-This procedure of using Bayes' Rule element by element
-is seen as self-evident in the robust Bayesian literature,
-but can be formally justified as being \emph{coherent}
-(a self-consistency property)
-in the framework of imprecise probability, where it is known as
-\emph{Generalized Bayes' Rule} \cite[\S 6.4]{1991:walley}.
-
-Technically, it is crucial to consider a range of pseudocounts $[\nzl, \nzu]$
-along with the range of prior guesses $[\yzl, \yzu]$,
-as only then $\taut/n \not\in [\yzl, \yzu]$
-leads to the set of posteriors being larger
-and hence reflecting prior-data conflict.
-
-Continuing the example from Section~\ref{sec:weibull} and Figure~\ref{fig:weibull-pdc},
-assume now for the mean component lifetimes the range 9 to 11 weeks,
-this corresponds to $[\yzl,\yzu] = [103.13, 154.06]$.
-Choosing $[\nzl,\nzu] =[2, 5]$
-means to value this information on mean component lifetimes as equivalent to having seen two to five observations.
-Compare now the set of posteriors obtained from observing
-$t_1 = 1$, $t_2 = 2$ (as before), see Figure~\ref{fig:setofpost-pdc-nopdc} (left),
-and $t_1 = 10$, $t_2 = 11$, see Figure~\ref{fig:setofpost-pdc-nopdc} (right).
-There is now a clear difference between the two scenarios of
-observations in line with expectations and observations in conflict.
-In the prior-data conflict case, the set of posteriors (blue)
-is shifted towards the left, but has about the same size as the set of priors (yellow),
-and so posterior quantification of reliability has the same precision,
-despite having seen two observations.
-Instead, in the no conflict case, the set of posteriors is smaller than the set of priors,
-such that the two observations have increased the precision of reliability statements.
-
-\begin{figure}
-\includegraphics[width=\textwidth]{fig2}
-\caption{Set of prior and posterior cdfs for $\lambda$ for two surprising observations $t_1 = 1$, $t_2 = 2$ (left)
-and two unsurprising observations $t_1 = 10$, $t_2 = 11$ (right).}
-\label{fig:setofpost-pdc-nopdc}
-\end{figure}
-
-As each posterior in $\MN$ corresponds to a predictive distribution for $\Tsys$,
-we will have a set of reliability functions $\Rsys(t)$.
-The derivation of $\Rsys(t)$ for systems with $K$ component types and arbitrary layout
-will be given in Section~\ref{sec:robrel} below.
-This will include, in contrast to previous studies using sets of priors of type 
-\eqref{eq:setofpriors}, the treatment of censored observations.
-More specifically, we consider the case of \emph{non-informative right censoring},
-where the censoring process is independent of the failure process.
-
-\newpage
-\section{Robust Reliability for Complex Systems via the Survival Signature}
-\label{sec:robrel}
-
-Consider now a system of arbitrary layout,
-consisting of components of $K$ types.
-This system is observed until time $\tnow$,
-leading to censored observation of lifetimes of components within the system,
-and we will explain in Section~\ref{sec:lambdawithcens}
-how the scale parameter $\lambda_k$ for component type $k$
-can be estimated in this situation.
-%
-Section~\ref{sec:sysrelwithsurvsign} describes then
-how the system reliability function can be efficiently obtained using the survival signature.
-%
-For this, we need the posterior predictive distribution
-of the number of components that function at times $t > \tnow$,
-which we will derive in Section~\ref{sec:postpred}.
-%
-Finally, in Section~\ref{sec:optimize} we describe how
-the lower and upper bound for the system reliability function
-are obtained when prior parameters $(\nkz,\ykz)$
-vary in sets $\PkZ = [\nkzl,\nkzu] \times [\ykzl,\ykzu]$,
-defining sets $\MkZ$ of prior distributions over $\lambda_k$,
-as introduced in Section~\ref{sec:modforsurpr}.
-
-\subsection{Bayesian Estimation of Component Scale Parameter with Right-censored Lifetimes}
-\label{sec:lambdawithcens}
-
-Consider observing a system until $\tnow$,
-where the system has $K$ different types of components,
-and for each type $k$ there are $n_k$ components in the system.
-Denoting the number of type $k$ components that have failed by $\tnow$ by $e_k$,
-there are $n_k - e_k$ components still functioning at $\tnow$.
-We denote the corresponding vector of observations by
-\begin{linenomath*}
-\begin{align}
-\vec{t}^k_{e_k;n_k} &= \big( \underbrace{t^k_1, \ldots, t^k_{e_k}}_{e_k \text{failure times}},
-                             \underbrace{\tpnow, \ldots, \tpnow}_{n_k-e_k \text{censored obs.}} \big)\,,
-\end{align}
-\end{linenomath*}
-where $t^+$ indicates a right-censored observation.
-%
-%***change to general right-censoring? So $n_k-e_k \to c_k$, $e_k+c_k=n_k$,
-%introduce sets of observed and censored?
-
-According to Bayes' rule, multiplying the prior density and the likelihood
-(which accounts for right-censored observations through the cdf terms)
-gives a term proportional to the density of the posterior distribution for $\lambda_k$:
-\begin{linenomath*}
-\begin{align}
-%f_{\lambda_k\mid\ldots}(\lambda_k\mid\nkz,\ykz,\mbf{t}^k_{e_k;n_k})
-% &\propto f_{\lambda_k}(\lambda_k)
-%          \big[ 1- F_k(\tnow\mid\lambda_k) \big]^{n_k-e_k}
-%          \prod_{i=1}^{e_k} f_k(t_i^k \mid \lambda_k) 
-f(\lambda_k\mid\nkz,\ykz,\vec{t}^k_{e_k;n_k})
- &\propto f(\lambda_k)
-          \big[ 1- F(\tnow\mid\lambda_k) \big]^{n_k-e_k}
-          \prod_{i=1}^{e_k} f(t_i^k \mid \lambda_k) 
-\end{align}
-\end{linenomath*}
-Conjugacy is preserved and we get 
-$\lambda_k\mid\nkz,\ykz,\vec{t}^k_{e_k;n_k} \sim \ig(\nkn + 1, \nkn\ykn)$, where
-\begin{linenomath*}
-\begin{align}
-\nkn + 1 &= \nkz + e_k + 1 \\
-\nkn\ykn &= \nkz\ykz + (n_k-e_k) (\tnow)^\beta + \sum_{i=1}^{e_k} (t_i^k)^\beta
-\end{align}
-\end{linenomath*}
-are the updated parameters of the inverse gamma distribution.
-%The posterior expectation for $\lambda_k$ is
-%\begin{linenomath*}
-%\begin{align}
-%\E[\lambda_k\mid\nkn,\ykn] &= \ykn
-%                            = \frac{\nkz}{\nkz + e_k} \ykz +
-%                              \frac{e_k}{\nkz + e_k} \cdot \Big[\frac{n_k-e_k}{e_k} (\tnow)^\beta 
-%                                                                    + \frac{1}{e_k} \sum_{i=1}^{e_k} (t_i^k)^\beta \Big]
-%\end{align}
-%\end{linenomath*}
-
-\subsection{System Reliability using the Survival Signature}
-\label{sec:sysrelwithsurvsign}
-
-The structure of complex systems can be visualized by reliability block diagrams,
-an example is given in Figure~\ref{fig:brakesys-layout}.
-Components are represented by boxes or nodes,
-and the system works when a path from the left end to the right exists
-which passes only through working components.
-In a system with $n$ components, the state of the components can be expressed by the state vector
-$\vec{x} = (x_1,x_2,\ldots,x_n) \in \{0,1\}^n$, with $x_i=1$ if the $i$th component functions 
-and $x_i=0$ if not.
-The structure function $\phi : \{0,1\}^n \rightarrow \{0,1\}$, defined for all possible $\vec{x}$, takes 
-the value 1 if the system functions and 0 if the system does not function for state vector $\vec{x}$
-\cite{BP75}.
-Most real-life systems are coherent,
-which means that $\phi(\vec{x})$ is non-decreasing in any of the components of $\vec{x}$,
-so system functioning cannot be improved by worse performance of one or more of its components.
-Furthermore, one can usually assume that $\phi(0, \ldots, 0) = 0$ and $\phi(1, \ldots, 1) = 1$.
-
-The survival signature \cite{2012:survsign} is a summary of the structure function
-for systems with $K$ groups of exchangeable components.
-Denoted by $\Phi(l_1,\ldots,l_K)$, with $l_k=0,1,\ldots,n_k$ for $k=1,\ldots,K$,
-it is defined as the probability for the event that the system functions
-given that precisely $l_k$ of its $n_k$ components of type $k$ function, for each $k\in \{1,\ldots,K\}$.
-Essentially, this creates a $K$-dimensional partition for the event $\Tsys > t$,
-such that $\Rsys(t) = P(\Tsys > t)$ can be calculated using the law of total probability,
-%System survival calculated by %(see Risk Analysis paper eq. (7))
-\begin{linenomath*}
-\begin{align}
-P(\Tsys > t) &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K)
-                                                                                  P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \nonumber\\
-             &= \sum_{l_1=0}^{n_1} \cdots \sum_{l_K=0}^{n_K} \Phi(l_1,\ldots,l_K) P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \nonumber\\
-%\intertext{ and assuming components of different types are independent,}
-             &= \sum_{l_1=0}^{n_1} \cdots \sum_{l_K=0}^{n_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K P(C^k_t = l_k)\,,
-\label{eq:sysrel-survsign}
-\end{align}
-\end{linenomath*}
-where $P(C^k_t = l_k)$ is the (predictive) probability that exactly $l_k$ components of type $k$ function at time $t$,
-and the last equality holds as we assume that components of different types are independent.
-Equation~\ref{eq:sysrel-survsign} shows that the survival signature allows to calculate the system reliability $P(\Tsys > t)$
-for arbitrary component failure time distributions,
-as the probabilities $P(C^k_t = l_k)$ can be determined from any failure time distribution.
-Note that for coherent systems,
-the survival signature $\Phi(l_1,\ldots,l_K)$ is non-decreasing in each $l_k$.
-
-%
-%A priori, we have, for $l_k = 0,1,\ldots, n_k$,
-%\begin{linenomath*}
-%\begin{align}
-%P(C^k_t = l_k\mid\nkz,\ykz)
-% &= { n_k \choose l_k} \int [F_k(t \mid\lambda_k)]^{n_k-l_k}
-%                        [1 - F_k(t \mid\lambda_k)]^{l_k} f_{\lambda_k}(\lambda_k\mid\nkz,\ykz) \dd \lambda_k
-%\end{align}
-%\end{linenomath*}
-%under the assumption that components of the same type are independent given $\lambda_k$.
-
-\subsection{Posterior Predictive Distribution}
-\label{sec:postpred}
-
-In calculating the system reliability using \eqref{eq:sysrel-survsign},
-the component-specific predictive probabilities $P(C^k_t = l_k)$
-need to use all information available at time $\tnow$,
-which, in the Bayesian framework,
-are given by the posterior predictive distribution 
-$P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$, $l_k = 0, 1, \ldots, n_k-e_k$. %$k=1,\ldots, K$.
-(Remember that $e_k$ type $k$ components have failed by $\tnow$,
-such that there can be at most $n_k-e_k$ working components beyond time $\tnow$.)
-%(Should one work with the subsystem consisting only of the non-failed $n_k - e_k$ components?)\\
-This posterior predictive distribution is obtained as
-\begin{linenomath*}
-\begin{align}
-\lefteqn{%
-P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})}\hspace*{5ex} \nonumber\\  %
- &= { n_k - e_k \choose l_k} \int \big[P(T^k >    t \mid T^k > \tnow, \lambda_k)\big]^{l_k} \times \nonumber\\ & \hspace*{17ex}
-                                  \big[P(T^k \leq t \mid T^k > \tnow, \lambda_k)\big]^{n_k - e_k - l_k}
-    f(\lambda_k\mid\nkz,\ykz,\vec{t}^k_{e_k;n_k}) \dd \lambda_k\,.
-\label{eq:postpredtnow}
-\end{align}
-\end{linenomath*}
-%
-Now, by the Weibull assumption \eqref{eq:weibullcdf}, one has
-\begin{linenomath*}
-\begin{align}
-P(T^k \leq t \mid T^k > \tnow, \lambda_k)
- &= \frac{P(\tnow < T^k \leq t \mid\lambda_k)}{P(T^k > \tnow \mid \lambda_k)} \nonumber\\
- &= \frac{F(t\mid\lambda_k) - F(\tnow\mid\lambda_k)}{1-F(\tnow\mid\lambda_k)} 
-% = \frac{e^{-\frac{(\tnow)^{\beta_k}}{\lambda_k}} - e^{-\frac{t^{\beta_k}}{\lambda_k}}}{e^{-\frac{(\tnow)^{\beta_k}}{\lambda_k}}}
-  = 1 - e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\,.
-\end{align}
-\end{linenomath*}
-%
-With this and the posterior \eqref{eq:ig-update-alpha} substituted into \eqref{eq:postpredtnow}, this gives
-\begin{linenomath*}
-\begin{align}
-\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})}\hspace*{5ex} \nonumber\\
- &= { n_k - e_k \choose l_k} \int \Big[    e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\Big]^{l_k}
-                                  \Big[1 - e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\Big]^{n_k - e_k - l_k}
-    \times \nonumber\\ & \hspace*{27ex}
-    \frac{\big(\nkn\ykn\big)^{\nkn + 1}}{\Gamma(\nkn+1)} \lambda_k^{-(\nkn + 1) - 1} e^{-\frac{\nkn\ykn}{\lambda_k}} \dd \lambda_k \nonumber\\
- &= { n_k - e_k \choose l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j { n_k - e_k - l_k \choose j} \frac{\big(\nkn\ykn\big)^{\nkn + 1}}{\Gamma(\nkn+1)} 
-    \times \nonumber\\ & \hspace*{13ex}
-    \int \lambda_k^{-(\nkn + 1) - 1} \exp\Big\{-\frac{(l_k + j) (t^{\beta_k} - (\tnow)^{\beta_k}) + \nkn\ykn}{\lambda_k}\Big\} \dd \lambda_k\,.
-\end{align}
-\end{linenomath*}
-%
-The terms remaining under the integral form the core of an inverse gamma distribution \eqref{eq:ig-def}
-with parameters $\nkn + 1$ and $\nkn\ykn + (l_k + j) (t^{\beta_k} - (\tnow)^{\beta_k}))$,
-allowing to solve the integral using the corresponding normalization constant.
-We thus have, for $l_k \in \{0,1,\ldots,n_k-e_k\}$,
-\begin{linenomath*}
-\begin{align}
-\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})} \nonumber\\
- &= { n_k - e_k \choose l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j { n_k - e_k - l_k \choose j}
-    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nkn + 1} \nonumber\\
- &= \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!}   
-    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nkn + 1} \nonumber\\
- &= \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!} \times \nonumber\\ & \hspace*{10ex}  
-    \left(\frac{\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^{\beta_k} + (n_k-e_k)       (\tnow)^{\beta_k} }%
-               {\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^{\beta_k} + (n_k-e_k-l_k-j) (\tnow)^{\beta_k} + (l_k + j) t^{\beta_k} }\right)^{%
-    \nkz + e_k + 1}.
-\label{eq:postpred-priorparams}
-\end{align}
-\end{linenomath*}
-%
-These posterior predictive probabilities can also be expressed as a cumulative probability mass function (cmf) 
-\begin{linenomath*}
-\begin{align}
-F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k}) = P(C^k_t \leq l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k}) 
- = \sum_{j=0}^{l_k} P(C^k_t = j \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})\,.
-%F_{C^k_t}(l_k \mid \ldots) = P(C^k_t \leq l_k\mid\ldots) = \sum_{q=0}^{l_k} P(C^k_t = q\mid\ldots)\,,
-\end{align}
-\end{linenomath*}
-%Seen as function in $t$, we see that $t$ appears $n_k-e_k-l_k+1$ times,
-%once in each summand, in the denominator of the fraction powered to the $\nkn+1$,
-%and summands whith even $j$ are decreasing in $t$,
-%while summands whith odd $j$ are increasing in $t$.
-%Nevertheless, in total $P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$
-%must be decreasing in $t$, as the remaining $n_k-e_k$ components continue to age,
-%and so the probability that $l_k$ of them remain operational must decrease.
-
-\subsection{Optimizing over Sets of Parameters}
-\label{sec:optimize}
-
-Together with \eqref{eq:postpred-priorparams},
-\eqref{eq:sysrel-survsign} allows to calculate the system reliability $\Rsys(t\mid t>\tnow)$
-for fixed prior parameters $(\nkz, \ykz)$, $k=1, \ldots, K$.
-In Section~\ref{sec:modforsurpr}, we argued for using sets of priors $\MZ$,
-which allow for vague and incomplete prior knowledge, and provide prior-data conflict sensitivity.
-%
-We will thus use, for each component type,
-a set of priors $\MkZ$ defined by varying $(\nkz,\ykz)$ in a prior parameter set $\PkZ = [\nkzl,\nkzu] \times [\ykzl,\ykzu]$,
-and the objective is to obtain the bounds
-%This leads to a set of system reliability functions with the bounds
-\begin{linenomath*}
-\begin{align}
-\lRsys(t \mid t > \tnow) &= \min_{\PZi{1},\ldots,\PZi{K}} \Rsys\big(t \mid t > \tnow, \cup_{k=1}^K \{\PkZ, \vec{t}^k_{e_k;n_k}\}\big)\,,
-\label{eq:lrsysdef}\\
-\uRsys(t \mid t > \tnow) &= \max_{\PZi{1},\ldots,\PZi{K}} \Rsys\big(t \mid t > \tnow, \cup_{k=1}^K \{\PkZ, \vec{t}^k_{e_k;n_k}\}\big)\,,
-\label{eq:ursysdef}
-\end{align}
-\end{linenomath*}
-where we suppress in notation that $\lRsys(t \mid t > \tnow)$ and $\uRsys(t \mid t > \tnow)$
-depend on prior parameter sets and data.
-
-Equations~\eqref{eq:lrsysdef} and \eqref{eq:ursysdef} seem to suggest that
-a full $2K$-dimensional box-constraint optimization is necessary,
-but this is not the case.
-Remember that $\Phi(l_1,\ldots,l_k)$ from \eqref{eq:sysrel-survsign} is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
-so if there is stochastic dominance in $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$,
-then there is, for each component type $k$,
-a prior parameter pair in $\PkZ$ that minimizes system reliability, and
-a prior parameter pair in $\PkZ$ that maximizes system reliability,
-independently of the other component types. 
-%such that system reliability is
-%minimized by a distribution that gives most weight to low values of $l_k$, and
-%maximized by a distribution that gives most weight to high values of $l_k$.
-Indeed, stochastic dominance in $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ is provided for $\ykz$.
-To see this, note that $\ykz$ gives the mean expected lifetime for type $k$ components.
-Thus, higher values for $\ykz$ mean higher expected lifetimes for the components,
-which in turn increases the probability that many components survive until time $t$,
-and with it, decreases the propability of few or no components surviving,
-so in total giving low probability weight for low values of $l_k$,
-and high probability weight for high values of $l_k$. 
-Therefore, for any fixed value of $\nkz$, 
-the lower bound of $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for all $l_k$ is obtained with $\ykzu$, and
-the upper bound of $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for all $l_k$ is obtained with $\ykzl$.
-%
-%***need formal first-order stochastic dominance in $\ykz$ result for $P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$?
-%I have it for inverse gamma posterior $f(\lambda_k\mid \nkz,\ykz, \vec{t}^k_{e_k;n_k})$,
-%but not for posterior predictive***
-%
-There is however no corresponding result for $\nkz$,
-such that different values of $\nkz$ may minimize (or maximize) $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ at different $l_k$'s.
-Therefore, the $\nkz$ values for lower and upper system reliability bounds are obtained by numeric optimization.
-%
-\iffalse %---------------------------
-\begin{linenomath*}
-\begin{align} \label{eq:25}
-\lefteqn{%
-P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)} \hspace*{10ex}\nonumber\\ 
- &= \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K
-    P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})
-\end{align}
-\end{linenomath*}
-we cannot simply plug in all the $\ul{P}(C^k_t = l_k\mid \ldots)$ %and $\ol{P}(C^k_t = l_k\mid \ldots)$
-to get $\ul{P}(\Tsys > t\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$, % and $\ol{P}(\Tsys > t\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$,
-as the $\ul{P}(C^k_t = l_k\mid \ldots)$ could correspond to different $(\nkz,\ykz)$ for each $l_k$.
-(It would give us a lower bound for $\ul{P}(\Tsys > t\mid\ldots)$, however, but it might be very coarse.)
-%
-While it is clear that the lower bounds for $\ykz$ will lead to the lower system survival function,
-the role of $\nkz$ is not so clear.
-We therefore resort to numerical optimization of \eqref{eq:25} over $\{\nkz, k=1,\ldots,K\}$
-to obtain the lower bound for $P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)$.
-\fi %---------------------------
-
-Writing out \eqref{eq:sysrel-survsign}, one obtains
-\begin{linenomath*}
-\begin{align}
-\lRsys(t \mid t > \tnow)
- &= \min_{\PZi{1},\ldots,\PZi{K}} \Rsys\big(t \mid t > \tnow, \cup_{k=1}^K \{\PkZ, \vec{t}^k_{e_k;n_k}\}\big) \nonumber\\
- &= \min_{\substack{\nkzfun{1} \in \left[\nkzlfun{1}, \nkzufun{1}\right]\\ \vdots\\ \nkzfun{K} \in \left[\nkzlfun{K}, \nkzufun{K}\right]}}
-    \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K P(C^k_t = l_k\mid\nkz,\ykzl, \mbf{t}^k_{e_k;n_k})\,,
-\label{eq:sysrel-optim-n0}
-\end{align}
-\end{linenomath*}
-such that a $K$-dimensional box-constraint optimization is needed to obtain $\lRsys(t \mid t > \tnow)$.
-The result for $\uRsys(t \mid t > \tnow)$ is completely analogous.
-Computing time can furthermore be saved
-by computing only those %$P(C^k_t = l_k\mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for $l_k$'s for which $\Phi(l_1,\ldots,l_K) > 0$
-summation terms for which $\Phi(l_1,\ldots,l_K) > 0$.
-
-\iffalse %---------------------------
-\begin{linenomath*}
-\begin{align}
-\lefteqn{P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)} \\
- &= \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K
-    P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k}) \\
- &= \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K
-    \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!} \times \\ & \hspace*{45ex}
-    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) (t^\kappa - (\tnow)^\kappa)}\right)^{\nkn + 1} \\
- &= \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K \label{eq:30}
-    \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!} \times \\ & \hspace*{17ex}
-    \left(\frac{\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^\kappa + (n_k-e_k) (\tnow)^\kappa }%
-               {\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^\kappa + (n_k-e_k-l_k-j) (\tnow)^\kappa + (l_k + j) t^\kappa }\right)^{%
-    \nkz + e_k + 1} 
-\end{align}
-\end{linenomath*}
-\fi %---------------------------
-
-We have implemented the method in the statistical computing environment \textsf{R} \cite{R},
-using box-constraint optimization via option \texttt{L-BFGS-B} of \texttt{optim}.
-Code for reproducing all results and figures for the examples in Section~\ref{sec:examples} below is available upon request.
-%and can also be found in the github repository \texttt{http://www.github.com/geeeero/asce-asme2016}.
-
-\section{Elicitation of prior parameter sets}
-\label{sec:elicitation}
-
-To represent expert knowledge on component failure times
-through bounds for $\ykz$ and $\nkz$,
-one can refer to the interpretations as given in Section~\ref{sec:weibull}:
-$\ykz$ is the prior expected value of $\lambda_k$,
-where $\lambda_k$ is linked to expected component lifetimes through \eqref{eq:lambdainterpret}.
-$\nkz$ can be seen as pseudocount, indicating how strong expert knowledge is trusted
-in comparison to a sample of size $n$.
-Crucially, the approach allows the expert to give ranges $[\ykzl, \ykzu]$ and $[\nkzl, \nkzu]$
-instead of requiring a precise answer.
-
-It is also possible to directly link $\nkz$ and $\ykz$
-to observed lifetimes using a prior predictive distribution.
-Dropping the component index $k$ for ease of notation, this is given by
-\begin{linenomath*}
-\begin{align}
-f(t\mid \nz, \yz)
- &= \int f(t\mid \lambda) f(\lambda\mid\nz,\yz) \dd \lambda \nonumber\\
- &= \beta\, t^{\beta - 1}\, (\nz + 1) \frac{(\nz \yz)^{\nz + 1}}{(\nz \yz + t^\beta)^{\nz + 2}} \,.
-\label{eq:tpriopred}
-\end{align}
-\end{linenomath*}
-Replacing the prior parameters $\nz$ and $\yz$
-with their posterior counterparts $\nn$ and $\yn$ as defined in \eqref{eq:ig-update},
-the effect of virtual observations on \eqref{eq:tpriopred}, or the corresponding reliability function, can be determined.
-This allows to determine $\nz$ and $\yz$ through a number of `what-if' scenarios,
-by asking the expert to state what (s)he would expect to learn from observing certain virtual data.
-
-This strategy is known as pre-posterior analysis,
-being first advocated by \citeN[p.~19]{1965:good}.
-We recommend to check whether the effects of $\PkZ$ on the inference of interest
-(this may not always be the full reliability function)
-reasonably reflect an expert's beliefs before the data and in case some specific data become available,
-both data agreeing with initial beliefs and surprising data.
-Essentially, we advise to do an analysis like in our examples in Section~\ref{sec:examples} below,
-using hypothetical data.
-
-To elicit a meaningful prior distribution, or a set of prior distributions,
-it is important to ask questions which enable experts to stay close to their actual expertise.
-\citeN{1996:coolen::cens} discussed the possibility of generalizing the usual conjugate prior distributions,
-for parameters of exponential family models, by including pseudo-data which are right-censored.
-If the real data set contains such values, then such generalized priors do not lead to more computational complexities,
-while they can have several advantages.
-In addition to providing slightly more general classes of prior distributions through an additional hyperparameter,
-they may enable more realistic elicitation of expert judgements,
-for example if the expert has no experience with certain components past a specific life time.
-For more details we refer to \citeN{1996:coolen::cens},
-it should be noted that adopting such generalized prior distributions
-may also provide more flexibility for modelling the effects of prior-data conflict,
-this is left as a topic for future research.
-
-\begin{figure}
 \centering
@@
 \end{tikzpicture}
-\caption{Reliability block diagram for a simplified automotive brake system,
-with those components marked that we assume to fail in the three scenarios.}
-\label{fig:brakesys-layout}
-\end{figure}
-
-\section{Examples}
-\label{sec:examples}
-
-%***brake system from ijar paper, Fig.~\ref{fig:brakesys-layout}
-As illustrative example, consider a simplified automotive brake system with four types of component.
-The master brake cylinder (M) activates all four wheel brake cylinders (C1 -- C4),
-which in turn actuate a braking pad assembly each (P1 -- P4).
-The hand brake mechanism (H) goes directly to the brake pad assemblies P3 and P4;
-the car brakes when at least one brake pad assembly is actuated.
-The system layout is depicted in Figure~\ref{fig:brakesys-layout},
-with those components marked that we assume to fail in each of the three cases studied below.
-The values for $\Phi \not\in \{0,1\}$ for the complete system are given in Table~\ref{tab:brake-survsign}.
-
-\begin{table}
-\caption{Survival signature values $\not\in \{0,1\}$ for the simplified automotive brake system depicted in Figure~\ref{fig:brakesys-layout}.}
-\label{tab:brake-survsign}
-\centering
-\begin{tabular}{cccclcccccl}
-  \toprule
-M & H & C & P & $\Phi$ & \quad & M & H & C & P & $\Phi$\\ 
-  \midrule
-1 & 0 & 1 & 1 & 0.25 & & 1 & 0 & 2 & 1 & 0.50 \\ 
-1 & 0 & 1 & 2 & 0.50 & & 1 & 0 & 2 & 2 & 0.83 \\ 
-1 & 0 & 1 & 3 & 0.75 & & 1 & 0 & 3 & 1 & 0.75 \\ 
-0 & 1 & 0 & 1 & 0.50 & & 1 & 1 & 0 & 1 & 0.50 \\ 
-0 & 1 & 0 & 2 & 0.83 & & 1 & 1 & 0 & 2 & 0.83 \\ 
-0 & 1 & 1 & 1 & 0.50 & & 1 & 1 & 1 & 1 & 0.62 \\ 
-0 & 1 & 1 & 2 & 0.83 & & 1 & 1 & 1 & 2 & 0.92 \\ 
-0 & 1 & 2 & 1 & 0.50 & & 1 & 1 & 2 & 1 & 0.75 \\ 
-0 & 1 & 2 & 2 & 0.83 & & 1 & 1 & 2 & 2 & 0.97 \\ 
-0 & 1 & 3 & 1 & 0.50 & & 1 & 1 & 3 & 1 & 0.88 \\ 
-0 & 1 & 3 & 2 & 0.83 \\
-0 & 1 & 4 & 1 & 0.50 \\
-0 & 1 & 4 & 2 & 0.83 \\
-   \bottomrule
-\end{tabular}
-\end{table}
-
-A fixed prior setting, described in Section~\ref{sec:ex-prior},
-will be combined with three different data scenarios,
-where one observes failure times in accordance with prior expectations in the first case (Section~\ref{sec:ex-case1}),
-surprisingly early failures in the second case (Section~\ref{sec:ex-case2}), and
-surprisingly late failures in the third case (Section~\ref{sec:ex-case3}).
-In each case, it is assumed that C2, C3, P2 and P3 fail, only the failure times are varied,
-investigating the effect of learning about these failures on the component level.
-%and for the running system.
-Effects on posterior reliability bounds for the running system
-are then discussed for all three cases in Section~\ref{sec:ex-sysrel}.
-
-\subsection{Prior Assumptions}
-\label{sec:ex-prior}
-
-The prior assumptions, which one can imagine to be determined by an expert,
-or by a combination of expert knowledge and component test data,
-are given by the prior parameter sets $\PkZ$, $k=\text{M}, \text{H}, \text{C}, \text{P}$,
-as described in Table~\ref{tab:priorparamsets}.
-There, $\El[T_i^k]$ and $\Eu[T_i^k]$ give the lower and upper bound for expected component lifetimes, respectively,
-which then have been transformed to bounds for the scale parameter using \eqref{eq:lambdainterpret},
-resulting in $\ykzl$ and $\ykzu$.
-For example, according to the expert, the mean time to failure for component type M is between 5 and 8 time units,
-leading to $\ykzlfun{\text{M}} = 75.4$ and $\ykzufun{\text{M}} = 244.1$,
-and the expert considers his knowledge on these expected lifetime bounds
-as having the strength of at least 2 and at most 5 observations.  
-\begin{table}
-\caption{Prior parameter sets for the four component types.}
-\label{tab:priorparamsets}
-\centering
-\begin{tabular}{crrrrrrr}
-  \toprule
-$k$ & $\beta_k$ & $\El[T_i^k]$ & $\Eu[T_i^k]$ & $\ykzl$ & $\ykzu$ & $\nkzl$ & $\nkzu$ \\
-  \midrule
-M & $2.5$ & $5$\rule{1.5ex}{0ex} & $ 8$\rule{1.5ex}{0ex} & $75.4$ & $244.1$ & $2$\rule{1ex}{0ex} & $ 5$\rule{1ex}{0ex} \\
-H & $1.2$ & $2$\rule{1.5ex}{0ex} & $20$\rule{1.5ex}{0ex} & $ 2.5$ & $ 39.2$ & $1$\rule{1ex}{0ex} & $10$\rule{1ex}{0ex} \\
-C & $2  $ & $8$\rule{1.5ex}{0ex} & $10$\rule{1.5ex}{0ex} & $81.5$ & $127.3$ & $1$\rule{1ex}{0ex} & $ 5$\rule{1ex}{0ex} \\
-P & $1.5$ & $3$\rule{1.5ex}{0ex} & $ 4$\rule{1.5ex}{0ex} & $ 6.1$ & $  9.3$ & $1$\rule{1ex}{0ex} & $10$\rule{1ex}{0ex} \\
-  \bottomrule
-\end{tabular}
-\end{table}
-%For the prior parameter sets $\PZi{\text{M}}$
-
-These prior assumptions for the four component types are visualized in Figure~\ref{fig:brake-comppriors},
-showing the sets of reliability functions corresponding to the prior predictive density \eqref{eq:tpriopred}.
-The figure thus displays the bounds for the probability that a single component,
-having been put under risk at time $0$, will have failed by time $t$.
-The top left graph in Figure~\ref{fig:brake-sysrels} shows what the prior assumptions on components
-signify for the system, depicting the prior bounds for the system reliability %before the system has started
-on a scale of time elapsed since system startup.
-For example, the prior probability of the system to survive until time $10$ is between $0.03$\% and $6.91$\%.
-%calender time scale, where $t = 0$ is the time when the system starts to run.
-
-\begin{figure}
-\includegraphics[width=\textwidth]{fig4}
-\caption{Sets of prior predictive reliability functions for the four component types,
-illustrating the choice of prior parameter sets $\PkZ$, $k=\text{M}, \text{H}, \text{C}, \text{P}$.}
-\label{fig:brake-comppriors}
-\end{figure}
-
-\subsection{Case 1: Failure Times as Expected}
-\label{sec:ex-case1}
-
-In the first case, we observe $t_1^\text{C} = 6$, $t_2^\text{C} = 7$, $t_1^\text{P} = 3$, $t_2^\text{P} = 4$,
-and observe the running system until $\tnow = 8$,
-i.e., $t_1^\text{M} = t_1^\text{H} = t_3^\text{C} = t_4^\text{C} = t_3^\text{P} = t_4^\text{P} = 8^+$.
-%***Notation as ordered, not to component numbers***
-(Note that component failure times are numbered by order, not by component number in the system layout.)
-These observations correspond more or less to prior expectations,
-and the corresponding posterior predictive component distributions are given in Figure~\ref{fig:comppost-1}.
-In analogue to Figure~\ref{fig:brake-comppriors},
-Figure~\ref{fig:comppost-1} displays the bounds for the probability that a single component,
-having been put under risk at time $0$, will have failed by time $t$,
-after having seen these (partly censored) observations.
-For easy comparisons, Figure~\ref{fig:comppost-1} also contains the prior bounds from Figure~\ref{fig:brake-comppriors}.
-
-\begin{figure}
-\includegraphics[width=\textwidth]{fig5a}
-\caption{Sets of posterior predictive reliability functions for the four component types
-for observations in line with prior expectations (case~1).}
-\label{fig:comppost-1}
-\end{figure}
-
-We see that the graphs for M and H do not change dramatically,
-as there is only one component of each in the system to learn from.
-For C, the bounds have considerably narrowed,
-showing the effect of having seen the four observations
-$t_1^\text{C} = 6$, $t_2^\text{C} = 7$, $t_3^\text{C} = t_4^\text{C} = 8^+$.
-The bounds for P have not narrowed as much;
-this is due to the two right-censored observations $t_3^\text{P} = t_4^\text{P} = 8^+$;
-from the viewpoint of the prior, surviving past time 8 is already quite unusual.
-
-\subsection{Case 2: Surprisingly Early Failure Times}
-\label{sec:ex-case2}
-
-For the second case, with $t_1^\text{C} = 1$, $t_2^\text{C} = 2$, $t_1^\text{P} = 0.25$, $t_2^\text{P} = 0.5$
-and $\tnow = 2$ (so $t_1^\text{M} = t_1^\text{H} = t_3^\text{C} = t_4^\text{C} = t_3^\text{P} = t_4^\text{P} = 2^+$),
-we assume to observe surprisingly early failures;
-the corresponding posterior predictive component distributions are given in Figure~\ref{fig:comppost-2}.
-%
-\begin{figure}
-\includegraphics[width=\textwidth]{fig6a}
-\caption{Sets of posterior predictive reliability functions for the four component types
-for surprisingly early failures (case~2).}
-\label{fig:comppost-2}
-\end{figure}
-%
-Having observed the system only until $t = 2$, the data are not very informative,
-such that prior and posterior predictive reliability bounds are very similar.
-For C, the effect of the early failures is however still visible,
-and posterior imprecision, i.e., the range between lower and upper posterior bound, is notably larger
-as compared to prior imprecision, and substantially larger that posterior imprecision in case~1.
-The effect for P is less pronounced,
-mainly because observing $\vec{t}^\text{P} = (0.25, 0.5, 2^+, 2^+)$ for P is less extreme
-as observing $\vec{t}^\text{C} = (1, 2, 2^+, 2^+)$ for C.
-
-\subsection{Case 3: Surprisingly Late Failure Times}
-\label{sec:ex-case3}
-
-For the third case, we assume to observe surprisingly late failures,
-namely $t_1^\text{C} = 11$, $t_2^\text{C} = 12$, $t_1^\text{P} = 8$, $t_2^\text{P} = 9$,
-and $\tnow = 12$ (so $t_1^\text{M} = t_1^\text{H} = t_3^\text{C} = t_4^\text{C} = t_3^\text{P} = t_4^\text{P} = 12^+$);
-the corresponding posterior predictive component distributions are given in Figure~\ref{fig:comppost-3}.
-%
-\begin{figure}
-\includegraphics[width=\textwidth]{fig7a}
-\caption{Sets of posterior predictive reliability functions for the four component types
-for surprisingly late failures (case~3).}
-\label{fig:comppost-3}
-\end{figure}
-%
-Having observed the system for a much longer time than in case 2,
-the data contain now much more information,
-resulting in considerable differences between prior and posterior bounds. %predictive reliability
-The effect of these surprisingly late failures is most prominent for P,
-with a set considerably shifted to the right and having very wide posterior bounds.
-The posterior set for C also indicates that,
-after having seen these late failures, one expects type C components to fail much later.
-This effect is also visible for M and H,
-but is weaker for them as there is only one component of each in the system.
-
-\subsection{Reliability Bounds for the Running System}
-\label{sec:ex-sysrel}
-
-\begin{figure}
-\includegraphics[width=\textwidth]{fig8}
-\caption{Sets of prior and posterior system reliability functions for the three cases
-on a time showing time elapsed since system startup.}
-\label{fig:brake-sysrels}
-\end{figure}
-%
-Figure~\ref{fig:brake-sysrels} depicts the set of prior system reliability functions,
-together with the sets of posterior system reliability function for the three cases,
-on a scale of elapsed time since system startup.
-Due to this time scale, posterior system reliability is 1 at $\tnow$,
-as it is known that the system has survived until $\tnow = 8, 2, 12$ in case 1,2,3, respectively.
-For all three cases, the posterior bounds drop faster after $\tnow$ than the prior bounds drop after $t = 0$
-since the components in the system have aged until $\tnow$ and so are expected to fail sooner.
-In the case of surprisingly early failures, posterior bounds are mostly within prior bounds,
-this is due to $\tnow$ being close to $0$ and weakly informative data in this scenario;
-the posterior bounds are nevertheless wider than those for case~1;
-posterior bounds are widest for case~3.
-%
-\begin{figure}
-%\centering
-\includegraphics[width=\textwidth]{fig9}
-\caption{Imprecision of prior and posterior system reliability sets.}
-\label{fig:brake-sysrels-imprecision}
-\end{figure}
-%
-This most visible in Figure~\ref{fig:brake-sysrels-imprecision},
-which shows $\uRsys(t) - \lRsys(t)$, the difference between upper and lower bound
-of prior and posterior system reliability.
-The left panel shows imprecision on the scale of elapsed time since system startup like in Figure~\ref{fig:brake-sysrels};
-the right panel shows imprecision on the scale of prospective time instead,
-indicating how far in the future periods are for which estimation of system reliability is most uncertain.
-Posterior imprecision is indeed considerably lower in case~1,
-where failure times were more or less like expected.
-On the prospective timescale, one can see that periods of heightened uncertainty are closer to the present for the posteriors,
-while uncertainty is considerably reduced for periods further in the future.
-%This has interesting indications for maintenance planning,
-%where uncertainty about system failure in the near future
-
-\newpage
-\section{Concluding Remarks}
-\label{sec:concluding}
-
-In this paper we presented a robust Bayesian approach to reliability estimation for systems of arbitrary layout,
-and showed how the use of sets of prior distributions results in increased imprecision,
-i.e., more cautious probability statements, in case of prior-data conflict (cases~2 and 3 in Section~\ref{sec:examples}),
-while giving more precise reliability bounds when prior and data are in agreement (case~1 in Section~\ref{sec:examples}).
-The parameters through which prior information is encoded have a clear interpretation
-and are thus easily elicited, either directly or with help of the prior predictive \eqref{eq:tpriopred}.
-Calculation of lower and upper predictive system reliability bounds is tractable,
-requiring only a simple $K$-dimensional box-constrained optimization in Equation~\eqref{eq:sysrel-optim-n0}.
-
-We think that increased imprecision is an appropriate tool for mirroring prior-data conflict
-when considering sets of priors as is done in both the robust Bayesian and imprecise probability framework.
-We want to emphazise, however, that this tool may be useful already
-for just highlighting `conflict' between multiple information sources,
-and that we do not think that the resulting set of posteriors,
-although it can form a meaningful basis, must necessarily be used
-for all consequential inferences, as a strict Bayesian would posit.
-We believe an analyst is free to reconsider any aspect of a model
-(of which the choice of prior can be seen to form a part) after seeing the data,
-and so may use our method only for becoming aware of a conflict between prior and data.
-
-The employed robust Bayesian setting provides many further modelling opportunities
-beyond the explicit reaction to prior-data conflict.
-These opportunities have not yet been explored and
-provide a wide field for further research.
-An example is our currently ongoing investigation into
-extending the present model to allow also for an appropriate reflection of very strong agreement between prior and data
-\cite{ipmu2016}.
-Another interesting avenue for future research may be to
-investigate measures of prior-data conflict based on imprecise probabilistic inference.
-These measures could be based on changes in imprecision for certain key probabilities,
-like the system reliability at a prescribed mission time.
-
-There are many aspects to further develop in our analysis and modeling.
-The general approaches used in this paper,
-namely the use of sets of conjugate priors for component lifetime models
-and the survival signature to calculate the system reliability,
-can be used with other parametric component lifetime distributions
-that form a canonical exponential family,
-since for such distributions, a canonical conjugate prior
-using the same canonical parameters $\nz$ and $\yz$ can be constructed,
-for details see, e.g., \citeN[p.~202 and 272f]{2000:bernardosmith}, or \citeN[p.~8]{diss}.
-%
-Likewise straightforward to implement is, e.g., the analysis of the effect of replacing failed components
-in the system on system reliability bounds. %the reliability quantification $[\lRsys(t \mid T > \tnow), \uRsys(t \mid T > \tnow)]$.
-Criteria for the trade-off between the cost of replacement and the gain in reliability
-would have to be adapted for the interval output of our model,
-leading to very interesting research questions.
-
-To estimate the shape parameters $\beta_k$ together with the scale parameters $\lambda_k$,
-one could follow standard Bayesian approaches and use a finite discrete distribution for $\beta_k$.
-Developing this together with suitable sets of priors for $\lambda_k$,
-in particular to show the effect of prior-data conflict, is another interesting challenge for future research.
-
-Another further important aspect in system reliability we have not accounted for yet
-is the possibility of common-cause failures,
-i.e., failure events where several components fail at the same time due to a shared or common root cause.
-This could be done by combining the common-cause failure model approaches
-of \citeN{Troffaes2014a} and \citeN{2015:coolen-commoncause}.
-
-On a more abstract level, the choice for the set of prior parameters
-(generating the set of prior component failure distributions) as $[\nkzl, \nkzu] \times [\ykzl, \ykzu]$
-has the advantage of allowing for easy elicitation and tractable inferences,
-but it may not be suitable to reflect certain kinds of prior knowledge.
-Also, as studied in \cite{Walter2011a} and \cite[\S 3.1]{diss},
-the shape of the prior parameter set has a crucial influence on model behaviour
-like the severity of prior-data conflict reaction.
-As noted in \cite[pp.~66f]{diss},
-more general prior parameter set shapes are possible in principle,
-but may be more difficult to elicit and make calculations more complex.
-
-\section*{Acknowledgements}
-
-Gero Walter was supported by the DINALOG project CAMPI
-(``Coordinated Advanced Maintenance and Logistics Planning for the Process Industries'').
-
-%\pagebreak
-%
-%
-% Now we start the appendices, with the new section name, "Appendix", and a 
-%  new counter, "I", "II", etc.
-%
-\appendix\label{section:references}
-%
-% Here's the first appendix, the list of references:
-%
-\bibliography{refs}
-%
-%\cite{key}   produces citations with full author list and year 
-%\citeNP{key} produces citations with full author list and year, but without enclosing parentheses
-%\citeA{key}  produces citations with only the full author list
-%\citeN{key}  produces citations with the full author list and year, but
-%             which can be used as nouns in a sentence; no parentheses appear around
-%             the author names, but only around the year
-%\citeyear{key}   produces the year information only, within parentheses
-%\citeyearNP{key} produces the year information only
-%
-%
-% And now for some pretty impressive notation.  In this example, I have used
-%   the tabular environment to line up the columns in ASCE style.
-%   Note that this and all appendices (except the references) start with 
-%   the \section command
-%
-\iffalse
-\section{Notation}
-\emph{The following symbols are used in this paper:}%\par\vspace{0.10in}
-\nopagebreak
-\par
-\begin{tabular}{r  @{\hspace{1em}=\hspace{1em}}  l}
-$D$                    & pile diameter (m); \\
-$R$                    & distance (m);      and\\
-$C_{\mathrm{Oh\;no!}}$ & fudge factor.
-\end{tabular}
-\fi
-
 \end{document}

### 2017-06-05 figures3f.R

@@ -76,7 +76,7 @@ fig4 # warnings refer to the four instances which have been rounded down to 1, b
 pdf("fig4.pdf", width=8, height=6)
 fig4
 dev.off()
-
+#embed_fonts("fig4.pdf")
 
 # data 1: fitting failure times ---------------------------------------------------------------- #
 brfts1 <- list(c(6, 7), NULL, NULL, c(3, 4))
@@ -276,9 +276,9 @@ fig9 <- ggplot(br5df, aes(x = tvec)) + theme_bw() + ylim(0, 1) + ijarcol + right
   facet_wrap(~Panel2, nrow=1) + xlab(expression(t)) + ylab(bquote(bar(R)[sys](t) - ~underline(R)[sys](t)))
 fig9
 
-#setEPS()
-#postscript("fig9.eps",width=8,height=6)
-pdf("fig9.pdf", width=8, height=3)
+setEPS()
+postscript("fig9.eps",width=8,height=3)
+#pdf("fig9.pdf", width=8, height=3)
 fig9
 dev.off()
 

### 2017-06-05 plotdefs.R

@@ -9,4 +9,7 @@ ijarcols <- c("#b2df8a", "#1f78b4")
 ijarcol <- scale_colour_manual(values = ijarcols)
 ijarfill <- scale_fill_manual(values = ijarcols)
 
+library(extrafont)
+#font_import()
+loadfonts()
 #

### 2017-06-05 figure1.R
fonts embedded using the showtext package

@@ -42,7 +42,9 @@ fig1 <- ggplot(fig1df, aes(x=x)) + geom_line(aes(y=y, group=p, colour=p)) + ylim
 #setEPS()
 #postscript("fig1.eps",width=5,height=3)
 pdf("fig1.pdf",width=6,height=3)
+showtext.begin()
 fig1
+showtext.end()
 dev.off()
 
 #

### 2017-06-05 figure2.R

@@ -47,8 +47,8 @@ weidf <- function(prior, data, tvec){
                            levels = c("Prior", "Posterior")))
 }
 
-fig2data2 <- weidf(forfig2, data2, tvec)
-fig2data3 <- weidf(forfig2, data3, tvec)
+fig2data2 <- weidf(forfig2, data2, lvec)
+fig2data3 <- weidf(forfig2, data3, lvec)
 fig2df <- rbind(data.frame(fig2data2, Panel = "Surprising Observations"),
                 data.frame(fig2data3, Panel = "Unsurprising Observations"))
 
@@ -61,7 +61,9 @@ fig2 <- ggplot(fig2df, aes(x = l)) + theme_bw() + ijarcol + ijarfill + ylim(0, 1
 #setEPS()
 #postscript("fig2.eps",width=8,height=3)
 pdf("fig2.pdf", width=8, height=3)
+showtext.begin()
 fig2
+showtext.end()
 dev.off()
 
 

### 2017-06-05 figures3f.R

@@ -74,9 +74,11 @@ fig4 # warnings refer to the four instances which have been rounded down to 1, b
 #setEPS()
 #postscript("fig4.eps",width=8,height=6)
 pdf("fig4.pdf", width=8, height=6)
+showtext.begin()
 fig4
+showtext.end()
 dev.off()
-#embed_fonts("fig4.pdf")
+#embed_fonts("fig4.pdf") # has problems with transparency
 
 # data 1: fitting failure times ---------------------------------------------------------------- #
 brfts1 <- list(c(6, 7), NULL, NULL, c(3, 4))
@@ -106,7 +108,9 @@ fig5a <- ggplot(popr1df, aes(x = tvec)) + theme_bw() + ijarcol + ijarfill + ylim
 fig5a # warnings refer to the instances which have been rounded down to 1, bug in ggplot?
 
 pdf("fig5a.pdf", width=8, height=6)
+showtext.begin()
 fig5a
+showtext.end()
 dev.off()
 
 # posterior system reliability function at tnow = 8
@@ -154,8 +158,11 @@ fig6a <- ggplot(popr2df, aes(x = tvec)) + theme_bw() + ijarcol + ijarfill + ylim
   geom_line(aes(y = upper, group = Item, colour = Item)) + 
   facet_wrap(~Part, nrow=2) + xlab(expression(t)) + ylab(expression(R(t))) + rightlegend 
 fig6a # warnings refer to the instances which have been rounded down to 1, bug in ggplot?
+
 pdf("fig6a.pdf", width=8, height=6)
+showtext.begin()
 fig6a
+showtext.end()
 dev.off()
 
 # posterior system reliability function at tnow = 2
@@ -203,8 +210,11 @@ fig7a <- ggplot(popr3df, aes(x = tvec)) + theme_bw() + ijarcol + ijarfill + ylim
   geom_line(aes(y = upper, group = Item, colour = Item)) + 
   facet_wrap(~Part, nrow=2) + xlab(expression(t)) + ylab(expression(R(t))) + rightlegend 
 fig7a # warnings refer to the instances which have been rounded down to 1, bug in ggplot?
+
 pdf("fig7a.pdf", width=8, height=6)
+showtext.begin()
 fig7a
+showtext.end()
 dev.off()
 
 # posterior system reliability function at tnow = 12
[…]

### 2017-06-05 plotdefs.R

@@ -9,7 +9,21 @@ ijarcols <- c("#b2df8a", "#1f78b4")
 ijarcol <- scale_colour_manual(values = ijarcols)
 ijarfill <- scale_fill_manual(values = ijarcols)
 
-library(extrafont)
+#library(extrafont) # has problems with transparency in figures
 #font_import()
-loadfonts()
+#loadfonts()
+
+#install.packages("showtext")
+#library(showtext)
+#old = setwd(tempdir())
+#download.file("http://downloads.sourceforge.net/project/cm-unicode/cm-unicode/0.7.0/cm-unicode-0.7.0-ttf.tar.xz",
+#              "cm-unicode-0.7.0-ttf.tar.xz")
+#untar("cm-unicode-0.7.0-ttf.tar.xz", compressed = "xz")
+#setwd("cm-unicode-0.7.0")
+#font.add("CM Roman",
+#         regular = "cmunrm.ttf",
+#         italic = "cmunti.ttf",
+#         symbol = "cmunti.ttf")
+#setwd(old)
+
 #

### 2017-06-05 asce-paper.tex
final changes in tex for submission

@@
 (for an overview on this approach, see, e.g.,
-\citeNP{1994:berger} or \citeNP{2000:rios}). %\citeNP{2005:ruggeri}, \citeNP{2000:bergerinsuaruggeri}
+\citeNP{1994:berger} or \citeNP{2000:rios}).
 
@@
 for a running system based on sets of priors for $\lambda_k$. 
-%To this end, Bayesian estimation of $\lambda_k$ under right-censored observations is covered in Section~\ref{sec:lambdawithcens},
-%followed by a brief introduction to the survival signature (Section~\ref{sec:sysrelwithsurvsign}).
-%Section~\ref{sec:postpred} then details how gathered information on component lifetimes
-%is transfomed to the necessary form for use within the survival signature framework,
-%and Section~\ref{sec:optimize} explains how lower and upper bounds for $\Rsys(t \mid t > \tnow)$
-%are obtained by efficiently optimizing over the parameter sets that define the sets of priors.
 Section~\ref{sec:elicitation} discusses elicitation,
@@
 and so conflict is averaged out, for details see \citeN{Walter2009a} and \citeN[\S 3.1.4 and \S A.1.2]{diss}.
-%
-%\iffalse
+
 \begin{figure}
@@
 \end{figure}
-%\fi
 
@@
 the tractability of the update step
-%(the posterior is again a parametric distribution)
 is a very attractive feature of the conjugate setting.
@@
 where $t^+$ indicates a right-censored observation.
-%
-%***change to general right-censoring? So $n_k-e_k \to c_k$, $e_k+c_k=n_k$,
-%introduce sets of observed and censored?
 
@@
 such that $\Rsys(t) = P(\Tsys > t)$ can be calculated using the law of total probability,
-%System survival calculated by %(see Risk Analysis paper eq. (7))
 \begin{linenomath*}
@@
 the survival signature $\Phi(l_1,\ldots,l_K)$ is non-decreasing in each $l_k$.
-
-%
-%A priori, we have, for $l_k = 0,1,\ldots, n_k$,
-%\begin{linenomath*}
-%\begin{align}
-%P(C^k_t = l_k\mid\nkz,\ykz)
-% &= { n_k \choose l_k} \int [F_k(t \mid\lambda_k)]^{n_k-l_k}
-%                        [1 - F_k(t \mid\lambda_k)]^{l_k} f_{\lambda_k}(\lambda_k\mid\nkz,\ykz) \dd \lambda_k
-%\end{align}
-%\end{linenomath*}
-%under the assumption that components of the same type are independent given $\lambda_k$.
 
@@
 such that there can be at most $n_k-e_k$ working components beyond time $\tnow$.)
-%(Should one work with the subsystem consisting only of the non-failed $n_k - e_k$ components?)\\
 This posterior predictive distribution is obtained as
@@
 \end{linenomath*}
-%Seen as function in $t$, we see that $t$ appears $n_k-e_k-l_k+1$ times,
-%once in each summand, in the denominator of the fraction powered to the $\nkn+1$,
-%and summands whith even $j$ are decreasing in $t$,
-%while summands whith odd $j$ are increasing in $t$.
-%Nevertheless, in total $P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$
-%must be decreasing in $t$, as the remaining $n_k-e_k$ components continue to age,
-%and so the probability that $l_k$ of them remain operational must decrease.
 
@@
 independently of the other component types. 
-%such that system reliability is
-%minimized by a distribution that gives most weight to low values of $l_k$, and
-%maximized by a distribution that gives most weight to high values of $l_k$.
 Indeed, stochastic dominance in $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ is provided for $\ykz$.
@@
 the upper bound of $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for all $l_k$ is obtained with $\ykzl$.
-%
-%***need formal first-order stochastic dominance in $\ykz$ result for $P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$?
-%I have it for inverse gamma posterior $f(\lambda_k\mid \nkz,\ykz, \vec{t}^k_{e_k;n_k})$,
-%but not for posterior predictive***
-%
 There is however no corresponding result for $\nkz$,
@@
 
-%\pagebreak
-%
+\pagebreak
 %
@@
 %  new counter, "I", "II", etc.
-%
-\appendix\label{section:references}
-%
-% Here's the first appendix, the list of references:
-%
+\appendix
+%
+%
+% Here's the list of references:
+%
+% \label{section:references}
 \bibliography{refs}
 %
-%\cite{key}   produces citations with full author list and year 
-%\citeNP{key} produces citations with full author list and year, but without enclosing parentheses
-%\citeA{key}  produces citations with only the full author list
-%\citeN{key}  produces citations with the full author list and year, but
-%             which can be used as nouns in a sentence; no parentheses appear around
-%             the author names, but only around the year
-%\citeyear{key}   produces the year information only, within parentheses
-%\citeyearNP{key} produces the year information only
-%
-%
-% And now for some pretty impressive notation.  In this example, I have used
-%   the tabular environment to line up the columns in ASCE style.
-%   Note that this and all appendices (except the references) start with 
-%   the \section command
-%
-\iffalse
-\section{Notation}
-\emph{The following symbols are used in this paper:}%\par\vspace{0.10in}
-\nopagebreak
-\par
-\begin{tabular}{r  @{\hspace{1em}=\hspace{1em}}  l}
-$D$                    & pile diameter (m); \\
-$R$                    & distance (m);      and\\
-$C_{\mathrm{Oh\;no!}}$ & fudge factor.
-\end{tabular}
-\fi
-
 \end{document}

### 2017-12-09 asce-revision-final.tex
Frank's revision of secs1-3

--- 2017-06-05 asce-paper.tex
@@
 \begin{abstract}
-In reliability engineering, data about failure events is often scarce.
-To arrive at meaningful estimates for the reliability of a system,
-it is therefore often necessary to also include expert information in the analysis,
-which is possible in the Bayesian approach by using an informative prior distribution.
-%
-A problem called prior-data conflict then can arise:
-observed data seem very surprising from the viewpoint of the prior,
-i.e., information from data is in conflict with prior assumptions.
-Models based on conjugate priors can be insensitive to prior-data conflict,
-in the sense that the spread of the posterior distribution does not increase in case of such a conflict,
-thus conveying a false sense of certainty.
-%
-An approach to highlight this issue is presented, by considering sets of prior distributions
-to model limited knowledge on Weibull distributed component lifetimes,
-treating systems with arbitrary layout using the survival signature.
-This approach can be seen as a robust Bayesian procedure or imprecise probability method
-that reflects surprisingly early or late component failures
-by wider system reliability bounds.
+This paper considers quantification of system reliability in scenarios
+where data, that is failures or absence of failures, occurring from the 
+system's use over time, are considered to be 
+surprising from the perspective of prior information.
+A generalized, or imprecise, Bayesian approach is presented for general
+system structures, where component lifetimes have Weibull distributions with
+known shape parameter. For the scale parameter, a specific set of prior distributions
+is assumed which enables prior-data conflict to be reflected through increased
+imprecision in posterior reliability bounds.
+
 \end{abstract}
@@
 %
-In reliability engineering, a central task is to describe the reliability of a complex system.
-This is usually done by determining the \emph{reliability function} $R(t)$,
-in other contexts also known as the \emph{survival function},
-giving the probability that the system has not failed by time $t$:
-\begin{linenomath*}
-\begin{align}
-\Rsys(t) = P(\Tsys \geq t)\,,
-\end{align}
-\end{linenomath*}
-where $\Tsys$ is the random variable giving the failure time of the system. %
-%\footnote{}
-Based on the distribution of $\Tsys$, which can also be expressed
-in terms of the cumulative distribution function $F_\text{sys}(t) = 1 - \Rsys(t)$,
-%the density $p_\text{sys}(t)$ or the hazard rate $\lambda_\text{sys}(t)$,
-decisions about, e.g., scheduling of maintenance work can be made.
-
-Often, there is no failure data for the system itself
-(e.g., if the system is a prototype, or the system is used under unique circumstances),
-but there is some information about failure times for the components the system is made of.
-The proposed method allows to analyse systems of arbitrary system structures, %layout of components,
-i.e., any combination and nesting of series, parallel, k-out-of-n, or bridge-type arrangements,
-by use of the survival signature \cite{2012:survsign}.
-In doing so, the present paper extends similar previous work
-which focused on a simple parallel system with homogeneous components \cite{2015:walter}.
-In this paper, we assume that components can be divided into $K$ different groups,
-and components within each group $k$ ($k=1, \ldots, K$) can be assumed to be exchangeable,
-i.e., to follow the same failure time distribution.
-Components of group $k$ are denoted as \emph{type $k$ components},
-and are assumed to be independent from components of other types.
-%such that failure times of components of different types are independent.
-Type $k$ component lifetimes $T_i^k$ ($i = 1, \ldots, n_k$)
-are assumed as Weibull distributed with type-specific parameters,
-where the shape parameter $\beta_k$ is known
-and the scale parameter $\lambda_k$ is unknown.
-
-Focusing on a running system,
-we assume that observations consist solely of the failure times of components in this system up to time $\tnow$,
-such that the failure times of components that have not failed by $\tnow$ are right-censored,
-and calculate $\Rsys(t \mid t > \tnow) = P(\Tsys \geq t \mid t > \tnow)$,
-which can be used to determine the remaining useful life of the system
-(in short RUL, see, e.g., \citeNP{2014:rul-review}).
-%This sparse information is complemented by expert information on component lifetimes $T_i^k$.
-
-The Bayesian approach allows to base estimation of the component failure distributions
-on both data and further knowledge not given by the data,
-the latter usually provided in the form of expert knowledge.
-This knowledge is encoded in form of a so-called prior distribution,
-which here, as the shape parameter $\beta_k$ is assumed to be known,
-is a distribution on the scale parameter $\lambda_k$. %of the component lifetime distribution.
-Expert knowledge is especially important when there is very few data on the components, %(like in our scenario),
-as only with its help meaningful estimates for the system reliability can be made.
-%
-Due to the iterative nature of the Bayesian framework,
-it is also possible to use a set of posteriors based on component test data as the set of priors
-instead of a purely expert-based set of priors as discussed so far.
-The component test data may also contain right-censored observations,
-which can be treated in the same way as those from the running system
-(see Section~\ref{sec:lambdawithcens} for details).
-
-The choice of prior distribution to encode given expert knowledge is often debatable,
-and a specific choice of prior is difficult to justify.
-A way to deal with this is to employ sensitivity analysis,
-i.e., studying the effect of different choices of prior distribution on the quantities of interest
-(in our case, the system reliability function, which, in Bayesian terms, is a posterior predictive distribution).
-This idea has been explored in systematic sensitivity analysis, or robust Bayesian methods
-(for an overview on this approach, see, e.g.,
-\citeNP{1994:berger} or \citeNP{2000:rios}).
-
-The work presented here can be seen as belonging to the robust Bayesian approach
-since it uses sets of priors. However, our focus and interpretation is slightly different,
-as we consider the result of our procedure, sets of reliability functions, as the proper result,
-while a robust Bayesian would base his analyses on a single reliability function from the set
-in case (s)he was able to conclude that quantities of interest are not `too sensitive' to the choice of prior.
-In contrast, our viewpoint is rooted in the theory of imprecise or interval probability \cite{1991:walley,itip},
-where sets of distributions are used to express the precision of probability statements themselves:
-the smaller the set, the more precise the probability statement.
-Indeed, the system reliability function $\Rsys(t)$ is a collection of probability statements,
-and a small set for $\Rsys(t)$ will indicate that the reliability of the system can be can quantified quite precisely,
-while a large set will indicate that available knowledge about $\Tsys$ is rather shaky.
-%
-In line with imprecise or interval probability methods, the method provides, for each $t$,
-a lower reliability $\lRsys(t) = \ul{P}(T_\text{sys} \geq t)$,
-and an upper reliability $\uRsys(t) = \ol{P}(T_\text{sys} \geq t)$.
-Sections~\ref{sec:modforsurpr} and \ref{sec:robrel} will explain how these bounds are obtained
-based on sets of prior distributions on the scale parameters of the component lifetime distributions.
-
-The central merit of the proposed method is that it adequately reflects prior-data conflict
-(see, e.g., \citeNP{2006:evans}),
-i.e.\ the conflict that can arise between prior assumptions on component lifetimes
-and observed behaviour of components in the system under study.
-As will be shown in Section~\ref{sec:weibull}, when taking the standard choice of a conjugate prior,
-prior-data conflict is ignored, as the spread of the posterior distribution does not increase in case of such a conflict,
-ultimately conveying a false sense of certainty
-by communicating that the reliability of a system can be quantified quite precisely when in fact it can not.
-%
-In contrast, the proposed method will indicate prior-data conflict by wider bounds for $\Rsys(t)$.
-This behaviour is obtained by a specific choice for the set of priors (see \citeNP{Walter2009a} and \citeNP{diss} \S 3.1.4)
-which leads to larger sets of posterior distributions when prior knowledge and data are in conflict
-(see Section~\ref{sec:modforsurpr} for more details).
-If a prior based on component test data is used,
-such prior-data conflict sensitivity furthermore allows to uncover a conflict between
-current observations in the running system and past observations from component tests.
-
-The topic of prior-data conflict or agreement has of course received attention within the precise Bayesian statistics framework.
-For example, \citeN{2008:bousquet} proposed a method for diagnostics of agreement or disagreement between the prior and data,
-based on a ratio of Kullback-Leibler divergences.
-\citeN{2012:ohagan-pericchi} propose the use of heavy-tailed distributions which,
-in case of conflict between multiple sources of prior information,
-typically provide more weight to one or more of these, when combined with the data,
-than would happen with more commonly used prior distributions.
-While such approaches have some interesting features, e.g. through the quantification of level of disagreement,
-they do not resolve the fundamental issue commented on here,
-namely that the end result of the Bayesian inference remains a single-valued probability
+
+In this paper, we consider a system consisting of components can be divided into $K$ different groups
+or types, with type $k$ components, for $k=1, \ldots, K$, assumed to have exchangeable failure
+times, whilst components of different types are assumed to have independent failure times. 
+We aim to predict the reliability of a running system, assuming we get component failure times 
+from this system up to the moment $\tnow$ of consideration. We use the Bayesian approach for
+component failure time distributions, where the ability to incorporate expert knowledge through
+prior distributions is important because, for most real-world systems, one does not have 
+many component failure times. In line with a generalized setting, advocated both as `robust Bayesian methods'
+(\citeNP{1994:berger}) and `imprecise probability theory' (\citeNP{1991:walley,itip}),
+we use a set of prior distributions which enables a level of indeterminacy to be taken into account on
+the prior information, which is particularly important in practical scenarios where for example prior
+knowledge may be mostly based on experience of similar but not identical components, or of such components
+functioning in different systems or under different circumstances.
+
+While the use of sets of prior distributions in Bayesian statistics has been widely presented in the
+literature, the key contribution of this paper is the presentation, in the system reliability context,
+of a specific set of prior distributions for the shape parameter of the Weibull distribution, such 
+that conflict between prior judgements and process data on the components leads to increased imprecision
+for the system reliability function, hence such conflict is explicitly reported. 
+Prior-data conflict has attracted some attention in the literature (see, e.g., \citeNP{2006:evans}),
+but less than one may have expected because of the obvious importance of noticing a considerable
+difference between prior judgements and process data. In standard Bayesian methods, the posterior 
+distribution is always effectively presenting a weighted average of the prior beliefs and the data,
+without any means to show the level of disagreement between these two sources of information. It is
+particularly surprising that researchers in robust Bayesian methods, who advocated the use of sets of
+priors to more adequately represent lack of perfect expert knowledge, did not put more effort in study
+of prior-data conflict and the possibility to use sets of prior distributions that enable such conflict
+to be clearly indicated.
+
+The approach used in this paper was introduced by \citeNP{Walter2009a} (see also \citeNP{diss} \S 3.1.4).
+It proposes the use of a specific set of prior distributions leading to increased imprecision in posterior 
+inferences when prior knowledge and data are in conflict than when these two sources of information are
+pretty much in agreement. This paper presents the first use of this statistical method for inference on
+component failure times, combined to provide predictions of a system's remaining time until failure.
+
+While we advocate the use of a specific set of prior distributions, in a generalized Bayesian framework,
+for dealing with prior-data conflict, there have also been proposals to reflect such conflict within the 
+standard `precise' Bayesian approach. For example, \citeN{2008:bousquet} proposed a method for diagnostics 
+of agreement or disagreement between the prior and data, based on a ratio of Kullback-Leibler divergences.
+\citeN{2012:ohagan-pericchi} propose the use of heavy-tailed distributions which, in case of conflict 
+between multiple sources of prior information, provide more weight to one or more of these, when combined 
+with the data, than would happen with more commonly used prior distributions. Such methods 
+quantify level of disagreement between prior judgements and data, yet they do not resolve the fundamental 
+issue that the end result of the standard Bayesian method remains a single-valued probability
 which is a weighted average of the prior and data inputs.
 
-The paper is organized as follows.
-In Section~\ref{sec:weibull}, a Bayesian analysis for Weibull component lifetimes
-with fixed shape parameter is described,
-illustrating the issue of prior-data conflict.
-Section~\ref{sec:modforsurpr} then details the use of sets of priors
-for the scale parameter $\lambda_k$ of the Weibull distribution,
-showing how this highlights the prior-data conflict issue for $\lambda_k$.
-Section~\ref{sec:robrel} then develops a method to calculate system reliability bounds
-for a running system based on sets of priors for $\lambda_k$. 
-Section~\ref{sec:elicitation} discusses elicitation,
-by giving guidelines on how to choose prior parameter bounds
-that reflect expert information on components.
+The paper is organized as follows. Section~\ref{sec:weibull} introduces the Bayesian model for the Weibull 
+distribution with fixed shape parameter, as used later in this paper for component failure times.
+Section~\ref{sec:modforsurpr} presents the use of specific sets of priors
+for the scale parameter of the Weibull distribution, in order to reflect prior-data conflict.
+Section~\ref{sec:robrel} presents a method to calculate system reliability bounds
+for a running system based on such sets of priors. An important aspect of the presented method
+is that it can be used for any system structure, through the use of the `survival signature'. 
+Section~\ref{sec:elicitation} discusses elicitation of sets of prior distributions.
 Section~\ref{sec:examples} contains examples illustrating the merits of our method,
@@
 Section~\ref{sec:concluding} concludes the paper by summarizing results
-and indicating avenues for further research.
+and discussing topics for further research.
+
+It should be noted that this paper builds on
+a paper presented at the 2015 ESREL conference and published in its proceedings \cite{2015:walter}. 
+The next two sections, in which the core generalized Bayesian method for inference about component lifetimes is
+introduced, follow that paper closely. Thereafter, the material presented in this paper goes far beyond
+the earlier work: while before only a parallel system consisting of a single type of components was
+considered, this paper presents methodology for any system structure consisting of multiple types of
+components, with prior-data conflict occurring at component level yet being reflected at full system level.
 
@@
 
-Consider a system with components of $k=1,\ldots,K$ different types;
-for each type $k$, there are $n_k$ exchangeable components in the system.
-For each type $k$ component, we assume for its lifetime $T_i^k$ ($i=1,\ldots,n_k$, $k = 1, \ldots, K$)
-a Weibull distribution with fixed shape parameter $\beta_k > 0$,
-in short $T_i^k \mid \lambda_k \sim \wei(\beta_k,\lambda_k)$,
-with density and cdf%
+In this paper, we consider a system with components of $K$ different types.
+There are $n_k$ components of type $k$ ($k=1,\ldots,K$) in the systems, their
+failure times $T_i^k$ ($i=1,\ldots,n_k$, $k = 1, \ldots, K$) are assumed to have
+a Weibull distribution with fixed shape parameter $\beta_k > 0$ and unknown scale
+parameter $\lambda_k$. This distribution has the following probability density function
+$f(\cdot)$ and cumulative distribution function $F(\cdot)$,
 \begin{linenomath*}
@@
 
-The shape parameter $\beta_k$ determines whether the hazard rate is increasing ($\beta_k > 1$)
-or decreasing ($\beta_k < 1$) over time.
-For $\beta_k=1$, one obtains the Exponential distribution with constant hazard rate as a special case.
-The value for $\beta_k$ will often be clear from practical considerations.
-
+The shape parameter $\beta_k$ determines whether the hazard rate is constant ($\beta_k=1$), increasing ($\beta_k > 1$)
+or decreasing ($\beta_k < 1$) over time. Throughout this paper we assume that $\beta_k$ is fixed, this may e.g.\ be
+based on engineering knowledge and insights into the practical failure causes.
 The scale parameter $\lambda_k$ can be interpreted through the relation
@@
 \end{linenomath*}
-For encoding expert knowledge about the reliability of the components,
-one needs to assign a prior distribution over the scale parameter $\lambda_k$.
-A convenient choice is to use the inverse Gamma distribution,
-commonly parametrized in terms of the hyperparameters $a_k > 0$ and $b_k > 0$:
-%Conjugate prior is $\lambda_k \sim \ig(a_k,b_k)$:
-\begin{linenomath*}
-\begin{align}
-f(\lambda_k\mid a_k,b_k) &= \frac{(b_k)^{a_k}}{\Gamma(a_k)} \lambda_k^{-a_k -1} e^{-\frac{b_k}{\lambda_k}}
+where $\Gamma(\cdot)$ is the Gamma function.
+
+In the Bayesian framework, a convenient choice of prior distribution for the scale parameter $\lambda_k$
+is the inverse Gamma distribution, characterized by the probability density function (with hyperparameters 
+$a_k > 0$ and $b_k > 0$)
+\begin{linenomath*}
+\begin{align}
+f(\lambda_k\mid a_k,b_k) &= \frac{(b_k)^{a_k}}{\Gamma(a_k)} \lambda_k^{-a_k -1} e^{-\frac{b_k}{\lambda_k}}\,.
 \label{eq:ig-def}
@@
 \end{linenomath*}
-in short, $\lambda_k \mid a_k, b_k \sim \ig(a_k,b_k)$.
+We indicate this distribution by $\lambda_k \mid a_k, b_k \sim \ig(a_k,b_k)$.
 The inverse Gamma is convenient because it is a conjugate prior,
@@
 
-In the standard Bayesian approach, 
-one has to fix a prior by choosing values for $a_k$ and $b_k$
-to encode specific prior information about component lifetimes.
-In our imprecise approach, we allow instead these parameters
-to vary in a set, this is advantageous also
-because expert knowledge is often vague,
-and it is difficult for the expert(s) to pin down precise hyperparameter values.
-For the definition of the hyperparameter set,
-we use however a parametrization in terms of $\nz > 1$ and $\yz > 0$ instead of $a_k$ and $b_k$,
-where we drop the index $k$ for the discussion about the prior model in the following,
+For the imprecise approach presented in this paper, using a set of inverse Gamma prior distributions for $\lambda_k$,
+we use a different parametrization which is more convenient to specify and interpret the set of prior distributions,
+and hence also to interpret the set of corresponding posterior distributions. We use $\nz > 1$ and $\yz > 0$ instead 
+of $a_k$ and $b_k$, where we drop the index $k$ for the discussion about the prior model in the following,
 keeping in mind that each component type will have its own specific parameters.
-We use
+Let
 %\begin{linenomath*}
@@
 This parametrization also makes the nature of the combination
-of prior information and data through Bayes' rule more clear:
+of prior information and data through Bayes' rule very clear:
 After observing $n$ component lifetimes $\vec{t} = (t_1, \ldots, t_n)$,
@@
 %\footnote{
-We thus have
+Hence, the posterior distribution for $\lambda$ is
 \begin{linenomath*}
@@
 \end{linenomath*}
-%In terms of canonical parameters $\nkz$ and $\ykz$, we assume $\lambda_k \mid \nkz,\ykz \sim \ig(\nkz + 1, \nkz\ykz)$.
-From the simple update rule \eqref{eq:ig-update}, we see that
+
+The update rule \eqref{eq:ig-update} shows that
 $\yn$ is a weighted average of the prior parameter $\yz$ and the maximum likelihood (ML) estimator $\taut/n$,
 with weights proportional to $\nz$ and $n$, respectively.
-$\nz$ can thus be interpreted as a prior strength or pseudocount,
+This enables $\nz$ to be interpreted as a prior strength or pseudocount,
 indicating how much our prior guess should weigh against the $n$ observations.
@@
 However, the weighted average structure for $\yn$
-is behind the problematic behaviour in case of prior-data conflict.
-Assume that from expert knowledge we expect
-to have a mean component lifetime of 9 weeks.
-Using \eqref{eq:lambdainterpret}, with $\beta=2$ we obtain $\yz = 103.13$.
+is behind the problematic behaviour in case of prior-data conflict; we
+illustrate this using a small example. Assume an expert judges that a component
+has a mean lifetime of 9 weeks.
+Using \eqref{eq:lambdainterpret} with $\beta=2$, we obtain $\yz = 103.13$.
 We choose $\nz = 2$, so our prior guess for the mean component lifetime
 counts like having two observations with this mean.
-If we now have a sample of two observations
-with surprisingly early failure times $t_1 = 1$ and $t_2 = 2$,
-using \eqref{eq:ig-update} we get $\nfun{2} = 4$
+Suppose that two observations of failures of such a component become available which
+are surprisingly small, say $t_1 = 1$ and $t_2 = 2$.
+Using \eqref{eq:ig-update} we get $\nfun{2} = 4$
 and $\yfun{2} = \frac{1}{4}(2 \cdot 103.13 + 1^2 + 2^2) = 52.82$,
-so our posterior expectation for the scale parameter $\lambda$ is $52.82$,
+so the posterior expectation for the scale parameter $\lambda$ is $52.82$,
 equivalent to a mean component lifetime of $6.44$ weeks.
@@
 thus conveying a false sense of certainty about $\lambda$.
-We would obtain almost the same %values of $\nfun{2}$ and $\yfun{2}$, and so the same 
+We would obtain almost the same 
 posterior distribution
@@
 and observed lifetimes $t_1 = 6$, $t_2 = 7$ in line with our expectations.
-It seems unreasonable to make the same probability statements on component lifetimes in these two fundamentally different scenarios.
+The main reason for developing the generalized Bayes approach with sets of priors, in order
+to reflect prior-data conflict, is that it seems unreasonable to make the same probability 
+statements on component lifetimes in these two fundamentally different scenarios.
 
@@
 
-Despite this issue of ignoring prior-data conflict,
+Despite the above mentioned issue of ignoring prior-data conflict,
 the tractability of the update step
-is a very attractive feature of the conjugate setting.
+is a very attractive feature of the conjugate setting used above.
 As was shown by \citeN{Walter2009a} (see also \citeNP{diss}, \S 3.1),
@@
 will be sensitive to the degree of prior-data conflict,
-i.e.\ leading to more cautious probability statements when prior-data conflict occurs.
-
-Instead of a single prior guess $\yz$ for the mean component lifetimes,
-we will now assume a range of prior guesses $[\yzl, \yzu]$, and also a range $[\nzl, \nzu]$ of pseudocounts,
-i.e., we now consider the set of priors
+leading to more cautious probability statements when prior-data conflict occurs.
+
+The generalized Bayes approach for the model for a component's lifetime in this
+paper is as follows. Instead of a single prior guess $\yz$ for the mean component 
+lifetimes, a range of prior guesses $[\yzl, \yzu]$ is used, together with a range $[\nzl, \nzu]$ of pseudocounts.
+The set of prior distributions considered is therefore
 \begin{linenomath*}
@@
 \end{linenomath*}
-to express our prior knowledge about component lifetimes.
 Each of the priors $f(\lambda\mid\nz,\yz)$ is then updated to the posterior
@@
 by using \eqref{eq:ig-update},
-such that the set of posteriors $\MN$ can be written as
+such that the set of posteriors $\MN$ becomes
 $\MN = \{ f(\lambda\mid\nn,\yn) \mid \nz \in [\nzl, \nzu], \yz \in [\yzl, \yzu] \}$.
@@
 
-Technically, it is crucial to consider a range of pseudocounts $[\nzl, \nzu]$
-along with the range of prior guesses $[\yzl, \yzu]$,
-as only then $\taut/n \not\in [\yzl, \yzu]$
-leads to the set of posteriors being larger
-and hence reflecting prior-data conflict.
+In order to reflect possible prior-data conflict, it is crucial to consider a range of pseudocounts $[\nzl, \nzu]$
+along with the range of prior guesses $[\yzl, \yzu]$, as only in this case $\taut/n \not\in [\yzl, \yzu]$
+leads to the set of posteriors being larger and hence reflecting prior-data conflict, as will be illustrated below and
+in the subsequent sections.
 
@@
 Choosing $[\nzl,\nzu] =[2, 5]$
-means to value this information on mean component lifetimes as equivalent to having seen two to five observations.
+means that this information on the mean component lifetimes is considered to be of equivalent value to having to two to five 
+actual observations.
 Compare now the set of posteriors obtained from observing
@@
 
-\newpage
 \section{Robust Reliability for Complex Systems via the Survival Signature}
@@
 P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})}\hspace*{5ex} \nonumber\\  %
- &= { n_k - e_k \choose l_k} \int \big[P(T^k >    t \mid T^k > \tnow, \lambda_k)\big]^{l_k} \times \nonumber\\ & \hspace*{17ex}
+ &= \binom{n_k - e_k}{l_k} \int \big[P(T^k >    t \mid T^k > \tnow, \lambda_k)\big]^{l_k} \times \nonumber\\ & \hspace*{17ex}
                                   \big[P(T^k \leq t \mid T^k > \tnow, \lambda_k)\big]^{n_k - e_k - l_k}
@@
 \lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})}\hspace*{5ex} \nonumber\\
- &= { n_k - e_k \choose l_k} \int \Big[    e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\Big]^{l_k}
+ &= \binom{n_k - e_k}{l_k} \int \Big[    e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\Big]^{l_k}
                                   \Big[1 - e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\Big]^{n_k - e_k - l_k}
@@
     \frac{\big(\nkn\ykn\big)^{\nkn + 1}}{\Gamma(\nkn+1)} \lambda_k^{-(\nkn + 1) - 1} e^{-\frac{\nkn\ykn}{\lambda_k}} \dd \lambda_k \nonumber\\
- &= { n_k - e_k \choose l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j { n_k - e_k - l_k \choose j} \frac{\big(\nkn\ykn\big)^{\nkn + 1}}{\Gamma(\nkn+1)} 
+ &= \binom{n_k - e_k}{l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \binom{n_k - e_k - l_k}{j} \frac{\big(\nkn\ykn\big)^{\nkn + 1}}{\Gamma(\nkn+1)} 
     \times \nonumber\\ & \hspace*{13ex}
@@
 \lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})} \nonumber\\
- &= { n_k - e_k \choose l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j { n_k - e_k - l_k \choose j}
+ &= \binom{n_k - e_k}{l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \binom{n_k - e_k - l_k}{j}
     \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nkn + 1} \nonumber\\

### 2017-12-09 asce-revision-final.tex
refrences to subsections deleted

@@
 This system is observed until time $\tnow$,
-leading to censored observation of lifetimes of components within the system,
-and we will explain in Section~\ref{sec:lambdawithcens}
+leading to censored observation of lifetimes of components within the system.
+We will first explain %in Section~\ref{sec:lambdawithcens}
 how the scale parameter $\lambda_k$ for component type $k$
-can be estimated in this situation.
-%
-Section~\ref{sec:sysrelwithsurvsign} describes then
+can be estimated in this situation;
+%
+%Section~\ref{sec:sysrelwithsurvsign} describes then
+then we describe
 how the system reliability function can be efficiently obtained using the survival signature.
 %
-For this, we need the posterior predictive distribution
-of the number of components that function at times $t > \tnow$,
-which we will derive in Section~\ref{sec:postpred}.
-%
-Finally, in Section~\ref{sec:optimize} we describe how
+To use this approach, we need to derive the posterior predictive distribution
+of the number of components that function at times $t > \tnow$.
+%which we will derive in Section~\ref{sec:postpred}.
+%
+%Finally, in Section~\ref{sec:optimize} we describe how
+Finally, we describe how
 the lower and upper bound for the system reliability function
@@
 defining sets $\MkZ$ of prior distributions over $\lambda_k$,
-as introduced in Section~\ref{sec:modforsurpr}.
+as introduced above. %in Section~\ref{sec:modforsurpr}.
 
@@
 
-%***brake system from ijar paper, Fig.~\ref{fig:brakesys-layout}
 As illustrative example, consider a simplified automotive brake system with four types of component.
@@
 
-A fixed prior setting, described in Section~\ref{sec:ex-prior},
+A fixed prior setting %, described in Section~\ref{sec:ex-prior},
 will be combined with three different data scenarios,
-where one observes failure times in accordance with prior expectations in the first case (Section~\ref{sec:ex-case1}),
-surprisingly early failures in the second case (Section~\ref{sec:ex-case2}), and
-surprisingly late failures in the third case (Section~\ref{sec:ex-case3}).
+where one observes failure times in accordance with prior expectations in the first case,
+%(Section~\ref{sec:ex-case1}),
+surprisingly early failures in the second case, and %(Section~\ref{sec:ex-case2}), and
+surprisingly late failures in the third case. %(Section~\ref{sec:ex-case3}).
 In each case, it is assumed that C2, C3, P2 and P3 fail, only the failure times are varied,
@@
 %and for the running system.
-Effects on posterior reliability bounds for the running system
-are then discussed for all three cases in Section~\ref{sec:ex-sysrel}.
+We then discuss effects on posterior reliability bounds for the running system for all three cases.
 
@@
 and posterior imprecision, i.e., the range between lower and upper posterior bound, is notably larger
-as compared to prior imprecision, and substantially larger that posterior imprecision in case~1.
+as compared to prior imprecision, and substantially larger than posterior imprecision in case~1.
 The effect for P is less pronounced,

### 2018-02-22 asce-revision-final.tex
two typos, no hyperref package

@@
 %\usepackage[bookmarks]{hyperref}
-\usepackage[colorlinks=true,citecolor=red,linkcolor=black]{hyperref}
+%\usepackage[colorlinks=true,citecolor=red,linkcolor=black]{hyperref}
+%\usepackage[colorlinks=false]{hyperref}
 
@@
 In this paper, we consider a system with components of $K$ different types.
-There are $n_k$ components of type $k$ ($k=1,\ldots,K$) in the systems, their
+There are $n_k$ components of type $k$ ($k=1,\ldots,K$) in the system, their
 failure times $T_i^k$ ($i=1,\ldots,n_k$, $k = 1, \ldots, K$) are assumed to have
@@
 \begin{align}
-P(\Tsys > t) &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K)
+P(\Tsys > t) &= \sum_{l_1=0}^{n_1} \cdots \sum_{l_K=0}^{n_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K)
                                                                                   P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \nonumber\\

### 2018-02-22 figure1.R

@@ -47,4 +47,5 @@ fig1
 showtext.end()
 dev.off()
 
+#embedFonts("fig1.pdf")
 #

### 2018-02-23 figures3f.R
renaming figures 5a, 6a, 7a to 5, 6, 7

@@ -107,7 +107,7 @@ fig5a <- ggplot(popr1df, aes(x = tvec)) + theme_bw() + ijarcol + ijarfill + ylim
   facet_wrap(~Part, nrow=2) + xlab(expression(t)) + ylab(expression(R(t))) + rightlegend 
 fig5a # warnings refer to the instances which have been rounded down to 1, bug in ggplot?
 
-pdf("fig5a.pdf", width=8, height=6)
+pdf("fig5.pdf", width=8, height=6)
 showtext.begin()
 fig5a
 showtext.end()
@@ -130,7 +130,7 @@ fig5
 
 #setEPS()
 #postscript("fig5.eps",width=8,height=6)
-pdf("fig5.pdf", width=8, height=3)
+pdf("fig5-old.pdf", width=8, height=3)
 fig5
 dev.off()
 
@@ -159,7 +159,7 @@ fig6a <- ggplot(popr2df, aes(x = tvec)) + theme_bw() + ijarcol + ijarfill + ylim
   facet_wrap(~Part, nrow=2) + xlab(expression(t)) + ylab(expression(R(t))) + rightlegend 
 fig6a # warnings refer to the instances which have been rounded down to 1, bug in ggplot?
 
-pdf("fig6a.pdf", width=8, height=6)
+pdf("fig6.pdf", width=8, height=6)
 showtext.begin()
 fig6a
 showtext.end()
@@ -182,7 +182,7 @@ fig6
 
 #setEPS()
 #postscript("fig6.eps",width=8,height=3)
-pdf("fig6.pdf", width=8, height=3)
+pdf("fig6-old.pdf", width=8, height=3)
 fig6
 dev.off()
 
@@ -213,7 +213,7 @@ fig7a # warnings refer to the instances which have been rounded down to 1, bug i
 
 pdf("fig7a.pdf", width=8, height=6)
 showtext.begin()
-fig7a
+fig7
 showtext.end()
 dev.off()
 
@@ -234,7 +234,7 @@ fig7
 
 #setEPS()
 #postscript("fig7.eps",width=8,height=3)
-pdf("fig7.pdf", width=8, height=3)
+pdf("fig7-old.pdf", width=8, height=3)
 fig7
 dev.off()
 

### 2018-04-21 asce-revision-final.tex
renaming figures 5a, 6a, 7a to 5, 6, 7
revision of figure 2, the corresponding caption, and the surv sign table

@@
 \includegraphics[width=\textwidth]{fig2}
-\caption{Set of prior and posterior cdfs for $\lambda$ for two surprising observations $t_1 = 1$, $t_2 = 2$ (left)
-and two unsurprising observations $t_1 = 10$, $t_2 = 11$ (right).}
+\caption{Set of prior and posterior cdfs for $\lambda$ for (a) two surprising observations $t_1 = 1$, $t_2 = 2$
+and (b) two unsurprising observations $t_1 = 10$, $t_2 = 11$.}
 \label{fig:setofpost-pdc-nopdc}
@@
   \toprule
-M & H & C & P & $\Phi$ & \quad & M & H & C & P & $\Phi$\\ 
+M & H & C & P & $\Phi$ \\ 
   \midrule
-1 & 0 & 1 & 1 & 0.25 & & 1 & 0 & 2 & 1 & 0.50 \\ 
-1 & 0 & 1 & 2 & 0.50 & & 1 & 0 & 2 & 2 & 0.83 \\ 
-1 & 0 & 1 & 3 & 0.75 & & 1 & 0 & 3 & 1 & 0.75 \\ 
-0 & 1 & 0 & 1 & 0.50 & & 1 & 1 & 0 & 1 & 0.50 \\ 
-0 & 1 & 0 & 2 & 0.83 & & 1 & 1 & 0 & 2 & 0.83 \\ 
-0 & 1 & 1 & 1 & 0.50 & & 1 & 1 & 1 & 1 & 0.62 \\ 
-0 & 1 & 1 & 2 & 0.83 & & 1 & 1 & 1 & 2 & 0.92 \\ 
-0 & 1 & 2 & 1 & 0.50 & & 1 & 1 & 2 & 1 & 0.75 \\ 
-0 & 1 & 2 & 2 & 0.83 & & 1 & 1 & 2 & 2 & 0.97 \\ 
-0 & 1 & 3 & 1 & 0.50 & & 1 & 1 & 3 & 1 & 0.88 \\ 
+1 & 1 & 0 & 1 & 0.50 \\
+1 & 1 & 0 & 2 & 0.83 \\
+1 & 1 & 1 & 1 & 0.62 \\
+1 & 1 & 1 & 2 & 0.92 \\
+1 & 1 & 2 & 1 & 0.75 \\
+1 & 1 & 2 & 2 & 0.97 \\
+1 & 1 & 3 & 1 & 0.88 \\
+1 & 0 & 1 & 1 & 0.25 \\ 
+1 & 0 & 1 & 2 & 0.50 \\ 
+1 & 0 & 1 & 3 & 0.75 \\ 
+1 & 0 & 2 & 1 & 0.50 \\
+1 & 0 & 2 & 2 & 0.83 \\
+1 & 0 & 3 & 1 & 0.75 \\
+0 & 1 & 0 & 1 & 0.50 \\
+0 & 1 & 0 & 2 & 0.83 \\
+0 & 1 & 1 & 1 & 0.50 \\
+0 & 1 & 1 & 2 & 0.83 \\
+0 & 1 & 2 & 1 & 0.50 \\
+0 & 1 & 2 & 2 & 0.83 \\
+0 & 1 & 3 & 1 & 0.50 \\
 0 & 1 & 3 & 2 & 0.83 \\
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{fig5a}
+\includegraphics[width=\textwidth]{fig5}
 \caption{Sets of posterior predictive reliability functions for the four component types
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{fig6a}
+\includegraphics[width=\textwidth]{fig6}
 \caption{Sets of posterior predictive reliability functions for the four component types
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{fig7a}
+\includegraphics[width=\textwidth]{fig7}
 \caption{Sets of posterior predictive reliability functions for the four component types

### 2018-04-21 figure2.R

@@ -49,8 +49,10 @@ weidf <- function(prior, data, tvec){
 
 fig2data2 <- weidf(forfig2, data2, lvec)
 fig2data3 <- weidf(forfig2, data3, lvec)
-fig2df <- rbind(data.frame(fig2data2, Panel = "Surprising Observations"),
-                data.frame(fig2data3, Panel = "Unsurprising Observations"))
+#fig2df <- rbind(data.frame(fig2data2, Panel = "Surprising Observations"),
+#                data.frame(fig2data3, Panel = "Unsurprising Observations"))
+fig2df <- rbind(data.frame(fig2data2, Panel = "(a)"),
+                data.frame(fig2data3, Panel = "(b)"))
 
 fig2 <- ggplot(fig2df, aes(x = l)) + theme_bw() + ijarcol + ijarfill + ylim(0, 1) +  
   geom_ribbon(aes(ymin = Fll, ymax = Flu, group = Item, colour = Item, fill = Item), alpha  =0.5) +
@@ -60,7 +62,7 @@ fig2 <- ggplot(fig2df, aes(x = l)) + theme_bw() + ijarcol + ijarfill + ylim(0, 1
 
 #setEPS()
 #postscript("fig2.eps",width=8,height=3)
-pdf("fig2-new.pdf", width=8, height=3)
+pdf("fig2.pdf", width=8, height=3)
 #showtext.begin()
 fig2
 #showtext.end()
